\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\title{}
\author{}
\date{}

\begin{document}
\begin{titlepage}
\centering
{\scshape\Huge\textbf The Greater Book of Transmutation \par}
\vspace{1.5cm}
{\scshape\large How to make almost anything in a few easy steps \par}
\vspace{5.5cm}
{\large A Procedurally Generated DIY Book \par}
{\large for the \href{https://github.com/dariusk/NaNoGenMo-2015}{NaNoGenMo 2015} \par}
\vspace{0.5cm}
{\large by \href{http://dragonlab.de}{Tobias Wehrum} \par}
\vfill
{\scriptsize using data by: \par}
\vspace{0.3cm}
{\scriptsize\href{http://web.usf.edu/FreeAssociation}{Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University of South Florida word association, rhyme, and word fragment norms}\par}
\vspace{0.3cm}
{\scriptsize\href{https://www.englishclub.com/vocabulary/nouns-uncountable-list.htm}{English Club: Uncountable Nouns List}\par}
\vspace{0.3cm}
{\scriptsize\href{http://archives.nd.edu/whitaker/dictpage.htm}{LATIN-ENGLISH DICTIONARY WORDLIST Version 1.97FC by William Whitaker}\par}
\vspace{0.5cm}
\end{titlepage}

\setcounter{tocdepth}{1}
\renewcommand*\contentsname{How to make...}
\tableofcontents
\newpage
\section{An abuse}How to make an \textbf{abuse} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.88 ounces of ill-usage
\item 
2.49 ounces of drug
\item 
12.68 ounces of neglect
\item 
14 shames
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Centrifuge
\item 
Vessel
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Put \textbf{12.68 ounces of neglect} into the rotating centrifuge.
\item 
Stir the vessel.
\item 
Crack \textbf{2.49 ounces of drug} with the hammer.
\item 
Stop the centrifuge and retrieve the \textbf{26.58 spoonful of centrifuged mixture "neglect"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a cross into the circle and place \textbf{4.88 ounces of ill-usage}, \textbf{2.49 ounces of cracked drug}, \textbf{14 shames} and \textbf{26.58 spoonful of centrifuged mixture "neglect"} on each corner.
\item 
Whisper the following spell: "Diptychoos!"
\item 
Suddendly, an \textbf{abuse} will appear inside the circle.
\end{enumerate}
\newpage
\section{An ache}How to make an \textbf{ache} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.46 ounces of pain
\item 
5.07 ounces of ear
\item 
4.23 spoonful of back
\item 
6.7 spoonful of muscle
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Cauldron
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4.23 spoonful of back} into the rotating centrifuge.
\item 
Put \textbf{1.46 ounces of pain} into the bonfire.
\item 
Let the cauldron cool down.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{6.7 spoonful of muscle} into the cauldron.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{33.69 spoonful of centrifuged mixture "back"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{27.91 spoonful of cauldron mixture "muscle"}.
\item 
Retrieve the \textbf{2.68 spoonful of ashes of "pain"} from the bonfire.
\item 
Fold the \textbf{5.07 ounces of ear}, \textbf{33.69 spoonful of centrifuged mixture "back"}, \textbf{27.91 spoonful of cauldron mixture "muscle"} and \textbf{2.68 spoonful of ashes of "pain"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in an \textbf{ache}.
\end{enumerate}
\newpage
\section{An achievement}How to make an \textbf{achievement} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.03 spoonful of accomplishment
\item 
75.75 ounces of survival
\item 
63 recognitions
\item 
9.16 ounces of capability
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot water
\item 
Bonfire
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{75.75 ounces of survival} briefly into the bonfire to burn them a bit.
\item 
Wait.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{9.16 ounces of capability} into the bonfire.
\item 
Put \textbf{5.03 spoonful of accomplishment} into the bonfire.
\item 
Wait for a minute.
\item 
Hold \textbf{75.75 ounces of slightly burned survival} briefly into the bonfire to burn them a bit.
\item 
Dip \textbf{63 recognitions} into the bucket with hot water.
\item 
Retrieve the \textbf{1.92 ounces of ashes of "capability and accomplishment"} from the bonfire.
\item 
Use tape to join the \textbf{75.75 ounces of burned survival}, \textbf{63 wet recognitions} and \textbf{1.92 ounces of ashes of "capability and accomplishment"} together into the shape of a passable \textbf{achievement}.
\end{enumerate}
\newpage
\section{An adjustment}How to make an \textbf{adjustment} in 3 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.01 ounces of attitude
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.01 ounces of attitude} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{49.56 spoonful of centrifuged mixture "attitude"}.
\item 
Use screws to join the \textbf{49.56 spoonful of centrifuged mixture "attitude"} together into the shape of a usable \textbf{adjustment}.
\end{enumerate}
\newpage
\section{An adolescent}How to make an \textbf{adolescent} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
29.11 spoonful of teenager
\item 
2.46 spoonful of delinquent
\item 
1 puberty
\item 
59.51 ounces of student
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Cauldron
\item 
Fireplace
\item 
Hammer
\item 
Pet hummingbird
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Feed \textbf{29.11 spoonful of teenager} to your pet hummingbird.
\item 
Put \textbf{1 puberty} into the cauldron.
\item 
Stir the cauldron.
\item 
Let your pet hummingbird sniff at \textbf{59.51 ounces of student}.
\item 
Put \textbf{59.51 ounces of student} into the cauldron.
\item 
Crack \textbf{2.46 spoonful of delinquent} with the hammer.
\item 
Hold \textbf{2.46 spoonful of cracked delinquent} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{2.46 spoonful of cracked and slightly burned delinquent} into the rotating centrifuge.
\item 
Wait until your pet hummingbird poops. Receive \textbf{1.23 ounces of a very dirty pile of "teenager"}.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{9.86 ounces of centrifuged mixture "cracked and slightly burned delinquent"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{2.27 spoonful of cauldron mixture "puberty and student"}.
\item 
Use tape to join the \textbf{1.23 ounces of a very dirty pile of "teenager"}, \textbf{9.86 ounces of centrifuged mixture "cracked and slightly burned delinquent"} and \textbf{2.27 spoonful of cauldron mixture "puberty and student"} together into the shape of a beautiful \textbf{adolescent}.
\end{enumerate}
\newpage
\section{An alike}How to make an \textbf{alike} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
18 vague notions of being opposite
\item 
4.6 ounces of similarity
\item 
60.46 ounces of share
\item 
3.13 ounces of relativity
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with clean water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{18 vague notions of being opposite} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{8.67 spoonful of centrifuged mixture "being opposite"}.
\item 
Dip \textbf{60.46 ounces of share} into the bucket with clean water.
\item 
Put \textbf{60.46 ounces of wet share} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.05 ounces of centrifuged mixture "wet share"}.
\item 
Wait for a very short time.
\item 
Dip \textbf{8.67 spoonful of centrifuged mixture "being opposite"} into the bucket with clean water.
\item 
Throw \textbf{7.05 ounces of centrifuged mixture "wet share"} away.
\item 
Put \textbf{4.6 ounces of similarity} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{36.21 ounces of centrifuged mixture "similarity"}.
\item 
Dump the \textbf{3.13 ounces of relativity}, \textbf{8.67 spoonful of wet centrifuged mixture "being opposite"} and \textbf{36.21 ounces of centrifuged mixture "similarity"} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{alike}.
\end{enumerate}
\newpage
\section{An alley}How to make an \textbf{alley} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17 bowls
\item 
2 clear concepts of being dark
\item 
9.77 spoonful of lane
\item 
10 shadows
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bonfire
\item 
Hammer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{17 bowls} into the rotating centrifuge.
\item 
Put \textbf{2 clear concepts of being dark} into the bonfire.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{12.53 ounces of centrifuged mixture "bowl"}.
\item 
Put \textbf{12.53 ounces of centrifuged mixture "bowl"} into the rotating centrifuge.
\item 
Put \textbf{9.77 spoonful of lane} into the bonfire.
\item 
Smash \textbf{10 shadows} with the hammer.
\item 
Stop the centrifuge and retrieve the \textbf{3.1 ounces of centrifuged mixture "centrifuged mixture "bowl""}.
\item 
Retrieve the \textbf{49.33 ounces of ashes of "being dark and lane"} from the bonfire.
\item 
Fold the \textbf{10 smashed shadows}, \textbf{3.1 ounces of centrifuged mixture "centrifuged mixture "bowl""} and \textbf{49.33 ounces of ashes of "being dark and lane"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in an \textbf{alley}.
\end{enumerate}
\newpage
\section{An alone}How to make an \textbf{alone} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 vague notions of being afraid
\item 
7 vague notions of being private
\item 
5 companions
\item 
45.35 ounces of apart
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Freezer
\item 
Vessel
\item 
Centrifuge
\item 
Bucket with clean liquid
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the vessel.
\item 
Put \textbf{45.35 ounces of apart} into the vessel.
\item 
Dip \textbf{5 companions} into the bucket with clean liquid.
\item 
Put \textbf{7 vague notions of being private} into the freezer for a while.
\item 
Put \textbf{5 wet companions} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{7 cooled vague notions of being private} into the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{2.83 ounces of centrifuged mixture "wet companion"}.
\item 
Fan the flames of the bonfire.
\item 
Hold \textbf{4 vague notions of being afraid} briefly into the bonfire to burn them a bit.
\item 
Pour out the mixture from the vessel to get the \textbf{5.23 spoonful of vessel mixture "apart and cooled being private"}.
\item 
Fold the \textbf{4 slightly burned vague notions of being afraid}, \textbf{2.83 ounces of centrifuged mixture "wet companion"} and \textbf{5.23 spoonful of vessel mixture "apart and cooled being private"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in an \textbf{alone}.
\end{enumerate}
\newpage
\section{An alternative}How to make an \textbf{alternative} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.99 spoonful of dissent
\item 
4 options
\item 
101 anothers
\item 
49.5 spoonful of choice
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Purifier
\item 
Bucket with hot water
\item 
Pet dog
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{4 options} into the bucket with hot water.
\item 
Let the cauldron cool down.
\item 
Put \textbf{7.99 spoonful of dissent} into the cauldron.
\item 
Feed \textbf{49.5 spoonful of choice} to your pet dog.
\item 
Let your pet dog sniff at \textbf{101 anothers}.
\item 
Purify \textbf{4 wet options} with the purifier.
\item 
Wait for a day.
\item 
Pour out the mixture from the cauldron to get the \textbf{14.09 spoonful of cauldron mixture "dissent"}.
\item 
Wait until your pet dog poops. Receive \textbf{5.75 spoonful of a very dirty pile of "choice"}.
\item 
Fold the \textbf{4 wet and purified options}, \textbf{101 anothers}, \textbf{14.09 spoonful of cauldron mixture "dissent"} and \textbf{5.75 spoonful of a very dirty pile of "choice"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in an \textbf{alternative}.
\end{enumerate}
\newpage
\section{An ankle}How to make an \textbf{ankle} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
36 wrists
\item 
46.28 spoonful of rick
\item 
1.3 ounces of elbow
\item 
6.2 ounces of strain
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{6.2 ounces of strain} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{36 wrists} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{46.28 spoonful of rick} briefly into the fireplace to burn them a bit.
\item 
Stir the vessel.
\item 
Let the vessel cool down.
\item 
Heat the vessel.
\item 
Put \textbf{6.2 ounces of slightly burned strain} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{35.12 spoonful of vessel mixture "slightly burned strain"}.
\item 
Dump the \textbf{36 slightly burned wrists}, \textbf{46.28 spoonful of slightly burned rick}, \textbf{1.3 ounces of elbow} and \textbf{35.12 spoonful of vessel mixture "slightly burned strain"} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{ankle}.
\end{enumerate}
\newpage
\section{An answer}How to make an \textbf{answer} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
15.46 ounces of decision
\item 
24.71 ounces of solution
\item 
114.71 spoonful of meaning
\item 
28 exclamations
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Saw
\item 
Centrifuge
\item 
Bucket with ice-cold liquid
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{15.46 ounces of decision} with the hammer.
\item 
Use the saw to slice \textbf{28 exclamations} into bits.
\item 
Wait.
\item 
Dip \textbf{24.71 ounces of solution} into the bucket with ice-cold liquid.
\item 
Put \textbf{114.71 spoonful of meaning} into the rotating centrifuge.
\item 
Wait for a rather long time.
\item 
Smash \textbf{15.46 ounces of cracked decision} with the hammer.
\item 
Put \textbf{15.46 ounces of cracked and smashed decision} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{24.71 ounces of wet solution} into bits.
\item 
Crack \textbf{28 sliced exclamations} with the hammer.
\item 
Stop the centrifuge and retrieve the \textbf{42.68 spoonful of centrifuged mixture "meaning and cracked and smashed decision"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a triangle into the circle and place \textbf{24.71 ounces of wet and sliced solution}, \textbf{28 sliced and cracked exclamations} and \textbf{42.68 spoonful of centrifuged mixture "meaning and cracked and smashed decision"} on each corner.
\item 
Chant the following spell: "Inputo adatus praemictius, iliutus!"
\item 
Reluctantly, an \textbf{answer} will appear inside the circle.
\end{enumerate}
\newpage
\section{An antenna}How to make an \textbf{antenna} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
82.0 spoonful of antler
\item 
4.91 spoonful of antlers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Container
\item 
Saw
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Wait.
\item 
Hold \textbf{4.91 spoonful of antlers} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{82.0 spoonful of antler} into the fireplace.
\item 
Purify \textbf{4.91 spoonful of slightly burned antlers} with the purifier.
\item 
Let the container cool down.
\item 
Use the saw to slice \textbf{4.91 spoonful of slightly burned and purified antlers} into bits.
\item 
Wait for a short time.
\item 
Retrieve the \textbf{14.37 ounces of ashes of "antler"} from the fireplace.
\item 
Fold the \textbf{4.91 spoonful of slightly burned, purified and sliced antlers} and \textbf{14.37 ounces of ashes of "antler"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in an \textbf{antenna}.
\end{enumerate}
\newpage
\section{An architect}How to make an \textbf{architect} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
32 contractors
\item 
9 designs
\item 
3 landscapes
\item 
5 builders
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot water
\item 
Familiar hummingbird
\item 
Container
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Use the saw to slice \textbf{5 builders} into bits.
\item 
Dip \textbf{32 contractors} into the bucket with hot water.
\item 
Let your familiar hummingbird sniff at \textbf{32 wet contractors}.
\item 
Feed \textbf{32 wet contractors} to your familiar hummingbird.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Dip \textbf{5 sliced builders} into the bucket with hot water.
\item 
Feed \textbf{5 sliced and wet builders} to your familiar hummingbird.
\item 
Wait until your familiar hummingbird poops. Receive \textbf{9.88 spoonful of a very dirty pile of "wet contractor and sliced and wet builder"}.
\item 
Dump the \textbf{9 designs}, \textbf{3 landscapes} and \textbf{9.88 spoonful of a very dirty pile of "wet contractor and sliced and wet builder"} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{architect}.
\end{enumerate}
\newpage
\section{An asia}How to make an \textbf{asia} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
25.91 ounces of orient
\item 
8 chinas
\item 
22.47 spoonful of africa
\item 
10.27 spoonful of europe
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Familiar unicorn
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Pet your familiar unicorn.
\item 
Put \textbf{22.47 spoonful of africa} into the rotating centrifuge.
\item 
Let your familiar unicorn lick \textbf{8 chinas}.
\item 
Stop the centrifuge and retrieve the \textbf{13.18 spoonful of centrifuged mixture "africa"}.
\item 
Let your familiar unicorn sniff at \textbf{8 licked chinas}.
\item 
Fold the \textbf{25.91 ounces of orient}, \textbf{8 licked chinas}, \textbf{10.27 spoonful of europe} and \textbf{13.18 spoonful of centrifuged mixture "africa"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in an \textbf{asia}.
\end{enumerate}
\newpage
\section{An asphalt}How to make an \textbf{asphalt} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
37.73 spoonful of tar
\item 
3.9 spoonful of concrete
\item 
7 driveways
\item 
1.03 spoonful of pavement
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Bonfire
\item 
Purifier
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{37.73 spoonful of tar} with the purifier.
\item 
Wait for a rather short time.
\item 
Smash \textbf{3.9 spoonful of concrete} with the mortar.
\item 
Put \textbf{7 driveways} into the bonfire.
\item 
Purify \textbf{1.03 spoonful of pavement} with the purifier.
\item 
Crack \textbf{3.9 spoonful of smashed concrete} with the mortar.
\item 
Smash \textbf{37.73 spoonful of purified tar} with the mortar.
\item 
Retrieve the \textbf{5.23 ounces of ashes of "driveway"} from the bonfire.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a square into the circle and place \textbf{37.73 spoonful of purified and smashed tar}, \textbf{3.9 spoonful of smashed and cracked concrete}, \textbf{1.03 spoonful of purified pavement} and \textbf{5.23 ounces of ashes of "driveway"} on each corner.
\item 
Intone the following spell: "Fruin! Invesco oblector!"
\item 
Suddendly, an \textbf{asphalt} will appear inside the circle.
\end{enumerate}
\newpage
\section{An aspirin}How to make an \textbf{aspirin} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
19.92 ounces of medicine
\item 
7.83 ounces of relief
\item 
10 headaches
\item 
40 pills
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Fireplace
\item 
Centrifuge
\item 
Cauldron
\item 
Pet ape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{40 pills} with the hammer.
\item 
Wait.
\item 
Fan the flames of the fireplace.
\item 
Smash \textbf{10 headaches} with the hammer.
\item 
Let the cauldron cool down.
\item 
Let your pet ape sniff at \textbf{19.92 ounces of medicine}.
\item 
Put \textbf{10 smashed headaches} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{31.07 ounces of centrifuged mixture "smashed headache"}.
\item 
Dump the \textbf{19.92 ounces of medicine}, \textbf{7.83 ounces of relief}, \textbf{40 cracked pills} and \textbf{31.07 ounces of centrifuged mixture "smashed headache"} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{aspirin}.
\end{enumerate}
\newpage
\section{An attic}How to make an \textbf{attic} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.81 ounces of basement
\item 
6.0 ounces of junk
\item 
3.21 ounces of cellar
\item 
19.59 spoonful of storage
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Bonfire
\item 
Mortar
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{6.0 ounces of junk} into the container.
\item 
Put \textbf{19.59 spoonful of storage} into the freezer for a while.
\item 
Smash \textbf{5.81 ounces of basement} with the mortar.
\item 
Pour out the mixture from the container to get the \textbf{28.34 ounces of container mixture "junk"}.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{5.81 ounces of smashed basement} into the freezer for a while.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Fold the \textbf{5.81 ounces of smashed and cooled basement}, \textbf{3.21 ounces of cellar}, \textbf{19.59 spoonful of cooled storage} and \textbf{28.34 ounces of container mixture "junk"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in an \textbf{attic}.
\end{enumerate}
\newpage
\section{An avenue}How to make an \textbf{avenue} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.85 spoonful of boulevard
\item 
9.62 ounces of park
\item 
8 ideas of being electric
\item 
8.1 spoonful of street
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Pet mouse
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Pet your pet mouse.
\item 
Wait.
\item 
Put \textbf{9.62 ounces of park} into the rotating centrifuge.
\item 
Feed \textbf{8 ideas of being electric} to your pet mouse.
\item 
Stop the centrifuge and retrieve the \textbf{8.62 ounces of centrifuged mixture "park"}.
\item 
Wait until your pet mouse poops. Receive \textbf{3.63 spoonful of a very dirty pile of "being electric"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{2.85 spoonful of boulevard}, \textbf{8.1 spoonful of street}, \textbf{8.62 ounces of centrifuged mixture "park"} and \textbf{3.63 spoonful of a very dirty pile of "being electric"} on each corner.
\item 
Chant the following spell: "Anguimina! Latio!"
\item 
Suddendly, an \textbf{avenue} will appear inside the circle.
\end{enumerate}
\newpage
\section{A baby}How to make a \textbf{baby} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.38 ounces of candy
\item 
6 nurseries
\item 
19 vague notions of being childish
\item 
7 carriages
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the container cool down.
\item 
Wait for a very short time.
\item 
Stir the container.
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Wait for a short time.
\item 
Dump the \textbf{3.38 ounces of candy}, \textbf{6 nurseries}, \textbf{19 vague notions of being childish} and \textbf{7 carriages} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{baby}.
\end{enumerate}
\newpage
\section{A back}How to make a \textbf{back} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
20.91 spoonful of through
\item 
1 clear concept of being rear
\item 
15 spines
\item 
29 reels
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 clear concept of being rear} into the rotating centrifuge.
\item 
Put \textbf{15 spines} into the fireplace.
\item 
Speed up the centrifuge.
\item 
Put \textbf{20.91 spoonful of through} into the fireplace.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{1.49 spoonful of centrifuged mixture "being rear"}.
\item 
Use the saw to slice \textbf{29 reels} into bits.
\item 
Put \textbf{29 sliced reels} into the fireplace.
\item 
Retrieve the \textbf{5.04 spoonful of ashes of "spine, through and sliced reel"} from the fireplace.
\item 
Fold the \textbf{1.49 spoonful of centrifuged mixture "being rear"} and \textbf{5.04 spoonful of ashes of "spine, through and sliced reel"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{back}.
\end{enumerate}
\newpage
\section{A backward}How to make a \textbf{backward} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.06 ounces of forwardness
\item 
158 ideas of bend
\item 
3.98 spoonful of retreat
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3.98 spoonful of retreat} into the rotating centrifuge.
\item 
Put \textbf{158 ideas of bend} into the rotating centrifuge.
\item 
Wait for a long time.
\item 
Stop the centrifuge and retrieve the \textbf{8.24 spoonful of centrifuged mixture "retreat and bend"}.
\item 
Use nails to join the \textbf{7.06 ounces of forwardness} and \textbf{8.24 spoonful of centrifuged mixture "retreat and bend"} together into the shape of a passable \textbf{backward}.
\end{enumerate}
\newpage
\section{A bag}How to make a \textbf{bag} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 canvasses
\item 
37 lunches
\item 
45 knapsacks
\item 
9.4 ounces of garbage
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Bucket with hot water
\item 
Centrifuge
\item 
Fireplace
\item 
Familiar unicorn
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{10 canvasses} into the fireplace.
\item 
Put \textbf{9.4 ounces of garbage} into the rotating centrifuge.
\item 
Dip \textbf{45 knapsacks} into the bucket with hot water.
\item 
Put \textbf{37 lunches} into the fireplace.
\item 
Pet your familiar unicorn.
\item 
Stir the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{8.35 ounces of centrifuged mixture "garbage"}.
\item 
Retrieve the \textbf{4.73 spoonful of ashes of "canvass and lunch"} from the fireplace.
\item 
Use screws to join the \textbf{45 wet knapsacks}, \textbf{8.35 ounces of centrifuged mixture "garbage"} and \textbf{4.73 spoonful of ashes of "canvass and lunch"} together into the shape of a beautiful \textbf{bag}.
\end{enumerate}
\newpage
\section{A bagel}How to make a \textbf{bagel} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 clear concepts of being plain
\item 
7 doughnuts
\item 
28.3 ounces of pastry
\item 
6 toasters
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Bonfire
\item 
Saw
\item 
Container
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9 clear concepts of being plain} into the freezer for a while.
\item 
Hold \textbf{28.3 ounces of pastry} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{6 toasters} into the container.
\item 
Hold \textbf{7 doughnuts} briefly into the bonfire to burn them a bit.
\item 
Let the container cool down.
\item 
Use the saw to slice \textbf{7 slightly burned doughnuts} into bits.
\item 
Fan the flames of the bonfire.
\item 
Purify \textbf{7 slightly burned and sliced doughnuts} with the purifier.
\item 
Pour out the mixture from the container to get the \textbf{2.68 ounces of container mixture "toaster"}.
\item 
Fold the \textbf{9 cooled clear concepts of being plain}, \textbf{7 slightly burned, sliced and purified doughnuts}, \textbf{28.3 ounces of slightly burned pastry} and \textbf{2.68 ounces of container mixture "toaster"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{bagel}.
\end{enumerate}
\newpage
\section{A band}How to make a \textbf{band} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 conductors
\item 
7.63 ounces of symphony
\item 
2 jazzes
\item 
1.08 ounces of wrist
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Put \textbf{2 jazzes} into the bonfire.
\item 
Wait.
\item 
Retrieve the \textbf{5.91 spoonful of ashes of "jazz"} from the bonfire.
\item 
Fold the \textbf{7 conductors}, \textbf{7.63 ounces of symphony}, \textbf{1.08 ounces of wrist} and \textbf{5.91 spoonful of ashes of "jazz"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{band}.
\end{enumerate}
\newpage
\section{A banjo}How to make a \textbf{banjo} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
20 guitars
\item 
2.65 spoonful of fiddle
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Familiar unicorn
\item 
Freezer
\item 
Centrifuge
\item 
Bucket with hot water
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{2.65 spoonful of fiddle} into the bucket with hot water.
\item 
Purify \textbf{2.65 spoonful of wet fiddle} with the purifier.
\item 
Put \textbf{2.65 spoonful of wet and purified fiddle} into the freezer for a while.
\item 
Let your familiar unicorn sniff at \textbf{2.65 spoonful of wet, purified and cooled fiddle}.
\item 
Put \textbf{20 guitars} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{5.17 ounces of centrifuged mixture "guitar"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a line into the circle and place \textbf{2.65 spoonful of wet, purified and cooled fiddle} and \textbf{5.17 ounces of centrifuged mixture "guitar"} on each end.
\item 
Intone the following spell: "Elatus! Ambenus armoco pubefacitro amnula connummodium gallero!"
\item 
Slowly, a \textbf{banjo} will appear inside the circle.
\end{enumerate}
\newpage
\section{A beach}How to make a \textbf{beach} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 corals
\item 
9.25 spoonful of sunshine
\item 
7 hawaiis
\item 
7.83 ounces of tide
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Pet unicorn
\item 
Freezer
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the container.
\item 
Let your pet unicorn lick \textbf{4 corals}.
\item 
Put \textbf{7 hawaiis} into the freezer for a while.
\item 
Let the container cool down.
\item 
Let your pet unicorn sniff at \textbf{7 cooled hawaiis}.
\item 
Put \textbf{7.83 ounces of tide} into the container.
\item 
Pour out the mixture from the container to get the \textbf{1.91 ounces of container mixture "tide"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a square into the circle and place \textbf{4 licked corals}, \textbf{9.25 spoonful of sunshine}, \textbf{7 cooled hawaiis} and \textbf{1.91 ounces of container mixture "tide"} on each corner.
\item 
Chant the following spell: "Epinexpens! Solandioneus andictia camphila pito amoro advivomo!"
\item 
Slowly, a \textbf{beach} will appear inside the circle.
\end{enumerate}
\newpage
\section{A beaker}How to make a \textbf{beaker} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 flasks
\item 
6 quantities
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Bucket with hot water
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{6 quantities} into the bucket with hot water.
\item 
Put \textbf{6 wet quantities} into the container.
\item 
Stir the container.
\item 
Heat the container.
\item 
Purify \textbf{8 flasks} with the purifier.
\item 
Pour out the mixture from the container to get the \textbf{17.88 spoonful of container mixture "wet quantity"}.
\item 
Fold the \textbf{8 purified flasks} and \textbf{17.88 spoonful of container mixture "wet quantity"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{beaker}.
\end{enumerate}
\newpage
\section{A beam}How to make a \textbf{beam} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 balances
\item 
8 lasers
\item 
3.79 spoonful of support
\item 
4.96 ounces of flashlight
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot water
\item 
Centrifuge
\item 
Mortar
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{3.79 spoonful of support} with the mortar.
\item 
Put \textbf{8 lasers} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.97 ounces of centrifuged mixture "laser"}.
\item 
Wait for 4 seconds.
\item 
Smash \textbf{3.79 spoonful of cracked support} with the mortar.
\item 
Dip \textbf{3.79 spoonful of cracked and smashed support} into the bucket with hot water.
\item 
Wait for 3 hours.
\item 
Use screws to join the \textbf{3 balances}, \textbf{3.79 spoonful of cracked, smashed and wet support}, \textbf{4.96 ounces of flashlight} and \textbf{1.97 ounces of centrifuged mixture "laser"} together into the form of a beautiful \textbf{beam}.
\end{enumerate}
\newpage
\section{Beer}How to make \textbf{beer} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 mugs
\item 
10 bellies
\item 
8.92 spoonful of pelter
\item 
8 buzzes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised liquid
\item 
Fireplace
\item 
Freezer
\item 
Stone
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{8.92 spoonful of pelter} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Dip \textbf{10 bellies} into the bucket with ionised liquid.
\item 
Smash \textbf{10 wet bellies} with the stone.
\item 
Put \textbf{8.92 spoonful of slightly burned pelter} into the freezer for a while.
\item 
Fold the \textbf{3 mugs}, \textbf{10 wet and smashed bellies}, \textbf{8.92 spoonful of slightly burned and cooled pelter} and \textbf{8 buzzes} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{beer}.
\end{enumerate}
\newpage
\section{A below}How to make a \textbf{below} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.66 spoonful of basement
\item 
25 beneaths
\item 
10 downstair
\item 
7 ideas of being lower
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Bucket with clean water
\item 
Bonfire
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{7.66 spoonful of basement} into the bucket with clean water.
\item 
Stir the container.
\item 
Put \textbf{25 beneaths} into the container.
\item 
Hold \textbf{10 downstair} briefly into the bonfire to burn them a bit.
\item 
Heat the container.
\item 
Stir the container.
\item 
Hold \textbf{7 ideas of being lower} briefly into the bonfire to burn them a bit.
\item 
Pour out the mixture from the container to get the \textbf{7.64 ounces of container mixture "beneath"}.
\item 
Use glue to join the \textbf{7.66 spoonful of wet basement}, \textbf{10 slightly burned downstair}, \textbf{7 slightly burned ideas of being lower} and \textbf{7.64 ounces of container mixture "beneath"} together into the form of a perfectly functional \textbf{below}.
\end{enumerate}
\newpage
\section{A best}How to make a \textbf{best} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.0 ounces of second
\item 
5 ideas of being superior
\item 
10 vague notions of being worst
\item 
2.46 spoonful of friend
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Saw
\item 
Vessel
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.0 ounces of second} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{2.67 ounces of vessel mixture "second"}.
\item 
Smash \textbf{10 vague notions of being worst} with the hammer.
\item 
Heat the vessel.
\item 
Use the saw to slice \textbf{10 smashed vague notions of being worst} into bits.
\item 
Wait for 4 hours.
\item 
Stir the vessel.
\item 
Throw \textbf{2.67 ounces of vessel mixture "second"} away.
\item 
Heat the vessel.
\item 
Use nails to join the \textbf{5 ideas of being superior}, \textbf{10 smashed and sliced vague notions of being worst} and \textbf{2.46 spoonful of friend} together into the form of a beautiful \textbf{best}.
\end{enumerate}
\newpage
\section{A billboard}How to make a \textbf{billboard} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 display
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 display} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Wait for a day.
\item 
Stop the centrifuge and retrieve the \textbf{1.3 ounces of centrifuged mixture "display"}.
\item 
Use nails to join the \textbf{1.3 ounces of centrifuged mixture "display"} together into the shape of a perfectly functional \textbf{billboard}.
\end{enumerate}
\newpage
\section{A blossom}How to make a \textbf{blossom} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.95 spoonful of bloom
\item 
8.94 spoonful of flower
\item 
17.76 spoonful of cherry
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ice-cold water
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{17.76 spoonful of cherry} into bits.
\item 
Wait.
\item 
Dip \textbf{8.94 spoonful of flower} into the bucket with ice-cold water.
\item 
Use the saw to slice \textbf{17.76 spoonful of sliced cherry} into bits.
\item 
Wait.
\item 
Fold the \textbf{5.95 spoonful of bloom}, \textbf{8.94 spoonful of wet flower} and \textbf{17.76 spoonful of fragmented cherry} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{blossom}.
\end{enumerate}
\newpage
\section{A bolt}How to make a \textbf{bolt} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 lightnings
\item 
6.11 ounces of nuts
\item 
8.42 ounces of lock
\item 
5 screws
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with clean liquid
\item 
Purifier
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{6.11 ounces of nuts} with the purifier.
\item 
Dip \textbf{5 screws} into the bucket with clean liquid.
\item 
Wait for a day.
\item 
Purify \textbf{5 wet screws} with the purifier.
\item 
Dip \textbf{10 lightnings} into the bucket with clean liquid.
\item 
Wait for a long time.
\item 
Purify \textbf{10 wet lightnings} with the purifier.
\item 
Throw \textbf{5 wet and purified screws} away.
\item 
Wait for 8 minutes.
\item 
Use nails to join the \textbf{10 wet and purified lightnings}, \textbf{6.11 ounces of purified nuts} and \textbf{8.42 ounces of lock} together into the shape of a perfectly functional \textbf{bolt}.
\end{enumerate}
\newpage
\section{A bond}How to make a \textbf{bond} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 clear concept of bound
\item 
27 winders
\item 
30.39 ounces of together
\item 
13.91 spoonful of chemical
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{1 clear concept of bound} with the purifier.
\item 
Crack \textbf{27 winders} with the stone.
\item 
Smash \textbf{30.39 ounces of together} with the stone.
\item 
Wait for 10 minutes.
\item 
Eat \textbf{27 cracked winders}.
\item 
Smash \textbf{30.39 ounces of smashed together} with the stone.
\item 
Purify \textbf{30.39 ounces of pulverized together} with the purifier.
\item 
Fold the \textbf{1 purified clear concept of bound}, \textbf{30.39 ounces of pulverized and purified together} and \textbf{13.91 spoonful of chemical} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{bond}.
\end{enumerate}
\newpage
\section{A bottle}How to make a \textbf{bottle} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.71 ounces of jar
\item 
7.41 ounces of baby
\item 
7.05 ounces of opener
\item 
8.35 spoonful of medicine
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Saw
\item 
Stone
\item 
Centrifuge
\item 
Cauldron
\item 
Pet dog
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{6.71 ounces of jar} with the stone.
\item 
Feed \textbf{7.41 ounces of baby} to your pet dog.
\item 
Stir the cauldron.
\item 
Use the saw to slice \textbf{6.71 ounces of cracked jar} into bits.
\item 
Hold \textbf{6.71 ounces of cracked and sliced jar} briefly into the bonfire to burn them a bit.
\item 
Stir the cauldron.
\item 
Hold \textbf{6.71 ounces of cracked, sliced and slightly burned jar} briefly into the bonfire to burn them a bit.
\item 
Smash \textbf{7.05 ounces of opener} with the stone.
\item 
Put \textbf{7.05 ounces of smashed opener} into the rotating centrifuge.
\item 
Put \textbf{8.35 spoonful of medicine} into the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{14.25 spoonful of centrifuged mixture "smashed opener"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{5.68 spoonful of cauldron mixture "medicine"}.
\item 
Wait until your pet dog poops. Receive \textbf{33.53 ounces of a very dirty pile of "baby"}.
\item 
Dump the \textbf{6.71 ounces of cracked, sliced and burned jar}, \textbf{14.25 spoonful of centrifuged mixture "smashed opener"}, \textbf{5.68 spoonful of cauldron mixture "medicine"} and \textbf{33.53 ounces of a very dirty pile of "baby"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{bottle}.
\end{enumerate}
\newpage
\section{A bouillon}How to make a \textbf{bouillon} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.72 spoonful of broth
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Cauldron
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the cauldron cool down.
\item 
Put \textbf{6.72 spoonful of broth} into the cauldron.
\item 
Fan the flames of the fireplace.
\item 
Wait for a rather long time.
\item 
Let the cauldron cool down.
\item 
Pour out the mixture from the cauldron to get the \textbf{3.68 ounces of cauldron mixture "broth"}.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Place \textbf{3.68 ounces of cauldron mixture "broth"} into the circle.
\item 
Whisper the following spell: "Miratus! Accummarens typus pagagalles! Paneus perriderecum flo gemmos auginabietio!"
\item 
Slowly, a \textbf{bouillon} will appear inside the circle.
\end{enumerate}
\newpage
\section{A break}How to make a \textbf{break} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 habits
\item 
22 ideas of escape
\item 
10 injuries
\item 
4.39 spoonful of chisel
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised water
\item 
Saw
\item 
Freezer
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Use the saw to slice \textbf{10 injuries} into bits.
\item 
Eat \textbf{6 habits}.
\item 
Put \textbf{4.39 spoonful of chisel} into the freezer for a while.
\item 
Dip \textbf{10 sliced injuries} into the bucket with ionised water.
\item 
Use the saw to slice \textbf{4.39 spoonful of cooled chisel} into bits.
\item 
Put \textbf{22 ideas of escape} into the freezer for a while.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a triangle into the circle and place \textbf{22 cooled ideas of escape}, \textbf{10 sliced and wet injuries} and \textbf{4.39 spoonful of cooled and sliced chisel} on each corner.
\item 
Whisper the following spell: "Pellis!"
\item 
Slowly, a \textbf{break} will appear inside the circle.
\end{enumerate}
\newpage
\section{A breed}How to make a \textbf{breed} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
115 spawners
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Hammer
\item 
Pet cat
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{115 spawners} into the fireplace.
\item 
Pet your pet cat.
\item 
Wait for 10 seconds.
\item 
Fan the flames of the fireplace.
\item 
Retrieve the \textbf{17.96 ounces of ashes of "spawner"} from the fireplace.
\item 
Smash \textbf{17.96 ounces of ashes of "spawner"} with the hammer.
\item 
Put \textbf{17.96 ounces of smashed ashes of "spawner"} into the fireplace.
\item 
Pet your pet cat.
\item 
Retrieve the \textbf{5.42 spoonful of ashes of "smashed ashes of "spawner""} from the fireplace.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Place \textbf{5.42 spoonful of ashes of "smashed ashes of "spawner""} into the circle.
\item 
Intone the following spell: "Flanio adtextre comporatio dedeco alcule, velior dehoratus! Exportunum! Alimabilis belud!"
\item 
Reluctantly, a \textbf{breed} will appear inside the circle.
\end{enumerate}
\newpage
\section{A bride}How to make a \textbf{bride} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 princesses
\item 
4 marriages
\item 
2.73 spoonful of groom
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\item 
Familiar dog
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{4 marriages} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{4 slightly burned marriages} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{2.73 spoonful of groom} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{4 burned marriages} into the vessel.
\item 
Feed \textbf{2.73 spoonful of slightly burned groom} to your familiar dog.
\item 
Pour out the mixture from the vessel to get the \textbf{16.22 ounces of vessel mixture "burned marriage"}.
\item 
Wait until your familiar dog poops. Receive \textbf{6.95 ounces of a very dirty pile of "slightly burned groom"}.
\item 
Use screws to join the \textbf{2 princesses}, \textbf{16.22 ounces of vessel mixture "burned marriage"} and \textbf{6.95 ounces of a very dirty pile of "slightly burned groom"} together into the shape of a passable \textbf{bride}.
\end{enumerate}
\newpage
\section{A broil}How to make a \textbf{broil} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 flames
\item 
7.19 spoonful of frier
\item 
7.58 ounces of baker
\item 
5.35 ounces of lobster
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bonfire
\item 
Hammer
\item 
Pet chinchilla
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{7.19 spoonful of frier} with the hammer.
\item 
Hold \textbf{5.35 ounces of lobster} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{3 flames} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Feed \textbf{5.35 ounces of slightly burned lobster} to your pet chinchilla.
\item 
Put \textbf{7.19 spoonful of cracked frier} into the bonfire.
\item 
Crack \textbf{7.58 ounces of baker} with the hammer.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Put \textbf{7.58 ounces of cracked baker} into the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{2.95 spoonful of centrifuged mixture "flame"}.
\item 
Retrieve the \textbf{3.31 spoonful of ashes of "cracked frier"} from the bonfire.
\item 
Wait until your pet chinchilla poops. Receive \textbf{16.6 ounces of a very dirty pile of "slightly burned lobster"}.
\item 
Pour out the mixture from the vessel to get the \textbf{9.56 spoonful of vessel mixture "cracked baker"}.
\item 
Fold the \textbf{2.95 spoonful of centrifuged mixture "flame"}, \textbf{3.31 spoonful of ashes of "cracked frier"}, \textbf{16.6 ounces of a very dirty pile of "slightly burned lobster"} and \textbf{9.56 spoonful of vessel mixture "cracked baker"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{broil}.
\end{enumerate}
\newpage
\section{A burglary}How to make a \textbf{burglary} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 thefts
\item 
38.38 spoonful of robbery
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Pet unicorn
\item 
Bonfire
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for 3 seconds.
\item 
Let your pet unicorn lick \textbf{38.38 spoonful of robbery}.
\item 
Hold \textbf{7 thefts} briefly into the bonfire to burn them a bit.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a line into the circle and place \textbf{7 slightly burned thefts} and \textbf{38.38 spoonful of licked robbery} on each end.
\item 
Intone the following spell: "Opalus! Vexitio caris scam dico!"
\item 
Slowly, a \textbf{burglary} will appear inside the circle.
\end{enumerate}
\newpage
\section{A bus}How to make a \textbf{bus} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 clear concepts of being gray
\item 
8.44 ounces of shuttle
\item 
4 cabs
\item 
5.07 ounces of truck
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4 cabs} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Wait.
\item 
Heat the container.
\item 
Stop the centrifuge and retrieve the \textbf{5.05 spoonful of centrifuged mixture "cab"}.
\item 
Dump the \textbf{3 clear concepts of being gray}, \textbf{8.44 ounces of shuttle}, \textbf{5.07 ounces of truck} and \textbf{5.05 spoonful of centrifuged mixture "cab"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{bus}.
\end{enumerate}
\newpage
\section{Business}How to make \textbf{business} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.84 ounces of company
\item 
6.45 spoonful of organization
\item 
456.15 ounces of contract
\item 
34.41 spoonful of agency
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Saw
\item 
Freezer
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{4.84 ounces of company} into bits.
\item 
Purify \textbf{456.15 ounces of contract} with the purifier.
\item 
Wait.
\item 
Use the saw to slice \textbf{34.41 spoonful of agency} into bits.
\item 
Put \textbf{34.41 spoonful of sliced agency} into the freezer for a while.
\item 
Purify \textbf{34.41 spoonful of sliced and cooled agency} with the purifier.
\item 
Use the saw to slice \textbf{6.45 spoonful of organization} into bits.
\item 
Wait for a rather short time.
\item 
Put \textbf{456.15 ounces of purified contract} into the freezer for a while.
\item 
Use glue to join the \textbf{4.84 ounces of sliced company}, \textbf{6.45 spoonful of sliced organization}, \textbf{456.15 ounces of purified and cooled contract} and \textbf{34.41 spoonful of sliced, cooled and purified agency} together into the shape of a beautiful \textbf{business}.
\end{enumerate}
\newpage
\section{A caboose}How to make a \textbf{caboose} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.3 ounces of train
\item 
5.31 ounces of railroad
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Hammer
\item 
Freezer
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{5.31 ounces of railroad} into the container.
\item 
Let the container cool down.
\item 
Pour out the mixture from the container to get the \textbf{8.21 spoonful of container mixture "railroad"}.
\item 
Wait for a rather short time.
\item 
Crack \textbf{4.3 ounces of train} with the hammer.
\item 
Grind a little bit of antler of the extinct flying stag to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Put \textbf{4.3 ounces of cracked train} into the freezer for a while.
\item 
Wait for a rather short time.
\item 
Use nails to join the \textbf{4.3 ounces of cracked and cooled train} and \textbf{8.21 spoonful of container mixture "railroad"} together into the shape of a usable \textbf{caboose}.
\end{enumerate}
\newpage
\section{A camera}How to make a \textbf{camera} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.21 ounces of lens
\item 
69 japans
\item 
28.77 spoonful of photo
\item 
20 clear concepts of being underwater
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Purifier
\item 
Saw
\item 
Stone
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{8.21 ounces of lens} with the purifier.
\item 
Smash \textbf{69 japans} with the stone.
\item 
Put \textbf{28.77 spoonful of photo} into the bonfire.
\item 
Purify \textbf{20 clear concepts of being underwater} with the purifier.
\item 
Use the saw to slice \textbf{8.21 ounces of purified lens} into bits.
\item 
Wait for 4 hours.
\item 
Put \textbf{69 smashed japans} into the rotating centrifuge.
\item 
Put \textbf{8.21 ounces of purified and sliced lens} into the bonfire.
\item 
Retrieve the \textbf{23.43 ounces of ashes of "photo and purified and sliced lens"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{5.38 spoonful of centrifuged mixture "smashed japan"}.
\item 
Fold the \textbf{20 purified clear concepts of being underwater}, \textbf{23.43 ounces of ashes of "photo and purified and sliced lens"} and \textbf{5.38 spoonful of centrifuged mixture "smashed japan"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{camera}.
\end{enumerate}
\newpage
\section{A cancer}How to make a \textbf{cancer} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.49 spoonful of lung
\item 
3.86 ounces of ulcer
\item 
8 treatments
\item 
6 cigarettes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Centrifuge
\item 
Stone
\item 
Familiar chinchilla
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{9.49 spoonful of lung} with the stone.
\item 
Put \textbf{9.49 spoonful of cracked lung} into the rotating centrifuge.
\item 
Let the vessel cool down.
\item 
Put \textbf{3.86 ounces of ulcer} into the vessel.
\item 
Crack \textbf{6 cigarettes} with the stone.
\item 
Smash \textbf{6 cracked cigarettes} with the stone.
\item 
Let your familiar chinchilla sniff at \textbf{8 treatments}.
\item 
Stop the centrifuge and retrieve the \textbf{6.67 ounces of centrifuged mixture "cracked lung"}.
\item 
Pour out the mixture from the vessel to get the \textbf{1.02 ounces of vessel mixture "ulcer"}.
\item 
Dump the \textbf{8 treatments}, \textbf{6 cracked and smashed cigarettes}, \textbf{6.67 ounces of centrifuged mixture "cracked lung"} and \textbf{1.02 ounces of vessel mixture "ulcer"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{cancer}.
\end{enumerate}
\newpage
\section{A candle}How to make a \textbf{candle} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.76 ounces of wicker
\item 
4.14 ounces of glow
\item 
30.0 ounces of flame
\item 
1 birthday
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Saw
\item 
Centrifuge
\item 
Bonfire
\item 
Container
\item 
Purifier
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{30.0 ounces of flame} briefly into the bonfire to burn them a bit.
\item 
Crack \textbf{4.14 ounces of glow} with the stone.
\item 
Let the container cool down.
\item 
Purify \textbf{1 birthday} with the purifier.
\item 
Put \textbf{1 purified birthday} into the rotating centrifuge.
\item 
Put \textbf{4.14 ounces of cracked glow} into the bonfire.
\item 
Use the saw to slice \textbf{4.76 ounces of wicker} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{9.3 ounces of centrifuged mixture "purified birthday"}.
\item 
Retrieve the \textbf{3.24 ounces of ashes of "cracked glow"} from the bonfire.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a square into the circle and place \textbf{4.76 ounces of sliced wicker}, \textbf{30.0 ounces of slightly burned flame}, \textbf{9.3 ounces of centrifuged mixture "purified birthday"} and \textbf{3.24 ounces of ashes of "cracked glow"} on each corner.
\item 
Intone the following spell: "Nuntifixus! Benaesurium!"
\item 
Reluctantly, a \textbf{candle} will appear inside the circle.
\end{enumerate}
\newpage
\section{A cane}How to make a \textbf{cane} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 walkers
\item 
8.68 spoonful of crutch
\item 
9.35 ounces of candy
\item 
8.75 ounces of staff
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Container
\item 
Fireplace
\item 
Pet mouse
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Heat the container.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Feed \textbf{9.35 ounces of candy} to your pet mouse.
\item 
Stir the container.
\item 
Let your pet mouse sniff at \textbf{8.75 ounces of staff}.
\item 
Use the saw to slice \textbf{8.68 spoonful of crutch} into bits.
\item 
Wait until your pet mouse poops. Receive \textbf{24.27 spoonful of a very dirty pile of "candy"}.
\item 
Use nails to join the \textbf{9 walkers}, \textbf{8.68 spoonful of sliced crutch}, \textbf{8.75 ounces of staff} and \textbf{24.27 spoonful of a very dirty pile of "candy"} together into the form of a beautiful \textbf{cane}.
\end{enumerate}
\newpage
\section{A canoe}How to make a \textbf{canoe} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 camps
\item 
3 ideas of paddle
\item 
5.28 ounces of oar
\item 
19 boats
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{19 boats} with the purifier.
\item 
Put \textbf{3 ideas of paddle} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{6.01 ounces of centrifuged mixture "paddle"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a square into the circle and place \textbf{8 camps}, \textbf{5.28 ounces of oar}, \textbf{19 purified boats} and \textbf{6.01 ounces of centrifuged mixture "paddle"} on each corner.
\item 
Whisper the following spell: "Secundus!"
\item 
Reluctantly, a \textbf{canoe} will appear inside the circle.
\end{enumerate}
\newpage
\section{A cellar}How to make a \textbf{cellar} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.24 spoonful of wine
\item 
14 dungeons
\item 
3.41 ounces of basement
\item 
4.52 ounces of attic
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Saw
\item 
Mortar
\item 
Purifier
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{14 dungeons} with the purifier.
\item 
Wait for a very short time.
\item 
Smash \textbf{4.52 ounces of attic} with the mortar.
\item 
Use the saw to slice \textbf{6.24 spoonful of wine} into bits.
\item 
Purify \textbf{6.24 spoonful of sliced wine} with the purifier.
\item 
Smash \textbf{14 purified dungeons} with the mortar.
\item 
Crack \textbf{6.24 spoonful of sliced and purified wine} with the mortar.
\item 
Use the saw to slice \textbf{6.24 spoonful of sliced, purified and cracked wine} into bits.
\item 
Put \textbf{6.24 spoonful of fragmented, purified and cracked wine} into the freezer for a while.
\item 
Smash \textbf{3.41 ounces of basement} with the mortar.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a square into the circle and place \textbf{6.24 spoonful of fragmented, purified, cracked and cooled wine}, \textbf{14 purified and smashed dungeons}, \textbf{3.41 ounces of smashed basement} and \textbf{4.52 ounces of smashed attic} on each corner.
\item 
Chant the following spell: "Conto futtia props! Depagogitio exclum pedater proculus condens maleunicus! Bar! Alter prosus malibernus, creputris! Inna!"
\item 
Slowly, a \textbf{cellar} will appear inside the circle.
\end{enumerate}
\newpage
\section{A chairperson}How to make a \textbf{chairperson} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.41 ounces of committee
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Saw
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{8.41 ounces of committee} into bits.
\item 
Put \textbf{8.41 ounces of sliced committee} into the freezer for a while.
\item 
Smash \textbf{8.41 ounces of sliced and cooled committee} with the hammer.
\item 
Wait for a rather long time.
\item 
Crack \textbf{8.41 ounces of sliced, cooled and smashed committee} with the hammer.
\item 
Dump the \textbf{8.41 ounces of sliced, cooled, smashed and cracked committee} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{chairperson}.
\end{enumerate}
\newpage
\section{Chalk}How to make \textbf{chalk} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.36 spoonful of chalkboard
\item 
1.24 spoonful of line
\item 
5.18 ounces of grit
\item 
40 boards
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Bucket with hot water
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Wait for 8 seconds.
\item 
Dip \textbf{1.24 spoonful of line} into the bucket with hot water.
\item 
Put \textbf{3.36 spoonful of chalkboard} into the freezer for a while.
\item 
Let the cauldron cool down.
\item 
Wait.
\item 
Fold the \textbf{3.36 spoonful of cooled chalkboard}, \textbf{1.24 spoonful of wet line}, \textbf{5.18 ounces of grit} and \textbf{40 boards} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in \textbf{chalk}.
\end{enumerate}
\newpage
\section{A champion}How to make a \textbf{champion} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.23 spoonful of winner
\item 
38.99 spoonful of boxer
\item 
4 titles
\item 
1.55 ounces of victor
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Mortar
\item 
Centrifuge
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{4 titles} into bits.
\item 
Wait for a rather short time.
\item 
Smash \textbf{2.23 spoonful of winner} with the mortar.
\item 
Put \textbf{2.23 spoonful of smashed winner} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{6.32 ounces of centrifuged mixture "smashed winner"}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a cross into the circle and place \textbf{38.99 spoonful of boxer}, \textbf{4 sliced titles}, \textbf{1.55 ounces of victor} and \textbf{6.32 ounces of centrifuged mixture "smashed winner"} on each corner.
\item 
Intone the following spell: "Dejurum ingulus consessa! Poreus communitas petrachina vigesciatus! Dedo balbus amarius! Homplicus!"
\item 
Slowly, a \textbf{champion} will appear inside the circle.
\end{enumerate}
\newpage
\section{A chase}How to make a \textbf{chase} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.2 ounces of paper
\item 
8.23 ounces of steeple
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Bucket with water
\item 
Centrifuge
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{8.23 ounces of steeple} with the stone.
\item 
Put \textbf{5.2 ounces of paper} into the rotating centrifuge.
\item 
Dip \textbf{8.23 ounces of smashed steeple} into the bucket with water.
\item 
Put \textbf{8.23 ounces of smashed and wet steeple} into the rotating centrifuge.
\item 
Let the cauldron cool down.
\item 
Stop the centrifuge and retrieve the \textbf{9.25 spoonful of centrifuged mixture "paper and smashed and wet steeple"}.
\item 
Fold the \textbf{9.25 spoonful of centrifuged mixture "paper and smashed and wet steeple"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{chase}.
\end{enumerate}
\newpage
\section{Chess}How to make \textbf{chess} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.02 ounces of strategy
\item 
11.79 ounces of bishop
\item 
7 ideas of check
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with clean liquid
\item 
Container
\item 
Saw
\item 
Fireplace
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a second.
\item 
Dip \textbf{6.02 ounces of strategy} into the bucket with clean liquid.
\item 
Stir the container.
\item 
Use the saw to slice \textbf{11.79 ounces of bishop} into bits.
\item 
Dip \textbf{7 ideas of check} into the bucket with clean liquid.
\item 
Let the container cool down.
\item 
Put \textbf{11.79 ounces of sliced bishop} into the fireplace.
\item 
Put \textbf{7 wet ideas of check} into the fireplace.
\item 
Retrieve the \textbf{21.77 ounces of ashes of "sliced bishop and wet check"} from the fireplace.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a line into the circle and place \textbf{6.02 ounces of wet strategy} and \textbf{21.77 ounces of ashes of "sliced bishop and wet check"} on each end.
\item 
Chant the following spell: "Emotunicius delio potis! Confrugion atter!"
\item 
Slowly, \textbf{chess} will appear inside the circle.
\end{enumerate}
\newpage
\section{A chorus}How to make a \textbf{chorus} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
26 tenors
\item 
10 ideas of sing
\item 
8.28 ounces of choir
\item 
1.43 spoonful of verse
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Vessel
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the vessel.
\item 
Let the vessel cool down.
\item 
Wait.
\item 
Purify \textbf{8.28 ounces of choir} with the purifier.
\item 
Stir the vessel.
\item 
Let the vessel cool down.
\item 
Use nails to join the \textbf{26 tenors}, \textbf{10 ideas of sing}, \textbf{8.28 ounces of purified choir} and \textbf{1.43 spoonful of verse} together into the form of a passable \textbf{chorus}.
\end{enumerate}
\newpage
\section{A chowder}How to make a \textbf{chowder} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.73 ounces of soup
\item 
5 clams
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot water
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{5.73 ounces of soup} into the bucket with hot water.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Wait.
\item 
Put \textbf{5 clams} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{3.82 spoonful of vessel mixture "clam"}.
\item 
Stir the vessel.
\item 
Fold the \textbf{5.73 ounces of wet soup} and \textbf{3.82 spoonful of vessel mixture "clam"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{chowder}.
\end{enumerate}
\newpage
\section{A chunk}How to make a \textbf{chunk} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 vague notions of bite
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ice-cold liquid
\item 
Fireplace
\item 
Stone
\item 
Freezer
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{7 vague notions of bite} with the stone.
\item 
Smash \textbf{7 cracked vague notions of bite} with the stone.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{7 cracked and smashed vague notions of bite} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{7 cracked, smashed and slightly burned vague notions of bite} into the freezer for a while.
\item 
Dip \textbf{7 cracked, smashed, slightly burned and cooled vague notions of bite} into the bucket with ice-cold liquid.
\item 
Fan the flames of the fireplace.
\item 
Use screws to join the \textbf{7 cracked, smashed, slightly burned, cooled and wet vague notions of bite} together into the shape of a passable \textbf{chunk}.
\end{enumerate}
\newpage
\section{A cocoon}How to make a \textbf{cocoon} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
15.55 ounces of moth
\item 
1.29 ounces of butterfly
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Saw
\item 
Centrifuge
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.29 ounces of butterfly} into the rotating centrifuge.
\item 
Heat the container.
\item 
Use the saw to slice \textbf{15.55 ounces of moth} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{21.16 spoonful of centrifuged mixture "butterfly"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a line into the circle and place \textbf{15.55 ounces of sliced moth} and \textbf{21.16 spoonful of centrifuged mixture "butterfly"} on each end.
\item 
Chant the following spell: "Negliga!"
\item 
Slowly, a \textbf{cocoon} will appear inside the circle.
\end{enumerate}
\newpage
\section{A comb}How to make a \textbf{comb} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 grooms
\item 
2.93 ounces of honey
\item 
8.23 ounces of hairspray
\item 
15.83 spoonful of hair
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Bonfire
\item 
Purifier
\item 
Pet unicorn
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Feed \textbf{3 grooms} to your pet unicorn.
\item 
Hold \textbf{8.23 ounces of hairspray} briefly into the bonfire to burn them a bit.
\item 
Let your pet unicorn lick \textbf{2.93 ounces of honey}.
\item 
Smash \textbf{8.23 ounces of slightly burned hairspray} with the stone.
\item 
Purify \textbf{15.83 spoonful of hair} with the purifier.
\item 
Wait until your pet unicorn poops. Receive \textbf{1.99 ounces of a very dirty pile of "groom"}.
\item 
Use nails to join the \textbf{2.93 ounces of licked honey}, \textbf{8.23 ounces of slightly burned and smashed hairspray}, \textbf{15.83 spoonful of purified hair} and \textbf{1.99 ounces of a very dirty pile of "groom"} together into the shape of a passable \textbf{comb}.
\end{enumerate}
\newpage
\section{A combination}How to make a \textbf{combination} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
86 mixtures
\item 
7 clear concepts of mix
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Bucket with ionised water
\item 
Centrifuge
\item 
Saw
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{86 mixtures} with the stone.
\item 
Put \textbf{86 cracked mixtures} into the rotating centrifuge.
\item 
Dip \textbf{7 clear concepts of mix} into the bucket with ionised water.
\item 
Wait.
\item 
Use the saw to slice \textbf{7 wet clear concepts of mix} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{36.66 spoonful of centrifuged mixture "cracked mixture"}.
\item 
Wait for a long time.
\item 
Use glue to join the \textbf{7 wet and sliced clear concepts of mix} and \textbf{36.66 spoonful of centrifuged mixture "cracked mixture"} together into the form of a usable \textbf{combination}.
\end{enumerate}
\newpage
\section{A commitment}How to make a \textbf{commitment} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 engagements
\item 
14.03 ounces of relationship
\item 
101.18 spoonful of marriage
\item 
16.63 spoonful of appointment
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Mortar
\item 
Bucket with hot water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{14.03 ounces of relationship} with the mortar.
\item 
Crack \textbf{14.03 ounces of smashed relationship} with the mortar.
\item 
Purify \textbf{6 engagements} with the purifier.
\item 
Wait.
\item 
Eat \textbf{16.63 spoonful of appointment}.
\item 
Dip \textbf{14.03 ounces of smashed and cracked relationship} into the bucket with hot water.
\item 
Crack \textbf{14.03 ounces of smashed, cracked and wet relationship} with the mortar.
\item 
Smash \textbf{14.03 ounces of smashed, crushed and wet relationship} with the mortar.
\item 
Wait for a second.
\item 
Fold the \textbf{6 purified engagements}, \textbf{14.03 ounces of pulverized, crushed and wet relationship} and \textbf{101.18 spoonful of marriage} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{commitment}.
\end{enumerate}
\newpage
\section{A community}How to make a \textbf{community} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.55 ounces of society
\item 
8 ideas of being local
\item 
34.7 ounces of development
\item 
15 distances
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Vessel
\item 
Centrifuge
\item 
Hammer
\item 
Familiar chinchilla
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a rather long time.
\item 
Throw \textbf{15 distances} away.
\item 
Let your familiar chinchilla lick \textbf{7.55 ounces of society}.
\item 
Purify \textbf{7.55 ounces of licked society} with the purifier.
\item 
Crack \textbf{34.7 ounces of development} with the hammer.
\item 
Let your familiar chinchilla sniff at \textbf{34.7 ounces of cracked development}.
\item 
Put \textbf{7.55 ounces of licked and purified society} into the rotating centrifuge.
\item 
Put \textbf{34.7 ounces of cracked development} into the freezer for a while.
\item 
Put \textbf{34.7 ounces of cracked and cooled development} into the vessel.
\item 
Let the vessel cool down.
\item 
Pour out the mixture from the vessel to get the \textbf{7.95 ounces of vessel mixture "cracked and cooled development"}.
\item 
Stop the centrifuge and retrieve the \textbf{9.61 spoonful of centrifuged mixture "licked and purified society"}.
\item 
Dump the \textbf{8 ideas of being local}, \textbf{7.95 ounces of vessel mixture "cracked and cooled development"} and \textbf{9.61 spoonful of centrifuged mixture "licked and purified society"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{community}.
\end{enumerate}
\newpage
\section{A companion}How to make a \textbf{companion} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.52 spoonful of mate
\item 
1.37 ounces of friend
\item 
10 friendships
\item 
1.33 ounces of girlfriend
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Centrifuge
\item 
Cauldron
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{10 friendships} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Crack \textbf{1.37 ounces of friend} with the stone.
\item 
Stir the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{20.88 ounces of centrifuged mixture "friendship"}.
\item 
Use tape to join the \textbf{9.52 spoonful of mate}, \textbf{1.37 ounces of cracked friend}, \textbf{1.33 ounces of girlfriend} and \textbf{20.88 ounces of centrifuged mixture "friendship"} together into the shape of a usable \textbf{companion}.
\end{enumerate}
\newpage
\section{A company}How to make a \textbf{company} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 records
\item 
24.31 spoonful of tobacco
\item 
40.5 ounces of alone
\item 
4 departments
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Hammer
\item 
Centrifuge
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{40.5 ounces of alone} into the rotating centrifuge.
\item 
Put \textbf{24.31 spoonful of tobacco} into the fireplace.
\item 
Retrieve the \textbf{3.13 ounces of ashes of "tobacco"} from the fireplace.
\item 
Crack \textbf{8 records} with the hammer.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{4 departments} into the fireplace.
\item 
Hold \textbf{8 cracked records} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{8 cracked and slightly burned records} into the fireplace.
\item 
Put \textbf{3.13 ounces of ashes of "tobacco"} into the fireplace.
\item 
Retrieve the \textbf{73.05 ounces of ashes of "department, cracked and slightly burned record and ashes of "tobacco""} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{9.45 ounces of centrifuged mixture "alone"}.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a line into the circle and place \textbf{73.05 ounces of ashes of "department, cracked and slightly burned record and ashes of "tobacco""} and \textbf{9.45 ounces of centrifuged mixture "alone"} on each end.
\item 
Whisper the following spell: "Levocubius molanss! Fagingo annipes! Fetia bris advorsus, concularius!"
\item 
Suddendly, a \textbf{company} will appear inside the circle.
\end{enumerate}
\newpage
\section{A cone}How to make a \textbf{cone} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.07 ounces of yogurt
\item 
9.07 ounces of cylinder
\item 
10.92 ounces of pine
\item 
20.61 spoonful of ice cream
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\item 
Stone
\item 
Bucket with clean liquid
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{20.61 spoonful of ice cream} into the rotating centrifuge.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Put \textbf{10.92 ounces of pine} into the rotating centrifuge.
\item 
Dip \textbf{9.07 ounces of cylinder} into the bucket with clean liquid.
\item 
Crack \textbf{3.07 ounces of yogurt} with the stone.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{1.33 ounces of centrifuged mixture "ice cream and pine"}.
\item 
Use screws to join the \textbf{3.07 ounces of cracked yogurt}, \textbf{9.07 ounces of wet cylinder} and \textbf{1.33 ounces of centrifuged mixture "ice cream and pine"} together into the shape of a beautiful \textbf{cone}.
\end{enumerate}
\newpage
\section{A contact}How to make a \textbf{contact} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
31 clear concepts of kiss
\item 
8 notices
\item 
3.19 ounces of lens
\item 
3.23 ounces of directness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\item 
Container
\item 
Freezer
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the container.
\item 
Put \textbf{31 clear concepts of kiss} into the freezer for a while.
\item 
Put \textbf{3.23 ounces of directness} into the rotating centrifuge.
\item 
Put \textbf{3.19 ounces of lens} into the container.
\item 
Wait for a long time.
\item 
Put \textbf{8 notices} into the rotating centrifuge.
\item 
Purify \textbf{31 cooled clear concepts of kiss} with the purifier.
\item 
Put \textbf{31 cooled and purified clear concepts of kiss} into the rotating centrifuge.
\item 
Pour out the mixture from the container to get the \textbf{21.95 spoonful of container mixture "lens"}.
\item 
Stop the centrifuge and retrieve the \textbf{1.15 spoonful of centrifuged mixture "directness, notice and cooled and purified kiss"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a line into the circle and place \textbf{21.95 spoonful of container mixture "lens"} and \textbf{1.15 spoonful of centrifuged mixture "directness, notice and cooled and purified kiss"} on each end.
\item 
Intone the following spell: "Sepisorbo!"
\item 
Slowly, a \textbf{contact} will appear inside the circle.
\end{enumerate}
\newpage
\section{A cowgirl}How to make a \textbf{cowgirl} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
46.95 spoonful of cowboy
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Centrifuge
\item 
Mortar
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{46.95 spoonful of cowboy} with the mortar.
\item 
Use the saw to slice \textbf{46.95 spoonful of cracked cowboy} into bits.
\item 
Wait for a day.
\item 
Put \textbf{46.95 spoonful of cracked and sliced cowboy} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{6.37 ounces of centrifuged mixture "cracked and sliced cowboy"}.
\item 
Wait for an hour.
\item 
Use nails to join the \textbf{6.37 ounces of centrifuged mixture "cracked and sliced cowboy"} together into the form of a beautiful \textbf{cowgirl}.
\end{enumerate}
\newpage
\section{A crack}How to make a \textbf{crack} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.9 ounces of drugs
\item 
2.57 spoonful of leak
\item 
8.24 ounces of walnut
\item 
7.62 spoonful of cocaine
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Fireplace
\item 
Centrifuge
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8.24 ounces of walnut} into the rotating centrifuge.
\item 
Put \textbf{7.62 spoonful of cocaine} into the fireplace.
\item 
Let the cauldron cool down.
\item 
Stop the centrifuge and retrieve the \textbf{10.29 spoonful of centrifuged mixture "walnut"}.
\item 
Put \textbf{10.29 spoonful of centrifuged mixture "walnut"} into the cauldron.
\item 
Wait for 7 seconds.
\item 
Stir the cauldron.
\item 
Heat the cauldron.
\item 
Put \textbf{9.9 ounces of drugs} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.13 spoonful of centrifuged mixture "drugs"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{3.81 ounces of cauldron mixture "centrifuged mixture "walnut""}.
\item 
Retrieve the \textbf{8.63 ounces of ashes of "cocaine"} from the fireplace.
\item 
Use screws to join the \textbf{2.57 spoonful of leak}, \textbf{1.13 spoonful of centrifuged mixture "drugs"}, \textbf{3.81 ounces of cauldron mixture "centrifuged mixture "walnut""} and \textbf{8.63 ounces of ashes of "cocaine"} together into the form of a passable \textbf{crack}.
\end{enumerate}
\newpage
\section{A crash}How to make a \textbf{crash} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.77 ounces of accident
\item 
7.06 ounces of wreck
\item 
3 bumpers
\item 
8 booms
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Put \textbf{8 booms} into the rotating centrifuge.
\item 
Crack \textbf{4.77 ounces of accident} with the hammer.
\item 
Put \textbf{7.06 ounces of wreck} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{2.28 spoonful of centrifuged mixture "boom and wreck"}.
\item 
Crack \textbf{2.28 spoonful of centrifuged mixture "boom and wreck"} with the hammer.
\item 
Fold the \textbf{4.77 ounces of cracked accident}, \textbf{3 bumpers} and \textbf{2.28 spoonful of cracked centrifuged mixture "boom and wreck"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{crash}.
\end{enumerate}
\newpage
\section{A criticism}How to make a \textbf{criticism} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.92 ounces of constructiveness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{1.92 ounces of constructiveness} with the purifier.
\item 
Wait.
\item 
Put \textbf{1.92 ounces of purified constructiveness} into the freezer for a while.
\item 
Throw \textbf{1.92 ounces of purified and cooled constructiveness} away.
\item 
Wait for a minute.
\item 
Grind a little bit of troll teeth to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Turn around. You will find that a \textbf{criticism} was there all along.
\end{enumerate}
\newpage
\section{A crutch}How to make a \textbf{crutch} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.6 ounces of cane
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.6 ounces of cane} into the rotating centrifuge.
\item 
Heat the cauldron.
\item 
Wait.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{3.64 spoonful of centrifuged mixture "cane"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Place \textbf{3.64 spoonful of centrifuged mixture "cane"} into the circle.
\item 
Intone the following spell: "Murithion tor assus! Letus! Diaculatus pertium abolum, dulus prologiato! Pauleia turganito bapticius composis incrum, inditio umbro! Illo!"
\item 
Suddendly, a \textbf{crutch} will appear inside the circle.
\end{enumerate}
\newpage
\section{A cuff}How to make a \textbf{cuff} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.68 spoonful of sleeve
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Container
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the container.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{3.68 spoonful of sleeve} into the bonfire.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Stir the container.
\item 
Retrieve the \textbf{3.88 spoonful of ashes of "sleeve"} from the bonfire.
\item 
Use tape to join the \textbf{3.88 spoonful of ashes of "sleeve"} together into the form of a passable \textbf{cuff}.
\end{enumerate}
\newpage
\section{A dash}How to make a \textbf{dash} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 ideas of daring
\item 
3 vague notions of sprinkle
\item 
4.16 ounces of bolt
\item 
4 pinches
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Vessel
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{4 pinches} into bits.
\item 
Let the vessel cool down.
\item 
Put \textbf{4.16 ounces of bolt} into the vessel.
\item 
Put \textbf{3 vague notions of sprinkle} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{4 sliced pinches} into bits.
\item 
Hold \textbf{4 fragmented pinches} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{4.69 spoonful of centrifuged mixture "sprinkle"}.
\item 
Pour out the mixture from the vessel to get the \textbf{9.94 ounces of vessel mixture "bolt"}.
\item 
Fold the \textbf{8 ideas of daring}, \textbf{4 fragmented and slightly burned pinches}, \textbf{4.69 spoonful of centrifuged mixture "sprinkle"} and \textbf{9.94 ounces of vessel mixture "bolt"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{dash}.
\end{enumerate}
\newpage
\section{A deer}How to make a \textbf{deer} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
19 clear concepts of crossing
\item 
23.29 spoonful of fawn
\item 
10 antlers
\item 
7.97 ounces of foe
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with hot liquid
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{19 clear concepts of crossing} into the rotating centrifuge.
\item 
Dip \textbf{7.97 ounces of foe} into the bucket with hot liquid.
\item 
Put \textbf{10 antlers} into the fireplace.
\item 
Retrieve the \textbf{13.47 spoonful of ashes of "antler"} from the fireplace.
\item 
Put \textbf{7.97 ounces of wet foe} into the rotating centrifuge.
\item 
Dip \textbf{23.29 spoonful of fawn} into the bucket with hot liquid.
\item 
Stop the centrifuge and retrieve the \textbf{27.32 spoonful of centrifuged mixture "crossing and wet foe"}.
\item 
Dump the \textbf{23.29 spoonful of wet fawn}, \textbf{13.47 spoonful of ashes of "antler"} and \textbf{27.32 spoonful of centrifuged mixture "crossing and wet foe"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{deer}.
\end{enumerate}
\newpage
\section{A defeat}How to make a \textbf{defeat} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 triumphs
\item 
6.64 spoonful of renunciation
\item 
2 conquests
\item 
2.52 ounces of victory
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Saw
\item 
Mortar
\item 
Fireplace
\item 
Centrifuge
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8 triumphs} into the container.
\item 
Crack \textbf{6.64 spoonful of renunciation} with the mortar.
\item 
Smash \textbf{2 conquests} with the mortar.
\item 
Pour out the mixture from the container to get the \textbf{37.08 ounces of container mixture "triumph"}.
\item 
Put \textbf{37.08 ounces of container mixture "triumph"} into the rotating centrifuge.
\item 
Smash \textbf{2 smashed conquests} with the mortar.
\item 
Crack \textbf{2 pulverized conquests} with the mortar.
\item 
Hold \textbf{6.64 spoonful of cracked renunciation} briefly into the fireplace to burn them a bit.
\item 
Use the saw to slice \textbf{6.64 spoonful of cracked and slightly burned renunciation} into bits.
\item 
Wait for a rather short time.
\item 
Stop the centrifuge and retrieve the \textbf{12.91 ounces of centrifuged mixture "container mixture "triumph""}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a square into the circle and place \textbf{6.64 spoonful of cracked, slightly burned and sliced renunciation}, \textbf{2 pulverized and cracked conquests}, \textbf{2.52 ounces of victory} and \textbf{12.91 ounces of centrifuged mixture "container mixture "triumph""} on each corner.
\item 
Whisper the following spell: "Parium oeniola! Ablon dedo anticatus! Ectrix batus usurro utcus linus, maneus irro!"
\item 
Suddendly, a \textbf{defeat} will appear inside the circle.
\end{enumerate}
\newpage
\section{A demand}How to make a \textbf{demand} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.74 spoonful of popularity
\item 
2 orders
\item 
13.18 ounces of request
\item 
7 reprimands
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Bonfire
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{6.74 spoonful of popularity} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{2 orders} into the freezer for a while.
\item 
Smash \textbf{2 cooled orders} with the hammer.
\item 
Hold \textbf{13.18 ounces of request} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{6.74 spoonful of slightly burned popularity} into the freezer for a while.
\item 
Fan the flames of the bonfire.
\item 
Dump the \textbf{6.74 spoonful of slightly burned and cooled popularity}, \textbf{2 cooled and smashed orders}, \textbf{13.18 ounces of slightly burned request} and \textbf{7 reprimands} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{demand}.
\end{enumerate}
\newpage
\section{A demi}How to make a \textbf{demi} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.11 spoonful of half
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.11 spoonful of half} into the container.
\item 
Pour out the mixture from the container to get the \textbf{1.67 spoonful of container mixture "half"}.
\item 
Wait for 4 minutes.
\item 
Stir the container.
\item 
Eat \textbf{1.67 spoonful of container mixture "half"}.
\item 
Fan the flames of the bonfire.
\item 
Heat the container.
\item 
Wait for an hour.
\item 
Wait a bit until a \textbf{demi} suddenly appears.
\end{enumerate}
\newpage
\section{A dew}How to make a \textbf{dew} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
11 mornings
\item 
31.35 spoonful of honey
\item 
10 mists
\item 
6.46 ounces of damper
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Bucket with liquid
\item 
Vessel
\item 
Mortar
\item 
Familiar cat
\item 
Centrifuge
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{11 mornings} with the mortar.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Smash \textbf{11 cracked mornings} with the mortar.
\item 
Wait for a second.
\item 
Feed \textbf{6.46 ounces of damper} to your familiar cat.
\item 
Purify \textbf{31.35 spoonful of honey} with the purifier.
\item 
Dip \textbf{11 cracked and smashed mornings} into the bucket with liquid.
\item 
Stir the vessel.
\item 
Put \textbf{10 mists} into the rotating centrifuge.
\item 
Wait until your familiar cat poops. Receive \textbf{18.5 spoonful of a very dirty pile of "damper"}.
\item 
Stop the centrifuge and retrieve the \textbf{21.31 ounces of centrifuged mixture "mist"}.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a cross into the circle and place \textbf{11 cracked, smashed and wet mornings}, \textbf{31.35 spoonful of purified honey}, \textbf{18.5 spoonful of a very dirty pile of "damper"} and \textbf{21.31 ounces of centrifuged mixture "mist"} on each corner.
\item 
Chant the following spell: "Aliteridus ductum! Divialiqueor axumeus pectus adstricus!"
\item 
Slowly, a \textbf{dew} will appear inside the circle.
\end{enumerate}
\newpage
\section{A digestion}How to make a \textbf{digestion} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
25 intestines
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Purifier
\item 
Bucket with clean liquid
\item 
Freezer
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{25 intestines} into the freezer for a while.
\item 
Dip \textbf{25 cooled intestines} into the bucket with clean liquid.
\item 
Crack \textbf{25 cooled and wet intestines} with the stone.
\item 
Put \textbf{25 cooled, wet and cracked intestines} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.87 ounces of centrifuged mixture "cooled, wet and cracked intestine"}.
\item 
Purify \textbf{1.87 ounces of centrifuged mixture "cooled, wet and cracked intestine"} with the purifier.
\item 
Put \textbf{1.87 ounces of purified centrifuged mixture "cooled, wet and cracked intestine"} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{1.95 spoonful of centrifuged mixture "purified centrifuged mixture "cooled, wet and cracked intestine""}.
\item 
Fold the \textbf{1.95 spoonful of centrifuged mixture "purified centrifuged mixture "cooled, wet and cracked intestine""} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{digestion}.
\end{enumerate}
\newpage
\section{Dignity}How to make \textbf{dignity} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.74 spoonful of respect
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Bonfire
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.74 spoonful of respect} into the cauldron.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Fan the flames of the bonfire.
\item 
Pour out the mixture from the cauldron to get the \textbf{6.91 ounces of cauldron mixture "respect"}.
\item 
Let the cauldron cool down.
\item 
Wait for a minute.
\item 
Put \textbf{6.91 ounces of cauldron mixture "respect"} into the bonfire.
\item 
Stir the cauldron.
\item 
Retrieve the \textbf{8.24 spoonful of ashes of "cauldron mixture "respect""} from the bonfire.
\item 
Use glue to join the \textbf{8.24 spoonful of ashes of "cauldron mixture "respect""} together into the shape of a passable \textbf{dignity}.
\end{enumerate}
\newpage
\section{A direction}How to make a \textbf{direction} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 signals
\item 
9.4 ounces of result
\item 
5.91 ounces of map
\item 
2.32 ounces of purpose
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Mortar
\item 
Bonfire
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{5.91 ounces of map} into bits.
\item 
Put \textbf{9.4 ounces of result} into the bonfire.
\item 
Put \textbf{5.91 ounces of sliced map} into the bonfire.
\item 
Crack \textbf{2.32 ounces of purpose} with the mortar.
\item 
Purify \textbf{2.32 ounces of cracked purpose} with the purifier.
\item 
Wait.
\item 
Retrieve the \textbf{8.06 ounces of ashes of "result and sliced map"} from the bonfire.
\item 
Fold the \textbf{5 signals}, \textbf{2.32 ounces of cracked and purified purpose} and \textbf{8.06 ounces of ashes of "result and sliced map"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{direction}.
\end{enumerate}
\newpage
\section{A disbelief}How to make a \textbf{disbelief} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.19 ounces of dismay
\item 
6 doubts
\item 
3.1 ounces of belief
\item 
9.5 ounces of shock
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Saw
\item 
Hammer
\item 
Bonfire
\item 
Bucket with clean water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{8.19 ounces of dismay} into bits.
\item 
Fan the flames of the bonfire.
\item 
Stir the cauldron.
\item 
Smash \textbf{9.5 ounces of shock} with the hammer.
\item 
Use the saw to slice \textbf{9.5 ounces of smashed shock} into bits.
\item 
Dip \textbf{6 doubts} into the bucket with clean water.
\item 
Put \textbf{3.1 ounces of belief} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{8.36 spoonful of centrifuged mixture "belief"}.
\item 
Dump the \textbf{8.19 ounces of sliced dismay}, \textbf{6 wet doubts}, \textbf{9.5 ounces of smashed and sliced shock} and \textbf{8.36 spoonful of centrifuged mixture "belief"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{disbelief}.
\end{enumerate}
\newpage
\section{A dish}How to make a \textbf{dish} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.56 ounces of china
\item 
7 saucers
\item 
1 vague notion of being ceramic
\item 
44.89 spoonful of silverware
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Stone
\item 
Bucket with hot water
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{1 vague notion of being ceramic} with the purifier.
\item 
Fan the flames of the bonfire.
\item 
Hold \textbf{1 purified vague notion of being ceramic} briefly into the bonfire to burn it a bit.
\item 
Hold \textbf{44.89 spoonful of silverware} briefly into the bonfire to burn them a bit.
\item 
Hold \textbf{1 purified and slightly burned vague notion of being ceramic} briefly into the bonfire to burn it a bit.
\item 
Put \textbf{44.89 spoonful of slightly burned silverware} into the bonfire.
\item 
Dip \textbf{7 saucers} into the bucket with hot water.
\item 
Purify \textbf{7 wet saucers} with the purifier.
\item 
Smash \textbf{1 purified and burned vague notion of being ceramic} with the stone.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{4.05 spoonful of ashes of "slightly burned silverware"} from the bonfire.
\item 
Dump the \textbf{3.56 ounces of china}, \textbf{7 wet and purified saucers}, \textbf{1 purified, burned and smashed vague notion of being ceramic} and \textbf{4.05 spoonful of ashes of "slightly burned silverware"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{dish}.
\end{enumerate}
\newpage
\section{A doughnut}How to make a \textbf{doughnut} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 frosts
\item 
3.17 spoonful of dough
\item 
30 custards
\item 
45.74 ounces of biscuit
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Hammer
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{30 custards} with the hammer.
\item 
Purify \textbf{3.17 spoonful of dough} with the purifier.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a square into the circle and place \textbf{5 frosts}, \textbf{3.17 spoonful of purified dough}, \textbf{30 cracked custards} and \textbf{45.74 ounces of biscuit} on each corner.
\item 
Chant the following spell: "Acus! Uniterrectum! Grasto!"
\item 
Reluctantly, a \textbf{doughnut} will appear inside the circle.
\end{enumerate}
\newpage
\section{A dove}How to make a \textbf{dove} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.11 spoonful of bird
\item 
16 ideas of being peaceful
\item 
9.16 ounces of turtle
\item 
1.87 ounces of symbol
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Centrifuge
\item 
Saw
\item 
Vessel
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{1.87 ounces of symbol} briefly into the fireplace to burn them a bit.
\item 
Use the saw to slice \textbf{1.87 ounces of slightly burned symbol} into bits.
\item 
Put \textbf{9.16 ounces of turtle} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Put \textbf{16 ideas of being peaceful} into the freezer for a while.
\item 
Stop the centrifuge and retrieve the \textbf{3.58 ounces of centrifuged mixture "turtle"}.
\item 
Fold the \textbf{4.11 spoonful of bird}, \textbf{16 cooled ideas of being peaceful}, \textbf{1.87 ounces of slightly burned and sliced symbol} and \textbf{3.58 ounces of centrifuged mixture "turtle"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{dove}.
\end{enumerate}
\newpage
\section{A doze}How to make a \textbf{doze} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.39 spoonful of drowse
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4.39 spoonful of drowse} into the fireplace.
\item 
Wait.
\item 
Retrieve the \textbf{9.12 spoonful of ashes of "drowse"} from the fireplace.
\item 
Hold \textbf{9.12 spoonful of ashes of "drowse"} briefly into the fireplace to burn them a bit.
\item 
Wait.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{9.12 spoonful of slightly burned ashes of "drowse"} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{9.12 spoonful of burned ashes of "drowse"} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{32.95 ounces of centrifuged mixture "burned ashes of "drowse""}.
\item 
Use nails to join the \textbf{32.95 ounces of centrifuged mixture "burned ashes of "drowse""} together into the shape of a beautiful \textbf{doze}.
\end{enumerate}
\newpage
\section{A dracula}How to make a \textbf{dracula} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.72 ounces of cape
\item 
6.09 ounces of fangs
\item 
4.0 ounces of coffin
\item 
3.29 spoonful of stake
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Freezer
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the container.
\item 
Put \textbf{3.29 spoonful of stake} into the container.
\item 
Put \textbf{4.0 ounces of coffin} into the freezer for a while.
\item 
Let the container cool down.
\item 
Pour out the mixture from the container to get the \textbf{4.12 ounces of container mixture "stake"}.
\item 
Put \textbf{6.09 ounces of fangs} into the container.
\item 
Hold \textbf{9.72 ounces of cape} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{4.0 ounces of cooled coffin} into the bonfire.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{2.67 spoonful of ashes of "cooled coffin"} from the bonfire.
\item 
Pour out the mixture from the container to get the \textbf{9.85 ounces of container mixture "fangs"}.
\item 
Fold the \textbf{9.72 ounces of slightly burned cape}, \textbf{4.12 ounces of container mixture "stake"}, \textbf{2.67 spoonful of ashes of "cooled coffin"} and \textbf{9.85 ounces of container mixture "fangs"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{dracula}.
\end{enumerate}
\newpage
\section{A drill}How to make a \textbf{drill} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.27 spoonful of bit
\item 
5.54 ounces of chuck
\item 
9.73 spoonful of dentist
\item 
5.77 ounces of sergeant
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Pet unicorn
\item 
Vessel
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{5.54 ounces of chuck} into the rotating centrifuge.
\item 
Pet your pet unicorn.
\item 
Let your pet unicorn lick \textbf{9.73 spoonful of dentist}.
\item 
Stir the vessel.
\item 
Put \textbf{5.77 ounces of sergeant} into the rotating centrifuge.
\item 
Let the vessel cool down.
\item 
Hold \textbf{9.27 spoonful of bit} briefly into the bonfire to burn them a bit.
\item 
Speed up the centrifuge.
\item 
Pet your pet unicorn.
\item 
Stop the centrifuge and retrieve the \textbf{5.41 spoonful of centrifuged mixture "chuck and sergeant"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a triangle into the circle and place \textbf{9.27 spoonful of slightly burned bit}, \textbf{9.73 spoonful of licked dentist} and \textbf{5.41 spoonful of centrifuged mixture "chuck and sergeant"} on each corner.
\item 
Chant the following spell: "Confrenda!"
\item 
Reluctantly, a \textbf{drill} will appear inside the circle.
\end{enumerate}
\newpage
\section{A driveway}How to make a \textbf{driveway} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.44 spoonful of gravel
\item 
8 parkways
\item 
9.57 ounces of concrete
\item 
5 asphalts
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Container
\item 
Stone
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{2.44 spoonful of gravel} with the stone.
\item 
Put \textbf{5 asphalts} into the rotating centrifuge.
\item 
Put \textbf{9.57 ounces of concrete} into the rotating centrifuge.
\item 
Heat the container.
\item 
Put \textbf{2.44 spoonful of smashed gravel} into the bonfire.
\item 
Put \textbf{8 parkways} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.78 ounces of centrifuged mixture "asphalt, concrete and parkway"}.
\item 
Retrieve the \textbf{8.38 ounces of ashes of "smashed gravel"} from the bonfire.
\item 
Dump the \textbf{4.78 ounces of centrifuged mixture "asphalt, concrete and parkway"} and \textbf{8.38 ounces of ashes of "smashed gravel"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{driveway}.
\end{enumerate}
\newpage
\section{A drop}How to make a \textbf{drop} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17 vague notions of dump
\item 
8 clear concepts of spill
\item 
10 clear concepts of lift
\item 
3 clear concepts of raise
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Mortar
\item 
Fireplace
\item 
Bucket with ice-cold water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3 clear concepts of raise} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Dip \textbf{17 vague notions of dump} into the bucket with ice-cold water.
\item 
Hold \textbf{8 clear concepts of spill} briefly into the fireplace to burn them a bit.
\item 
Smash \textbf{10 clear concepts of lift} with the mortar.
\item 
Speed up the centrifuge.
\item 
Put \textbf{17 wet vague notions of dump} into the rotating centrifuge.
\item 
Hold \textbf{8 slightly burned clear concepts of spill} briefly into the fireplace to burn them a bit.
\item 
Wait.
\item 
Dip \textbf{8 burned clear concepts of spill} into the bucket with ice-cold water.
\item 
Stop the centrifuge and retrieve the \textbf{6.57 ounces of centrifuged mixture "raise and wet dump"}.
\item 
Dump the \textbf{8 burned and wet clear concepts of spill}, \textbf{10 smashed clear concepts of lift} and \textbf{6.57 ounces of centrifuged mixture "raise and wet dump"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{drop}.
\end{enumerate}
\newpage
\section{A dwarf}How to make a \textbf{dwarf} in 4 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.62 ounces of dwarves
\item 
2 elves
\item 
7.37 spoonful of midget
\item 
6 vague notions of being sleepy
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{8.62 ounces of dwarves} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{8.62 ounces of slightly burned dwarves} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{2 elves} briefly into the fireplace to burn them a bit.
\item 
Use glue to join the \textbf{8.62 ounces of burned dwarves}, \textbf{2 slightly burned elves}, \textbf{7.37 spoonful of midget} and \textbf{6 vague notions of being sleepy} together into the form of a beautiful \textbf{dwarf}.
\end{enumerate}
\newpage
\section{An ears}How to make an \textbf{ears} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 swabs
\item 
3.02 spoonful of elf
\item 
5 rabbits
\item 
122.94 spoonful of eyes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ice-cold water
\item 
Bonfire
\item 
Stone
\item 
Vessel
\item 
Centrifuge
\item 
Freezer
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Put \textbf{6 swabs} into the rotating centrifuge.
\item 
Crack \textbf{5 rabbits} with the stone.
\item 
Put \textbf{3.02 spoonful of elf} into the freezer for a while.
\item 
Dip \textbf{3.02 spoonful of cooled elf} into the bucket with ice-cold water.
\item 
Fan the flames of the bonfire.
\item 
Crack \textbf{5 cracked rabbits} with the stone.
\item 
Put \textbf{3.02 spoonful of cooled and wet elf} into the bonfire.
\item 
Put \textbf{122.94 spoonful of eyes} into the rotating centrifuge.
\item 
Retrieve the \textbf{18.92 spoonful of ashes of "cooled and wet elf"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{5.52 spoonful of centrifuged mixture "swab and eyes"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a triangle into the circle and place \textbf{5 crushed rabbits}, \textbf{18.92 spoonful of ashes of "cooled and wet elf"} and \textbf{5.52 spoonful of centrifuged mixture "swab and eyes"} on each corner.
\item 
Intone the following spell: "Sta expalo carbium apopus! Perbunde putatante reperitustuo metrictus!"
\item 
Reluctantly, an \textbf{ears} will appear inside the circle.
\end{enumerate}
\newpage
\section{An editor}How to make an \textbf{editor} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.22 ounces of letters
\item 
5 writers
\item 
3.75 ounces of publisher
\item 
2.96 spoonful of author
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with ionised liquid
\item 
Purifier
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a rather short time.
\item 
Heat the vessel.
\item 
Purify \textbf{3.75 ounces of publisher} with the purifier.
\item 
Put \textbf{4.22 ounces of letters} into the vessel.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Put \textbf{2.96 spoonful of author} into the rotating centrifuge.
\item 
Let the vessel cool down.
\item 
Dip \textbf{5 writers} into the bucket with ionised liquid.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{17.45 ounces of centrifuged mixture "author"}.
\item 
Pour out the mixture from the vessel to get the \textbf{7.94 ounces of vessel mixture "letters"}.
\item 
Fold the \textbf{5 wet writers}, \textbf{3.75 ounces of purified publisher}, \textbf{17.45 ounces of centrifuged mixture "author"} and \textbf{7.94 ounces of vessel mixture "letters"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in an \textbf{editor}.
\end{enumerate}
\newpage
\section{An ego}How to make an \textbf{ego} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.78 spoonful of bravado
\item 
4 clear concepts of being arrogant
\item 
10 vague notions of being cocky
\item 
5.38 ounces of confidence
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Bucket with ionised water
\item 
Fireplace
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{10 vague notions of being cocky} into the bucket with ionised water.
\item 
Use the saw to slice \textbf{1.78 spoonful of bravado} into bits.
\item 
Put \textbf{1.78 spoonful of sliced bravado} into the rotating centrifuge.
\item 
Hold \textbf{10 wet vague notions of being cocky} briefly into the fireplace to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{2.63 ounces of centrifuged mixture "sliced bravado"}.
\item 
Fold the \textbf{4 clear concepts of being arrogant}, \textbf{10 wet and slightly burned vague notions of being cocky}, \textbf{5.38 ounces of confidence} and \textbf{2.63 ounces of centrifuged mixture "sliced bravado"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in an \textbf{ego}.
\end{enumerate}
\newpage
\section{An employee}How to make an \textbf{employee} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.32 spoonful of faculty
\item 
19 ideas of associate
\item 
1.49 spoonful of manager
\item 
4.52 spoonful of union
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Hammer
\item 
Fireplace
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Smash \textbf{4.52 spoonful of union} with the hammer.
\item 
Stir the vessel.
\item 
Crack \textbf{1.49 spoonful of manager} with the hammer.
\item 
Let the vessel cool down.
\item 
Hold \textbf{1.49 spoonful of cracked manager} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{4.52 spoonful of smashed union} into the fireplace.
\item 
Wait for a rather long time.
\item 
Put \textbf{19 ideas of associate} into the vessel.
\item 
Hold \textbf{1.49 spoonful of cracked and slightly burned manager} briefly into the fireplace to burn them a bit.
\item 
Pour out the mixture from the vessel to get the \textbf{15.19 ounces of vessel mixture "associate"}.
\item 
Retrieve the \textbf{6.98 spoonful of ashes of "smashed union"} from the fireplace.
\item 
Use nails to join the \textbf{6.32 spoonful of faculty}, \textbf{1.49 spoonful of cracked and burned manager}, \textbf{15.19 ounces of vessel mixture "associate"} and \textbf{6.98 spoonful of ashes of "smashed union"} together into the form of a passable \textbf{employee}.
\end{enumerate}
\newpage
\section{Entertainment}How to make \textbf{entertainment} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.5 ounces of movie
\item 
39 televisions
\item 
1 idea of show
\item 
2.92 spoonful of performance
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Pet hummingbird
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.5 ounces of movie} into the freezer for a while.
\item 
Pet your pet hummingbird.
\item 
Put \textbf{1 idea of show} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{18.46 ounces of centrifuged mixture "show"}.
\item 
Dump the \textbf{7.5 ounces of cooled movie}, \textbf{39 televisions}, \textbf{2.92 spoonful of performance} and \textbf{18.46 ounces of centrifuged mixture "show"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{entertainment}.
\end{enumerate}
\newpage
\section{An eraser}How to make an \textbf{eraser} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.18 ounces of chalkboard
\item 
3.72 ounces of marker
\item 
39 errors
\item 
10.93 spoonful of remover
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the cauldron cool down.
\item 
Put \textbf{10.93 spoonful of remover} into the rotating centrifuge.
\item 
Put \textbf{9.18 ounces of chalkboard} into the cauldron.
\item 
Speed up the centrifuge.
\item 
Let the cauldron cool down.
\item 
Pour out the mixture from the cauldron to get the \textbf{4.39 ounces of cauldron mixture "chalkboard"}.
\item 
Heat the cauldron.
\item 
Put \textbf{4.39 ounces of cauldron mixture "chalkboard"} into the cauldron.
\item 
Put \textbf{39 errors} into the rotating centrifuge.
\item 
Heat the cauldron.
\item 
Pour out the mixture from the cauldron to get the \textbf{4.87 ounces of cauldron mixture "cauldron mixture "chalkboard""}.
\item 
Stop the centrifuge and retrieve the \textbf{6.55 ounces of centrifuged mixture "remover and error"}.
\item 
Use screws to join the \textbf{3.72 ounces of marker}, \textbf{4.87 ounces of cauldron mixture "cauldron mixture "chalkboard""} and \textbf{6.55 ounces of centrifuged mixture "remover and error"} together into the form of a usable \textbf{eraser}.
\end{enumerate}
\newpage
\section{Evidence}How to make \textbf{evidence} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 vague notions of prove
\item 
12.44 spoonful of confutation
\item 
7 circumstances
\item 
2 traces
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot liquid
\item 
Container
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7 circumstances} into the rotating centrifuge.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Dip \textbf{12.44 spoonful of confutation} into the bucket with hot liquid.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{5.03 ounces of centrifuged mixture "circumstance"}.
\item 
Dump the \textbf{7 vague notions of prove}, \textbf{12.44 spoonful of wet confutation}, \textbf{2 traces} and \textbf{5.03 ounces of centrifuged mixture "circumstance"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{evidence}.
\end{enumerate}
\newpage
\section{An exchange}How to make an \textbf{exchange} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.44 spoonful of barter
\item 
7.4 ounces of trade
\item 
10 clear concepts of transplant
\item 
4.19 spoonful of switch
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Freezer
\item 
Bonfire
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{4.19 spoonful of switch} briefly into the bonfire to burn them a bit.
\item 
Wait for a minute.
\item 
Put \textbf{10 clear concepts of transplant} into the rotating centrifuge.
\item 
Throw \textbf{7.4 ounces of trade} away.
\item 
Hold \textbf{4.19 spoonful of slightly burned switch} briefly into the bonfire to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{25.77 spoonful of centrifuged mixture "transplant"}.
\item 
Put \textbf{25.77 spoonful of centrifuged mixture "transplant"} into the freezer for a while.
\item 
Fan the flames of the bonfire.
\item 
Wait.
\item 
Hold \textbf{7.44 spoonful of barter} briefly into the bonfire to burn them a bit.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a triangle into the circle and place \textbf{7.44 spoonful of slightly burned barter}, \textbf{4.19 spoonful of burned switch} and \textbf{25.77 spoonful of cooled centrifuged mixture "transplant"} on each corner.
\item 
Whisper the following spell: "Asperetitum apax kadapatur!"
\item 
Reluctantly, an \textbf{exchange} will appear inside the circle.
\end{enumerate}
\newpage
\section{An existence}How to make an \textbf{existence} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.53 spoonful of presence
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Fireplace
\item 
Stone
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Crack \textbf{3.53 spoonful of presence} with the stone.
\item 
Smash \textbf{3.53 spoonful of cracked presence} with the stone.
\item 
Put \textbf{3.53 spoonful of cracked and smashed presence} into the fireplace.
\item 
Let the vessel cool down.
\item 
Heat the vessel.
\item 
Stir the vessel.
\item 
Let the vessel cool down.
\item 
Heat the vessel.
\item 
Retrieve the \textbf{10.9 spoonful of ashes of "cracked and smashed presence"} from the fireplace.
\item 
Dump the \textbf{10.9 spoonful of ashes of "cracked and smashed presence"} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{existence}.
\end{enumerate}
\newpage
\section{An express}How to make an \textbf{express} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.37 spoonful of orient
\item 
1397.36 ounces of pony
\item 
3 ideas of being federal
\item 
10 opinions
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Bucket with liquid
\item 
Bonfire
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{10 opinions} with the purifier.
\item 
Use the saw to slice \textbf{1397.36 ounces of pony} into bits.
\item 
Dip \textbf{9.37 spoonful of orient} into the bucket with liquid.
\item 
Fan the flames of the bonfire.
\item 
Hold \textbf{3 ideas of being federal} briefly into the bonfire to burn them a bit.
\item 
Dump the \textbf{9.37 spoonful of wet orient}, \textbf{1397.36 ounces of sliced pony}, \textbf{3 slightly burned ideas of being federal} and \textbf{10 purified opinions} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{express}.
\end{enumerate}
\newpage
\section{A face}How to make a \textbf{face} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 mouths
\item 
9.83 spoonful of mug
\item 
4.51 ounces of powder
\item 
18.4 ounces of mask
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot liquid
\item 
Freezer
\item 
Centrifuge
\item 
Vessel
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Put \textbf{18.4 ounces of mask} into the freezer for a while.
\item 
Put \textbf{4.51 ounces of powder} into the rotating centrifuge.
\item 
Dip \textbf{9 mouths} into the bucket with hot liquid.
\item 
Hold \textbf{18.4 ounces of cooled mask} briefly into the fireplace to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{16.95 spoonful of centrifuged mixture "powder"}.
\item 
Dump the \textbf{9 wet mouths}, \textbf{9.83 spoonful of mug}, \textbf{18.4 ounces of cooled and slightly burned mask} and \textbf{16.95 spoonful of centrifuged mixture "powder"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{face}.
\end{enumerate}
\newpage
\section{A fade}How to make a \textbf{fade} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.67 spoonful of death
\item 
9 disintegrations
\item 
2 vague notions of decrease
\item 
2 stains
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\item 
Freezer
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2 stains} into the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{2 vague notions of decrease} into the freezer for a while.
\item 
Put \textbf{9 disintegrations} into the vessel.
\item 
Put \textbf{7.67 spoonful of death} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Stir the vessel.
\item 
Let the vessel cool down.
\item 
Put \textbf{2 cooled vague notions of decrease} into the freezer for a while.
\item 
Hold \textbf{2 frozen vague notions of decrease} briefly into the fireplace to burn them a bit.
\item 
Retrieve the \textbf{2.83 spoonful of ashes of "stain"} from the fireplace.
\item 
Pour out the mixture from the vessel to get the \textbf{4.05 ounces of vessel mixture "disintegration"}.
\item 
Stop the centrifuge and retrieve the \textbf{593.76 ounces of centrifuged mixture "death"}.
\item 
Dump the \textbf{2 frozen and slightly burned vague notions of decrease}, \textbf{2.83 spoonful of ashes of "stain"}, \textbf{4.05 ounces of vessel mixture "disintegration"} and \textbf{593.76 ounces of centrifuged mixture "death"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{fade}.
\end{enumerate}
\newpage
\section{A fan}How to make a \textbf{fan} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 ceilings
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{5 ceilings} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{5 slightly burned ceilings} into the bonfire.
\item 
Let the container cool down.
\item 
Retrieve the \textbf{7.74 ounces of ashes of "slightly burned ceiling"} from the bonfire.
\item 
Fold the \textbf{7.74 ounces of ashes of "slightly burned ceiling"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{fan}.
\end{enumerate}
\newpage
\section{A fast}How to make a \textbf{fast} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 clear concepts of being brief
\item 
2.4 spoonful of spree
\item 
2 clear concepts of ride
\item 
3.35 spoonful of hunger
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Bucket with ionised water
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2 clear concepts of ride} into the fireplace.
\item 
Put \textbf{2.4 spoonful of spree} into the rotating centrifuge.
\item 
Wait for a short time.
\item 
Grind a little bit of hair from a president to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Dip \textbf{3.35 spoonful of hunger} into the bucket with ionised water.
\item 
Stop the centrifuge and retrieve the \textbf{6.13 ounces of centrifuged mixture "spree"}.
\item 
Put \textbf{6.13 ounces of centrifuged mixture "spree"} into the rotating centrifuge.
\item 
Put \textbf{3.35 spoonful of wet hunger} into the rotating centrifuge.
\item 
Dip \textbf{7 clear concepts of being brief} into the bucket with ionised water.
\item 
Stop the centrifuge and retrieve the \textbf{16.54 spoonful of centrifuged mixture "centrifuged mixture "spree" and wet hunger"}.
\item 
Retrieve the \textbf{26.55 ounces of ashes of "ride"} from the fireplace.
\item 
Fold the \textbf{7 wet clear concepts of being brief}, \textbf{16.54 spoonful of centrifuged mixture "centrifuged mixture "spree" and wet hunger"} and \textbf{26.55 ounces of ashes of "ride"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{fast}.
\end{enumerate}
\newpage
\section{A favorite}How to make a \textbf{favorite} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 ideas of being special
\item 
7 preferences
\item 
34 leasts
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Fireplace
\item 
Container
\item 
Centrifuge
\item 
Pet ape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Pet your pet ape.
\item 
Hold \textbf{7 preferences} briefly into the fireplace to burn them a bit.
\item 
Let the container cool down.
\item 
Put \textbf{7 slightly burned preferences} into the rotating centrifuge.
\item 
Purify \textbf{5 ideas of being special} with the purifier.
\item 
Put \textbf{34 leasts} into the rotating centrifuge.
\item 
Heat the container.
\item 
Stop the centrifuge and retrieve the \textbf{9.66 spoonful of centrifuged mixture "slightly burned preference and least"}.
\item 
Fold the \textbf{5 purified ideas of being special} and \textbf{9.66 spoonful of centrifuged mixture "slightly burned preference and least"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{favorite}.
\end{enumerate}
\newpage
\section{A fawn}How to make a \textbf{fawn} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 does
\item 
2.24 spoonful of deer
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Container
\item 
Freezer
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{2.24 spoonful of deer} into bits.
\item 
Put \textbf{2.24 spoonful of sliced deer} into the freezer for a while.
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Purify \textbf{10 does} with the purifier.
\item 
Heat the container.
\item 
Fold the \textbf{10 purified does} and \textbf{2.24 spoonful of sliced and cooled deer} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{fawn}.
\end{enumerate}
\newpage
\section{A fence}How to make a \textbf{fence} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
36.64 spoonful of thicket
\item 
3.52 ounces of border
\item 
20.41 ounces of roost
\item 
10 gates
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Freezer
\item 
Bucket with liquid
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Dip \textbf{36.64 spoonful of thicket} into the bucket with liquid.
\item 
Use the saw to slice \textbf{3.52 ounces of border} into bits.
\item 
Put \textbf{20.41 ounces of roost} into the freezer for a while.
\item 
Fold the \textbf{36.64 spoonful of wet thicket}, \textbf{3.52 ounces of sliced border}, \textbf{20.41 ounces of cooled roost} and \textbf{10 gates} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{fence}.
\end{enumerate}
\newpage
\section{A florida}How to make a \textbf{florida} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16.2 spoonful of crocodile
\item 
19 tampas
\item 
6.69 ounces of center
\item 
1.74 spoonful of sunshine
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Heat the cauldron.
\item 
Put \textbf{1.74 spoonful of sunshine} into the rotating centrifuge.
\item 
Stir the cauldron.
\item 
Speed up the centrifuge.
\item 
Heat the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{8.51 spoonful of centrifuged mixture "sunshine"}.
\item 
Use nails to join the \textbf{16.2 spoonful of crocodile}, \textbf{19 tampas}, \textbf{6.69 ounces of center} and \textbf{8.51 spoonful of centrifuged mixture "sunshine"} together into the shape of a perfectly functional \textbf{florida}.
\end{enumerate}
\newpage
\section{A foil}How to make a \textbf{foil} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.84 ounces of aluminum
\item 
7 tins
\item 
27 wrappers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Container
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{7 tins} with the stone.
\item 
Wait for 8 minutes.
\item 
Grind a little bit of troll teeth to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Let the container cool down.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a triangle into the circle and place \textbf{4.84 ounces of aluminum}, \textbf{7 smashed tins} and \textbf{27 wrappers} on each corner.
\item 
Chant the following spell: "Butinus monitumuscus! Calceola! Calis! Canome struo euphonubinus!"
\item 
Slowly, a \textbf{foil} will appear inside the circle.
\end{enumerate}
\newpage
\section{A forest}How to make a \textbf{forest} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.09 ounces of raccoon
\item 
26 wildnesses
\item 
2 trees
\item 
8.5 spoonful of wilderness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Vessel
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{26 wildnesses} into the rotating centrifuge.
\item 
Wait for a minute.
\item 
Put \textbf{2.09 ounces of raccoon} into the freezer for a while.
\item 
Eat \textbf{2 trees}.
\item 
Heat the vessel.
\item 
Put \textbf{8.5 spoonful of wilderness} into the rotating centrifuge.
\item 
Wait for 9 hours.
\item 
Put \textbf{2.09 ounces of cooled raccoon} into the vessel.
\item 
Speed up the centrifuge.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{7.39 spoonful of centrifuged mixture "wildness and wilderness"}.
\item 
Pour out the mixture from the vessel to get the \textbf{9.77 spoonful of vessel mixture "cooled raccoon"}.
\item 
Use nails to join the \textbf{7.39 spoonful of centrifuged mixture "wildness and wilderness"} and \textbf{9.77 spoonful of vessel mixture "cooled raccoon"} together into the shape of a passable \textbf{forest}.
\end{enumerate}
\newpage
\section{A fox}How to make a \textbf{fox} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.4 ounces of century
\item 
4.64 spoonful of rabbit
\item 
20.67 spoonful of hound
\item 
8 vague notions of being sly
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Use the saw to slice \textbf{20.67 spoonful of hound} into bits.
\item 
Throw \textbf{4.64 spoonful of rabbit}, \textbf{20.67 spoonful of sliced hound}, \textbf{3.4 ounces of century} and \textbf{8 vague notions of being sly} away.
\item 
Wait.
\item 
Buy a \textbf{fox} on Amazon.
\end{enumerate}
\newpage
\section{A freezer}How to make a \textbf{freezer} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.62 ounces of deicer
\item 
29.2 ounces of refrigerator
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with hot water
\item 
Fireplace
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{29.2 ounces of refrigerator} into the bucket with hot water.
\item 
Put \textbf{7.62 ounces of deicer} into the rotating centrifuge.
\item 
Hold \textbf{29.2 ounces of wet refrigerator} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{29.2 ounces of wet and slightly burned refrigerator} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{9.37 spoonful of centrifuged mixture "deicer and wet and slightly burned refrigerator"}.
\item 
Wait for a rather short time.
\item 
Dip \textbf{9.37 spoonful of centrifuged mixture "deicer and wet and slightly burned refrigerator"} into the bucket with hot water.
\item 
Put \textbf{9.37 spoonful of wet centrifuged mixture "deicer and wet and slightly burned refrigerator"} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.78 ounces of centrifuged mixture "wet centrifuged mixture "deicer and wet and slightly burned refrigerator""}.
\item 
Use glue to join the \textbf{7.78 ounces of centrifuged mixture "wet centrifuged mixture "deicer and wet and slightly burned refrigerator""} together into the form of a perfectly functional \textbf{freezer}.
\end{enumerate}
\newpage
\section{A frost}How to make a \textbf{frost} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.19 ounces of dew
\item 
94 chills
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Bucket with ice-cold liquid
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{94 chills} with the purifier.
\item 
Wait.
\item 
Dip \textbf{6.19 ounces of dew} into the bucket with ice-cold liquid.
\item 
Purify \textbf{6.19 ounces of wet dew} with the purifier.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a line into the circle and place \textbf{6.19 ounces of wet and purified dew} and \textbf{94 purified chills} on each end.
\item 
Intone the following spell: "Defacistator!"
\item 
Slowly, a \textbf{frost} will appear inside the circle.
\end{enumerate}
\newpage
\section{A function}How to make a \textbf{function} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.62 spoonful of computer
\item 
6 physiologies
\item 
46.78 ounces of use
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Centrifuge
\item 
Hammer
\item 
Container
\item 
Bonfire
\item 
Familiar cat
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{6.62 spoonful of computer} with the hammer.
\item 
Feed \textbf{6.62 spoonful of cracked computer} to your familiar cat.
\item 
Let the container cool down.
\item 
Hold \textbf{6 physiologies} briefly into the bonfire to burn them a bit.
\item 
Heat the container.
\item 
Put \textbf{6 slightly burned physiologies} into the rotating centrifuge.
\item 
Let the container cool down.
\item 
Use the saw to slice \textbf{46.78 ounces of use} into bits.
\item 
Heat the container.
\item 
Stop the centrifuge and retrieve the \textbf{4.64 spoonful of centrifuged mixture "slightly burned physiology"}.
\item 
Wait until your familiar cat poops. Receive \textbf{4.66 spoonful of a very dirty pile of "cracked computer"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a triangle into the circle and place \textbf{46.78 ounces of sliced use}, \textbf{4.64 spoonful of centrifuged mixture "slightly burned physiology"} and \textbf{4.66 spoonful of a very dirty pile of "cracked computer"} on each corner.
\item 
Intone the following spell: "Anarulesco!"
\item 
Reluctantly, a \textbf{function} will appear inside the circle.
\end{enumerate}
\newpage
\section{Furniture}How to make \textbf{furniture} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 ideas of move
\item 
3.19 ounces of patio
\item 
5.25 ounces of dust
\item 
3 vague notions of drop
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Put \textbf{3 vague notions of drop} into the rotating centrifuge.
\item 
Put \textbf{5.25 ounces of dust} into the freezer for a while.
\item 
Put \textbf{5 ideas of move} into the container.
\item 
Stop the centrifuge and retrieve the \textbf{44.81 spoonful of centrifuged mixture "drop"}.
\item 
Pour out the mixture from the container to get the \textbf{16.3 ounces of container mixture "move"}.
\item 
Fold the \textbf{3.19 ounces of patio}, \textbf{5.25 ounces of cooled dust}, \textbf{44.81 spoonful of centrifuged mixture "drop"} and \textbf{16.3 ounces of container mixture "move"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in \textbf{furniture}.
\end{enumerate}
\newpage
\section{A fuss}How to make a \textbf{fuss} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.22 spoonful of quarrel
\item 
6.65 spoonful of scolder
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.22 spoonful of quarrel} into the vessel.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{6.65 spoonful of scolder} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{6.65 spoonful of slightly burned scolder} into the vessel.
\item 
Heat the vessel.
\item 
Fan the flames of the fireplace.
\item 
Stir the vessel.
\item 
Wait for a rather long time.
\item 
Pour out the mixture from the vessel to get the \textbf{43.66 spoonful of vessel mixture "quarrel and slightly burned scolder"}.
\item 
Put \textbf{43.66 spoonful of vessel mixture "quarrel and slightly burned scolder"} into the fireplace.
\item 
Retrieve the \textbf{12.4 spoonful of ashes of "vessel mixture "quarrel and slightly burned scolder""} from the fireplace.
\item 
Fold the \textbf{12.4 spoonful of ashes of "vessel mixture "quarrel and slightly burned scolder""} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{fuss}.
\end{enumerate}
\newpage
\section{A fuzz}How to make a \textbf{fuzz} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 lints
\item 
6 peaches
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Bonfire
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{6 peaches} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{28.57 ounces of centrifuged mixture "peach"}.
\item 
Hold \textbf{28.57 ounces of centrifuged mixture "peach"} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{28.57 ounces of slightly burned centrifuged mixture "peach"} into the bonfire.
\item 
Wait.
\item 
Put \textbf{3 lints} into the bonfire.
\item 
Heat the cauldron.
\item 
Retrieve the \textbf{9.48 spoonful of ashes of "slightly burned centrifuged mixture "peach" and lint"} from the bonfire.
\item 
Use nails to join the \textbf{9.48 spoonful of ashes of "slightly burned centrifuged mixture "peach" and lint"} together into the shape of a passable \textbf{fuzz}.
\end{enumerate}
\newpage
\section{A gang}How to make a \textbf{gang} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.02 ounces of mob
\item 
37.42 spoonful of bandanna
\item 
12 crews
\item 
4.24 ounces of chain
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Bucket with clean water
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Dip \textbf{4.24 ounces of chain} into the bucket with clean water.
\item 
Hold \textbf{8.02 ounces of mob} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Use glue to join the \textbf{8.02 ounces of slightly burned mob}, \textbf{37.42 spoonful of bandanna}, \textbf{12 crews} and \textbf{4.24 ounces of wet chain} together into the form of a perfectly functional \textbf{gang}.
\end{enumerate}
\newpage
\section{Garlic}How to make \textbf{garlic} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 vague notions of spice
\item 
13.38 ounces of onion
\item 
25 herbs
\item 
8.58 spoonful of oregano
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Hammer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{3 vague notions of spice} with the hammer.
\item 
Crack \textbf{13.38 ounces of onion} with the hammer.
\item 
Let the container cool down.
\item 
Put \textbf{25 herbs} into the container.
\item 
Pour out the mixture from the container to get the \textbf{7.57 spoonful of container mixture "herb"}.
\item 
Fold the \textbf{3 smashed vague notions of spice}, \textbf{13.38 ounces of cracked onion}, \textbf{8.58 spoonful of oregano} and \textbf{7.57 spoonful of container mixture "herb"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in \textbf{garlic}.
\end{enumerate}
\newpage
\section{A gavel}How to make a \textbf{gavel} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
27.57 ounces of judge
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{27.57 ounces of judge} into the cauldron.
\item 
Fan the flames of the fireplace.
\item 
Heat the cauldron.
\item 
Wait for a short time.
\item 
Pour out the mixture from the cauldron to get the \textbf{11.74 ounces of cauldron mixture "judge"}.
\item 
Put \textbf{11.74 ounces of cauldron mixture "judge"} into the fireplace.
\item 
Heat the cauldron.
\item 
Let the cauldron cool down.
\item 
Retrieve the \textbf{6.49 spoonful of ashes of "cauldron mixture "judge""} from the fireplace.
\item 
Heat the cauldron.
\item 
Dump the \textbf{6.49 spoonful of ashes of "cauldron mixture "judge""} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{gavel}.
\end{enumerate}
\newpage
\section{A geese}How to make a \textbf{geese} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
14.52 ounces of vomit
\item 
10 geese
\item 
5 duck
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Container
\item 
Centrifuge
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{10 geese} into the fireplace.
\item 
Put \textbf{14.52 ounces of vomit} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{5 duck} into bits.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{5 sliced duck} into the fireplace.
\item 
Stir the container.
\item 
Wait for a second.
\item 
Retrieve the \textbf{8.37 ounces of ashes of "goose and sliced ducks"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{6.29 spoonful of centrifuged mixture "vomit"}.
\item 
Fold the \textbf{8.37 ounces of ashes of "goose and sliced ducks"} and \textbf{6.29 spoonful of centrifuged mixture "vomit"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{geese}.
\end{enumerate}
\newpage
\section{A gender}How to make a \textbf{gender} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 sexes
\item 
19.84 spoonful of stereotype
\item 
2 biases
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Container
\item 
Bucket with ionised water
\item 
Bonfire
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Dip \textbf{2 biases} into the bucket with ionised water.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Hold \textbf{2 wet biases} briefly into the bonfire to burn them a bit.
\item 
Dip \textbf{2 wet and slightly burned biases} into the bucket with ionised water.
\item 
Heat the container.
\item 
Crack \textbf{2 sexes} with the stone.
\item 
Hold \textbf{19.84 spoonful of stereotype} briefly into the bonfire to burn them a bit.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a triangle into the circle and place \textbf{2 cracked sexes}, \textbf{19.84 spoonful of slightly burned stereotype} and \textbf{2 very wet and slightly burned biases} on each corner.
\item 
Whisper the following spell: "Parcincum mare cron, zabilis elemodi!"
\item 
Slowly, a \textbf{gender} will appear inside the circle.
\end{enumerate}
\newpage
\section{A geometry}How to make a \textbf{geometry} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.58 spoonful of square
\item 
3 cones
\item 
7 cubes
\item 
7 apexes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Freezer
\item 
Mortar
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Crack \textbf{7 apexes} with the mortar.
\item 
Heat the container.
\item 
Wait.
\item 
Let the container cool down.
\item 
Put \textbf{7 cracked apexes} into the freezer for a while.
\item 
Stir the container.
\item 
Heat the container.
\item 
Put \textbf{3 cones} into the container.
\item 
Pour out the mixture from the container to get the \textbf{3.74 ounces of container mixture "cone"}.
\item 
Use tape to join the \textbf{2.58 spoonful of square}, \textbf{7 cubes}, \textbf{7 cracked and cooled apexes} and \textbf{3.74 ounces of container mixture "cone"} together into the shape of a perfectly functional \textbf{geometry}.
\end{enumerate}
\newpage
\section{A ghetto}How to make a \textbf{ghetto} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.39 ounces of neighborhood
\item 
21.27 spoonful of suburb
\item 
5.28 ounces of slum
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Purifier
\item 
Bucket with ice-cold water
\item 
Fireplace
\item 
Pet chinchilla
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the vessel.
\item 
Hold \textbf{21.27 spoonful of suburb} briefly into the fireplace to burn them a bit.
\item 
Stir the vessel.
\item 
Pet your pet chinchilla.
\item 
Dip \textbf{9.39 ounces of neighborhood} into the bucket with ice-cold water.
\item 
Purify \textbf{5.28 ounces of slum} with the purifier.
\item 
Use glue to join the \textbf{9.39 ounces of wet neighborhood}, \textbf{21.27 spoonful of slightly burned suburb} and \textbf{5.28 ounces of purified slum} together into the shape of a passable \textbf{ghetto}.
\end{enumerate}
\newpage
\section{A giant}How to make a \textbf{giant} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 elves
\item 
16 cyclones
\item 
9 ideas of being large
\item 
9 monsters
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Centrifuge
\item 
Familiar mouse
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let your familiar mouse sniff at \textbf{9 ideas of being large}.
\item 
Purify \textbf{9 ideas of being large} with the purifier.
\item 
Let your familiar mouse lick \textbf{9 purified ideas of being large}.
\item 
Put \textbf{9 monsters} into the rotating centrifuge.
\item 
Put \textbf{9 purified and licked ideas of being large} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.02 ounces of centrifuged mixture "monster and purified and licked being large"}.
\item 
Feed \textbf{4.02 ounces of centrifuged mixture "monster and purified and licked being large"} to your familiar mouse.
\item 
Wait.
\item 
Wait until your familiar mouse poops. Receive \textbf{2.9 ounces of a very dirty pile of "centrifuged mixture "monster and purified and licked being large""}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a triangle into the circle and place \textbf{10 elves}, \textbf{16 cyclones} and \textbf{2.9 ounces of a very dirty pile of "centrifuged mixture "monster and purified and licked being large""} on each corner.
\item 
Intone the following spell: "Tratia adnuntialis liquagium pigro obseratus caustio, minium!"
\item 
Reluctantly, a \textbf{giant} will appear inside the circle.
\end{enumerate}
\newpage
\section{A girl}How to make a \textbf{girl} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 boyfriends
\item 
6.62 ounces of handbag
\item 
1.93 ounces of mary
\item 
4.35 ounces of person
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Saw
\item 
Hammer
\item 
Vessel
\item 
Centrifuge
\item 
Pet hummingbird
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Smash \textbf{9 boyfriends} with the hammer.
\item 
Heat the vessel.
\item 
Use the saw to slice \textbf{1.93 ounces of mary} into bits.
\item 
Stir the vessel.
\item 
Put \textbf{6.62 ounces of handbag} into the bonfire.
\item 
Put \textbf{1.93 ounces of sliced mary} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Feed \textbf{9 smashed boyfriends} to your pet hummingbird.
\item 
Put \textbf{4.35 ounces of person} into the bonfire.
\item 
Retrieve the \textbf{5.46 ounces of ashes of "handbag and person"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{5.94 ounces of centrifuged mixture "sliced mary"}.
\item 
Wait until your pet hummingbird poops. Receive \textbf{4.84 ounces of a very dirty pile of "smashed boyfriend"}.
\item 
Use glue to join the \textbf{5.46 ounces of ashes of "handbag and person"}, \textbf{5.94 ounces of centrifuged mixture "sliced mary"} and \textbf{4.84 ounces of a very dirty pile of "smashed boyfriend"} together into the form of a perfectly functional \textbf{girl}.
\end{enumerate}
\newpage
\section{A glands}How to make a \textbf{glands} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.55 spoonful of sweat
\item 
3 salivas
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Container
\item 
Stone
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.55 spoonful of sweat} into the rotating centrifuge.
\item 
Put \textbf{3 salivas} into the freezer for a while.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Crack \textbf{3 cooled salivas} with the stone.
\item 
Wait for 4 seconds.
\item 
Stop the centrifuge and retrieve the \textbf{1.57 ounces of centrifuged mixture "sweat"}.
\item 
Dump the \textbf{3 cooled and cracked salivas} and \textbf{1.57 ounces of centrifuged mixture "sweat"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{glands}.
\end{enumerate}
\newpage
\section{A glue}How to make a \textbf{glue} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 vague notions of being sticky
\item 
3 bonds
\item 
11.57 ounces of sticker
\item 
11 tapes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Mortar
\item 
Vessel
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Put \textbf{2 vague notions of being sticky} into the vessel.
\item 
Stir the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{3.38 ounces of vessel mixture "being sticky"}.
\item 
Hold \textbf{11 tapes} briefly into the bonfire to burn them a bit.
\item 
Smash \textbf{3 bonds} with the mortar.
\item 
Heat the vessel.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a cross into the circle and place \textbf{3 smashed bonds}, \textbf{11.57 ounces of sticker}, \textbf{11 slightly burned tapes} and \textbf{3.38 ounces of vessel mixture "being sticky"} on each corner.
\item 
Intone the following spell: "Enarchissor eclemblemnia crepantatus, adtonon! Belluvius vesco!"
\item 
Slowly, a \textbf{glue} will appear inside the circle.
\end{enumerate}
\newpage
\section{A grab}How to make a \textbf{grab} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16.04 ounces of tackle
\item 
3 vague notions of snatch
\item 
2 ideas of clench
\item 
23.68 ounces of grip
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with clean liquid
\item 
Bonfire
\item 
Hammer
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Put \textbf{3 vague notions of snatch} into the bonfire.
\item 
Throw \textbf{23.68 ounces of grip} away.
\item 
Crack \textbf{2 ideas of clench} with the hammer.
\item 
Dip \textbf{16.04 ounces of tackle} into the bucket with clean liquid.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{16.04 ounces of wet tackle} into the rotating centrifuge.
\item 
Hold \textbf{2 cracked ideas of clench} briefly into the bonfire to burn them a bit.
\item 
Dip \textbf{2 cracked and slightly burned ideas of clench} into the bucket with clean liquid.
\item 
Stop the centrifuge and retrieve the \textbf{6.35 spoonful of centrifuged mixture "wet tackle"}.
\item 
Retrieve the \textbf{6.03 ounces of ashes of "snatch"} from the bonfire.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a triangle into the circle and place \textbf{2 cracked, slightly burned and wet ideas of clench}, \textbf{6.35 spoonful of centrifuged mixture "wet tackle"} and \textbf{6.03 ounces of ashes of "snatch"} on each corner.
\item 
Whisper the following spell: "Demnatus agnosco inoffulgaris! Galis! Camens naucia trix, poliarum! Direm!"
\item 
Slowly, a \textbf{grab} will appear inside the circle.
\end{enumerate}
\newpage
\section{A grandma}How to make a \textbf{grandma} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
79 vague notions of knit
\item 
7.25 spoonful of quilting
\item 
17 vague notions of being relative
\item 
1.41 ounces of frailness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Bonfire
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.25 spoonful of quilting} into the bonfire.
\item 
Put \textbf{1.41 ounces of frailness} into the bonfire.
\item 
Put \textbf{17 vague notions of being relative} into the bonfire.
\item 
Use the saw to slice \textbf{79 vague notions of knit} into bits.
\item 
Put \textbf{79 sliced vague notions of knit} into the bonfire.
\item 
Retrieve the \textbf{4.94 spoonful of ashes of "quilting, frailness, being relative and sliced knit"} from the bonfire.
\item 
Put \textbf{4.94 spoonful of ashes of "quilting, frailness, being relative and sliced knit"} into the bonfire.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{3.49 spoonful of ashes of "ashes of "quilting, frailness, being relative and sliced knit""} from the bonfire.
\item 
Use the saw to slice \textbf{3.49 spoonful of ashes of "ashes of "quilting, frailness, being relative and sliced knit""} into bits.
\item 
Use tape to join the \textbf{3.49 spoonful of sliced ashes of "ashes of "quilting, frailness, being relative and sliced knit""} together into the form of a beautiful \textbf{grandma}.
\end{enumerate}
\newpage
\section{A half}How to make a \textbf{half} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 clear concepts of being mediocre
\item 
1 vague notion of break
\item 
17 vague notions of cut
\item 
8 percentages
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Mortar
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{5 clear concepts of being mediocre} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{5 slightly burned clear concepts of being mediocre} into the fireplace.
\item 
Hold \textbf{1 vague notion of break} briefly into the fireplace to burn it a bit.
\item 
Hold \textbf{17 vague notions of cut} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{8 percentages} into the fireplace.
\item 
Wait for a rather long time.
\item 
Smash \textbf{1 slightly burned vague notion of break} with the mortar.
\item 
Retrieve the \textbf{37.25 ounces of ashes of "slightly burned being mediocre and percentage"} from the fireplace.
\item 
Dump the \textbf{1 slightly burned and smashed vague notion of break}, \textbf{17 slightly burned vague notions of cut} and \textbf{37.25 ounces of ashes of "slightly burned being mediocre and percentage"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{half}.
\end{enumerate}
\newpage
\section{A harmony}How to make a \textbf{harmony} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
31.04 spoonful of peace
\item 
7 clear concepts of being peaceful
\item 
8.52 spoonful of melody
\item 
2.63 spoonful of agreement
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Cauldron
\item 
Centrifuge
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8.52 spoonful of melody} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{8.1 spoonful of centrifuged mixture "melody"}.
\item 
Put \textbf{7 clear concepts of being peaceful} into the cauldron.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Put \textbf{8.1 spoonful of centrifuged mixture "melody"} into the rotating centrifuge.
\item 
Put \textbf{31.04 spoonful of peace} into the rotating centrifuge.
\item 
Wait.
\item 
Speed up the centrifuge.
\item 
Put \textbf{2.63 spoonful of agreement} into the freezer for a while.
\item 
Pour out the mixture from the cauldron to get the \textbf{4.59 spoonful of cauldron mixture "being peaceful"}.
\item 
Stop the centrifuge and retrieve the \textbf{5.19 ounces of centrifuged mixture "centrifuged mixture "melody" and peace"}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a triangle into the circle and place \textbf{2.63 spoonful of cooled agreement}, \textbf{4.59 spoonful of cauldron mixture "being peaceful"} and \textbf{5.19 ounces of centrifuged mixture "centrifuged mixture "melody" and peace"} on each corner.
\item 
Chant the following spell: "Antatus hanneglutia! Vesco!"
\item 
Reluctantly, a \textbf{harmony} will appear inside the circle.
\end{enumerate}
\newpage
\section{A hawk}How to make a \textbf{hawk} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.37 spoonful of owl
\item 
2 sparrows
\item 
34 preys
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Saw
\item 
Bucket with ionised liquid
\item 
Freezer
\item 
Centrifuge
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{2 sparrows} into the bucket with ionised liquid.
\item 
Put \textbf{34 preys} into the rotating centrifuge.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Put \textbf{2 wet sparrows} into the freezer for a while.
\item 
Use the saw to slice \textbf{8.37 spoonful of owl} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{14.31 ounces of centrifuged mixture "prey"}.
\item 
Use nails to join the \textbf{8.37 spoonful of sliced owl}, \textbf{2 wet and cooled sparrows} and \textbf{14.31 ounces of centrifuged mixture "prey"} together into the form of a beautiful \textbf{hawk}.
\end{enumerate}
\newpage
\section{A heading}How to make a \textbf{heading} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17 titles
\item 
10 directions
\item 
3.47 ounces of label
\item 
1.48 spoonful of caption
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Stone
\item 
Centrifuge
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.48 spoonful of caption} into the freezer for a while.
\item 
Put \textbf{10 directions} into the rotating centrifuge.
\item 
Smash \textbf{17 titles} with the stone.
\item 
Crack \textbf{17 smashed titles} with the stone.
\item 
Stop the centrifuge and retrieve the \textbf{2.43 spoonful of centrifuged mixture "direction"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{17 smashed and cracked titles}, \textbf{3.47 ounces of label}, \textbf{1.48 spoonful of cooled caption} and \textbf{2.43 spoonful of centrifuged mixture "direction"} on each corner.
\item 
Chant the following spell: "Des!"
\item 
Suddendly, a \textbf{heading} will appear inside the circle.
\end{enumerate}
\newpage
\section{A heart}How to make a \textbf{heart} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
226 spades
\item 
8.87 spoonful of attack
\item 
7.02 ounces of liver
\item 
2.64 spoonful of glands
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with clean liquid
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{8.87 spoonful of attack} into bits.
\item 
Wait for a long time.
\item 
Dip \textbf{226 spades} into the bucket with clean liquid.
\item 
Throw \textbf{8.87 spoonful of sliced attack} away.
\item 
Use the saw to slice \textbf{2.64 spoonful of glands} into bits.
\item 
Wait for a rather short time.
\item 
Dip \textbf{226 wet spades} into the bucket with clean liquid.
\item 
Throw \textbf{226 very wet spades}, \textbf{2.64 spoonful of sliced glands} and \textbf{7.02 ounces of liver} away.
\item 
Wait.
\item 
Realise that you never really needed a \textbf{heart}.
\end{enumerate}
\newpage
\section{A hen}How to make a \textbf{hen} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.48 ounces of egg
\item 
2.55 ounces of roost
\item 
10.96 ounces of chick
\item 
3.28 ounces of eggs
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Vessel
\item 
Purifier
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the vessel.
\item 
Wait.
\item 
Purify \textbf{10.96 ounces of chick} with the purifier.
\item 
Put \textbf{3.48 ounces of egg} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Wait.
\item 
Eat \textbf{3.28 ounces of eggs}.
\item 
Stop the centrifuge and retrieve the \textbf{6.61 spoonful of centrifuged mixture "egg"}.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a triangle into the circle and place \textbf{2.55 ounces of roost}, \textbf{10.96 ounces of purified chick} and \textbf{6.61 spoonful of centrifuged mixture "egg"} on each corner.
\item 
Chant the following spell: "Altipor perbenebrate!"
\item 
Suddendly, a \textbf{hen} will appear inside the circle.
\end{enumerate}
\newpage
\section{An herb}How to make an \textbf{herb} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
26 parsleys
\item 
10 cloves
\item 
26.41 ounces of oregano
\item 
7.6 spoonful of smoke
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Purifier
\item 
Bucket with ice-cold water
\item 
Container
\item 
Familiar dog
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{26.41 ounces of oregano} into the container.
\item 
Let your familiar dog lick \textbf{26 parsleys}.
\item 
Put \textbf{26 licked parsleys} into the rotating centrifuge.
\item 
Dip \textbf{10 cloves} into the bucket with ice-cold water.
\item 
Pour out the mixture from the container to get the \textbf{2.56 ounces of container mixture "oregano"}.
\item 
Wait for a rather short time.
\item 
Purify \textbf{7.6 spoonful of smoke} with the purifier.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{14.65 ounces of centrifuged mixture "licked parsley"}.
\item 
Use glue to join the \textbf{10 wet cloves}, \textbf{7.6 spoonful of purified smoke}, \textbf{2.56 ounces of container mixture "oregano"} and \textbf{14.65 ounces of centrifuged mixture "licked parsley"} together into the shape of a passable \textbf{herb}.
\end{enumerate}
\newpage
\section{A hobby}How to make a \textbf{hobby} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.98 spoonful of chore
\item 
9 activities
\item 
10 interests
\item 
5.41 ounces of craft
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9 activities} into the rotating centrifuge.
\item 
Put \textbf{10 interests} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{8.04 ounces of centrifuged mixture "activity and interest"}.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{8.04 ounces of centrifuged mixture "activity and interest"} into the bonfire.
\item 
Retrieve the \textbf{44.72 spoonful of ashes of "centrifuged mixture "activity and interest""} from the bonfire.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a triangle into the circle and place \textbf{3.98 spoonful of chore}, \textbf{5.41 ounces of craft} and \textbf{44.72 spoonful of ashes of "centrifuged mixture "activity and interest""} on each corner.
\item 
Chant the following spell: "Deho cupineus refacifica! Praeeo!"
\item 
Slowly, a \textbf{hobby} will appear inside the circle.
\end{enumerate}
\newpage
\section{A horoscope}How to make a \textbf{horoscope} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.99 spoonful of astrology
\item 
1 leo
\item 
2 periscopes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Saw
\item 
Centrifuge
\item 
Familiar unicorn
\item 
Stone
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{2.99 spoonful of astrology} with the purifier.
\item 
Heat the cauldron.
\item 
Put \textbf{1 leo} into the rotating centrifuge.
\item 
Put \textbf{2.99 spoonful of purified astrology} into the cauldron.
\item 
Let your familiar unicorn sniff at \textbf{2 periscopes}.
\item 
Feed \textbf{2 periscopes} to your familiar unicorn.
\item 
Wait until your familiar unicorn poops. Receive \textbf{14.23 spoonful of a very dirty pile of "periscope"}.
\item 
Heat the cauldron.
\item 
Smash \textbf{14.23 spoonful of a very dirty pile of "periscope"} with the stone.
\item 
Use the saw to slice \textbf{14.23 spoonful of smashed a very dirty pile of "periscope"} into bits.
\item 
Pour out the mixture from the cauldron to get the \textbf{20.71 spoonful of cauldron mixture "purified astrology"}.
\item 
Stop the centrifuge and retrieve the \textbf{8.45 spoonful of centrifuged mixture "leo"}.
\item 
Dump the \textbf{14.23 spoonful of smashed and sliced a very dirty pile of "periscope"}, \textbf{20.71 spoonful of cauldron mixture "purified astrology"} and \textbf{8.45 spoonful of centrifuged mixture "leo"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{horoscope}.
\end{enumerate}
\newpage
\section{A hound}How to make a \textbf{hound} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 wolves
\item 
8 vague notions of being gray
\item 
9.92 spoonful of blood
\item 
3.06 ounces of fox
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{9.92 spoonful of blood} with the mortar.
\item 
Fan the flames of the fireplace.
\item 
Crack \textbf{8 vague notions of being gray} with the mortar.
\item 
Smash \textbf{3.06 ounces of fox} with the mortar.
\item 
Wait for 5 days.
\item 
Dump the \textbf{9 wolves}, \textbf{8 cracked vague notions of being gray}, \textbf{9.92 spoonful of smashed blood} and \textbf{3.06 ounces of smashed fox} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{hound}.
\end{enumerate}
\newpage
\section{An hours}How to make an \textbf{hours} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 severals
\item 
6.65 ounces of minutes
\item 
35 flexiblenesses
\item 
17.09 spoonful of after
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with clean liquid
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2 severals} into the rotating centrifuge.
\item 
Wait for 10 hours.
\item 
Dip \textbf{35 flexiblenesses} into the bucket with clean liquid.
\item 
Put \textbf{17.09 spoonful of after} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.56 spoonful of centrifuged mixture "several and after"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a triangle into the circle and place \textbf{6.65 ounces of minutes}, \textbf{35 wet flexiblenesses} and \textbf{4.56 spoonful of centrifuged mixture "several and after"} on each corner.
\item 
Intone the following spell: "Detrum! N anero grato verno!"
\item 
Slowly, an \textbf{hours} will appear inside the circle.
\end{enumerate}
\newpage
\section{A humiliate}How to make a \textbf{humiliate} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.58 ounces of insult
\item 
6 blockages
\item 
28.38 ounces of shame
\item 
6 degradations
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{6 degradations} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{2.58 ounces of insult} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{28.38 ounces of shame} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{28.38 ounces of slightly burned shame} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{2.58 ounces of slightly burned insult} briefly into the fireplace to burn them a bit.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a square into the circle and place \textbf{2.58 ounces of burned insult}, \textbf{6 blockages}, \textbf{28.38 ounces of burned shame} and \textbf{6 slightly burned degradations} on each corner.
\item 
Chant the following spell: "Anx!"
\item 
Slowly, a \textbf{humiliate} will appear inside the circle.
\end{enumerate}
\newpage
\section{Hydrogen}How to make \textbf{hydrogen} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.47 spoonful of oxygen
\item 
6.79 spoonful of helium
\item 
6.34 ounces of peroxide
\item 
6.25 spoonful of element
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Freezer
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Put \textbf{6.34 ounces of peroxide} into the rotating centrifuge.
\item 
Let the cauldron cool down.
\item 
Put \textbf{6.25 spoonful of element} into the freezer for a while.
\item 
Heat the cauldron.
\item 
Put \textbf{6.79 spoonful of helium} into the rotating centrifuge.
\item 
Put \textbf{6.25 spoonful of cooled element} into the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{3.46 spoonful of centrifuged mixture "peroxide and helium"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{7.99 spoonful of cauldron mixture "cooled element"}.
\item 
Fold the \textbf{3.47 spoonful of oxygen}, \textbf{3.46 spoonful of centrifuged mixture "peroxide and helium"} and \textbf{7.99 spoonful of cauldron mixture "cooled element"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in \textbf{hydrogen}.
\end{enumerate}
\newpage
\section{A hyper}How to make a \textbf{hyper} in 4 easy steps:

\subsection{Materials}\begin{itemize}
\item 
30 clear concepts of being active
\item 
10.55 ounces of rock
\item 
37.22 ounces of anxiety
\item 
7.46 ounces of earnestness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Wait.
\item 
Use glue to join the \textbf{30 clear concepts of being active}, \textbf{10.55 ounces of rock}, \textbf{37.22 ounces of anxiety} and \textbf{7.46 ounces of earnestness} together into the form of a beautiful \textbf{hyper}.
\end{enumerate}
\newpage
\section{An imagination}How to make an \textbf{imagination} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.7 spoonful of creativity
\item 
9.93 ounces of image
\item 
9.44 ounces of pretense
\item 
5.73 spoonful of reality
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Cauldron
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.44 ounces of pretense} into the rotating centrifuge.
\item 
Wait.
\item 
Let the cauldron cool down.
\item 
Put \textbf{9.93 ounces of image} into the cauldron.
\item 
Smash \textbf{5.73 spoonful of reality} with the hammer.
\item 
Speed up the centrifuge.
\item 
Wait for 8 minutes.
\item 
Pour out the mixture from the cauldron to get the \textbf{10.76 spoonful of cauldron mixture "image"}.
\item 
Stop the centrifuge and retrieve the \textbf{19.53 ounces of centrifuged mixture "pretense"}.
\item 
Fold the \textbf{6.7 spoonful of creativity}, \textbf{5.73 spoonful of smashed reality}, \textbf{10.76 spoonful of cauldron mixture "image"} and \textbf{19.53 ounces of centrifuged mixture "pretense"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in an \textbf{imagination}.
\end{enumerate}
\newpage
\section{An inertia}How to make an \textbf{inertia} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 matter
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Freezer
\item 
Vessel
\item 
Hammer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the vessel.
\item 
Put \textbf{1 matter} into the bonfire.
\item 
Let the vessel cool down.
\item 
Wait for a day.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{8.06 ounces of ashes of "matter"} from the bonfire.
\item 
Smash \textbf{8.06 ounces of ashes of "matter"} with the hammer.
\item 
Put \textbf{8.06 ounces of smashed ashes of "matter"} into the freezer for a while.
\item 
Put \textbf{8.06 ounces of smashed and cooled ashes of "matter"} into the bonfire.
\item 
Retrieve the \textbf{3.04 ounces of ashes of "smashed and cooled ashes of "matter""} from the bonfire.
\item 
Dump the \textbf{3.04 ounces of ashes of "smashed and cooled ashes of "matter""} into a pile on the floor.
\item 
Wait until they magically transform into an \textbf{inertia}.
\end{enumerate}
\newpage
\section{An ink}How to make an \textbf{ink} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 squids
\item 
7 newspapers
\item 
8.81 ounces of pen
\item 
1 smear
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Mortar
\item 
Freezer
\item 
Saw
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 smear} into the freezer for a while.
\item 
Wait for a second.
\item 
Use the saw to slice \textbf{8.81 ounces of pen} into bits.
\item 
Purify \textbf{7 newspapers} with the purifier.
\item 
Smash \textbf{8.81 ounces of sliced pen} with the mortar.
\item 
Use nails to join the \textbf{4 squids}, \textbf{7 purified newspapers}, \textbf{8.81 ounces of sliced and smashed pen} and \textbf{1 cooled smear} together into the shape of a perfectly functional \textbf{ink}.
\end{enumerate}
\newpage
\section{An inmate}How to make an \textbf{inmate} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.15 spoonful of primate
\item 
18 cells
\item 
8 prisoners
\item 
6.87 ounces of prison
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Vessel
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8 prisoners} into the vessel.
\item 
Let the vessel cool down.
\item 
Crack \textbf{18 cells} with the mortar.
\item 
Put \textbf{9.15 spoonful of primate} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{2.6 spoonful of vessel mixture "prisoner and primate"}.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a triangle into the circle and place \textbf{18 cracked cells}, \textbf{6.87 ounces of prison} and \textbf{2.6 spoonful of vessel mixture "prisoner and primate"} on each corner.
\item 
Whisper the following spell: "Deprectio gynemodeo fodi, apidarium!"
\item 
Slowly, an \textbf{inmate} will appear inside the circle.
\end{enumerate}
\newpage
\section{Intelligence}How to make \textbf{intelligence} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12 insights
\item 
39.51 ounces of mind
\item 
9.19 spoonful of skill
\item 
17.63 ounces of logic
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{12 insights} into the bonfire.
\item 
Wait for a second.
\item 
Put \textbf{17.63 ounces of logic} into the bonfire.
\item 
Retrieve the \textbf{1.83 ounces of ashes of "insight and logic"} from the bonfire.
\item 
Fold the \textbf{39.51 ounces of mind}, \textbf{9.19 spoonful of skill} and \textbf{1.83 ounces of ashes of "insight and logic"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in \textbf{intelligence}.
\end{enumerate}
\newpage
\section{A jar}How to make a \textbf{jar} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
42.78 spoonful of mason
\item 
39.56 spoonful of flask
\item 
14 bottles
\item 
4 jugs
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Freezer
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Put \textbf{4 jugs} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{42.78 spoonful of mason} into bits.
\item 
Put \textbf{42.78 spoonful of sliced mason} into the freezer for a while.
\item 
Speed up the centrifuge.
\item 
Put \textbf{14 bottles} into the rotating centrifuge.
\item 
Put \textbf{42.78 spoonful of sliced and cooled mason} into the freezer for a while.
\item 
Stop the centrifuge and retrieve the \textbf{20.33 ounces of centrifuged mixture "jug and bottle"}.
\item 
Dump the \textbf{42.78 spoonful of sliced and frozen mason}, \textbf{39.56 spoonful of flask} and \textbf{20.33 ounces of centrifuged mixture "jug and bottle"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{jar}.
\end{enumerate}
\newpage
\section{A jet}How to make a \textbf{jet} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.37 spoonful of airplane
\item 
6.8 ounces of air force
\item 
3.87 ounces of mirage
\item 
8.98 ounces of plane
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bonfire
\item 
Purifier
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{4.37 spoonful of airplane} with the purifier.
\item 
Put \textbf{3.87 ounces of mirage} into the bonfire.
\item 
Put \textbf{4.37 spoonful of purified airplane} into the rotating centrifuge.
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Put \textbf{8.98 ounces of plane} into the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{1.7 spoonful of centrifuged mixture "purified airplane"}.
\item 
Retrieve the \textbf{4.97 spoonful of ashes of "mirage and plane"} from the bonfire.
\item 
Fold the \textbf{6.8 ounces of air force}, \textbf{1.7 spoonful of centrifuged mixture "purified airplane"} and \textbf{4.97 spoonful of ashes of "mirage and plane"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{jet}.
\end{enumerate}
\newpage
\section{A journal}How to make a \textbf{journal} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
23.35 ounces of newspaper
\item 
3 diaries
\item 
7.7 spoonful of dairy
\item 
2.81 spoonful of editorial
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Saw
\item 
Bucket with clean liquid
\item 
Stone
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{23.35 ounces of newspaper} into the bonfire.
\item 
Dip \textbf{7.7 spoonful of dairy} into the bucket with clean liquid.
\item 
Retrieve the \textbf{9.53 spoonful of ashes of "newspaper"} from the bonfire.
\item 
Crack \textbf{9.53 spoonful of ashes of "newspaper"} with the stone.
\item 
Use the saw to slice \textbf{2.81 spoonful of editorial} into bits.
\item 
Dip \textbf{9.53 spoonful of cracked ashes of "newspaper"} into the bucket with clean liquid.
\item 
Smash \textbf{3 diaries} with the stone.
\item 
Wait for 3 seconds.
\item 
Crack \textbf{2.81 spoonful of sliced editorial} with the stone.
\item 
Use the saw to slice \textbf{3 smashed diaries} into bits.
\item 
Fold the \textbf{3 smashed and sliced diaries}, \textbf{7.7 spoonful of wet dairy}, \textbf{2.81 spoonful of sliced and cracked editorial} and \textbf{9.53 spoonful of cracked and wet ashes of "newspaper"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{journal}.
\end{enumerate}
\newpage
\section{A knife}How to make a \textbf{knife} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.84 spoonful of weapon
\item 
26.79 spoonful of dullness
\item 
4 surgeons
\item 
7 clear concepts of hunting
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Cauldron
\item 
Centrifuge
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Put \textbf{26.79 spoonful of dullness} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{4 surgeons} into bits.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{2.56 spoonful of centrifuged mixture "dullness"}.
\item 
Put \textbf{2.56 spoonful of centrifuged mixture "dullness"} into the rotating centrifuge.
\item 
Put \textbf{4 sliced surgeons} into the rotating centrifuge.
\item 
Wait for a very short time.
\item 
Stop the centrifuge and retrieve the \textbf{22.76 ounces of centrifuged mixture "centrifuged mixture "dullness" and sliced surgeon"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a triangle into the circle and place \textbf{3.84 spoonful of weapon}, \textbf{7 clear concepts of hunting} and \textbf{22.76 ounces of centrifuged mixture "centrifuged mixture "dullness" and sliced surgeon"} on each corner.
\item 
Whisper the following spell: "Comminatus!"
\item 
Slowly, a \textbf{knife} will appear inside the circle.
\end{enumerate}
\newpage
\section{A knot}How to make a \textbf{knot} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.49 ounces of tie
\item 
9.04 ounces of string
\item 
5.04 spoonful of loop
\item 
9 ropes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Pet chinchilla
\item 
Centrifuge
\item 
Cauldron
\item 
Hammer
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for 3 seconds.
\item 
Let your pet chinchilla lick \textbf{5.04 spoonful of loop}.
\item 
Crack \textbf{9 ropes} with the hammer.
\item 
Smash \textbf{7.49 ounces of tie} with the hammer.
\item 
Put \textbf{5.04 spoonful of licked loop} into the rotating centrifuge.
\item 
Heat the cauldron.
\item 
Feed \textbf{7.49 ounces of smashed tie} to your pet chinchilla.
\item 
Pet your pet chinchilla.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Wait until your pet chinchilla poops. Receive \textbf{9.59 ounces of a very dirty pile of "smashed tie"}.
\item 
Stop the centrifuge and retrieve the \textbf{37.83 ounces of centrifuged mixture "licked loop"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a square into the circle and place \textbf{9.04 ounces of string}, \textbf{9 cracked ropes}, \textbf{9.59 ounces of a very dirty pile of "smashed tie"} and \textbf{37.83 ounces of centrifuged mixture "licked loop"} on each corner.
\item 
Whisper the following spell: "Auctio aprunculus! Sauculla colluscus bulus! Pitis recetrator chamarrhum craticus seceptorium!"
\item 
Slowly, a \textbf{knot} will appear inside the circle.
\end{enumerate}
\newpage
\section{A lap}How to make a \textbf{lap} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
52.7 spoonful of napkin
\item 
6 vague notions of sitting
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{52.7 spoonful of napkin} into the bonfire.
\item 
Put \textbf{6 vague notions of sitting} into the rotating centrifuge.
\item 
Retrieve the \textbf{9.39 spoonful of ashes of "napkin"} from the bonfire.
\item 
Put \textbf{9.39 spoonful of ashes of "napkin"} into the bonfire.
\item 
Fan the flames of the bonfire.
\item 
Speed up the centrifuge.
\item 
Wait.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{5.31 spoonful of ashes of "ashes of "napkin""} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{16.29 spoonful of centrifuged mixture "sitting"}.
\item 
Use screws to join the \textbf{5.31 spoonful of ashes of "ashes of "napkin""} and \textbf{16.29 spoonful of centrifuged mixture "sitting"} together into the form of a beautiful \textbf{lap}.
\end{enumerate}
\newpage
\section{A laser}How to make a \textbf{laser} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 ray
\item 
2 disintegrations
\item 
2.98 spoonful of beam
\item 
11.44 spoonful of disc
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Hammer
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{11.44 spoonful of disc} with the hammer.
\item 
Stir the cauldron.
\item 
Smash \textbf{1 ray} with the hammer.
\item 
Use the saw to slice \textbf{2 disintegrations} into bits.
\item 
Put \textbf{2.98 spoonful of beam} into the rotating centrifuge.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Stop the centrifuge and retrieve the \textbf{7.86 ounces of centrifuged mixture "beam"}.
\item 
Fold the \textbf{1 smashed ray}, \textbf{2 sliced disintegrations}, \textbf{11.44 spoonful of cracked disc} and \textbf{7.86 ounces of centrifuged mixture "beam"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{laser}.
\end{enumerate}
\newpage
\section{A laws}How to make a \textbf{laws} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.05 ounces of regulations
\item 
46.44 spoonful of legislature
\item 
5.41 spoonful of governor
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Hammer
\item 
Saw
\item 
Bucket with water
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{4.05 ounces of regulations} into bits.
\item 
Stir the cauldron.
\item 
Put \textbf{5.41 spoonful of governor} into the freezer for a while.
\item 
Dip \textbf{46.44 spoonful of legislature} into the bucket with water.
\item 
Smash \textbf{46.44 spoonful of wet legislature} with the hammer.
\item 
Put \textbf{5.41 spoonful of cooled governor} into the freezer for a while.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Dump the \textbf{4.05 ounces of sliced regulations}, \textbf{46.44 spoonful of wet and smashed legislature} and \textbf{5.41 spoonful of frozen governor} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{laws}.
\end{enumerate}
\newpage
\section{A lawsuit}How to make a \textbf{lawsuit} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12 ideas of sue
\item 
39.15 ounces of lawyer
\item 
9 libels
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Vessel
\item 
Fireplace
\item 
Bucket with hot liquid
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{39.15 ounces of lawyer} into the rotating centrifuge.
\item 
Dip \textbf{9 libels} into the bucket with hot liquid.
\item 
Let the vessel cool down.
\item 
Put \textbf{9 wet libels} into the fireplace.
\item 
Hold \textbf{12 ideas of sue} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{12 slightly burned ideas of sue} into the vessel.
\item 
Retrieve the \textbf{9.57 spoonful of ashes of "wet libel"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{36.82 spoonful of centrifuged mixture "lawyer"}.
\item 
Pour out the mixture from the vessel to get the \textbf{8.37 spoonful of vessel mixture "slightly burned sue"}.
\item 
Fold the \textbf{9.57 spoonful of ashes of "wet libel"}, \textbf{36.82 spoonful of centrifuged mixture "lawyer"} and \textbf{8.37 spoonful of vessel mixture "slightly burned sue"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{lawsuit}.
\end{enumerate}
\newpage
\section{A layer}How to make a \textbf{layer} in 4 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 bricks
\item 
5.13 ounces of zone
\item 
9 ozones
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Familiar ape
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{5.13 ounces of zone} briefly into the bonfire to burn them a bit.
\item 
Let your familiar ape sniff at \textbf{5.13 ounces of slightly burned zone}.
\item 
Fold the \textbf{8 bricks}, \textbf{5.13 ounces of slightly burned zone} and \textbf{9 ozones} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{layer}.
\end{enumerate}
\newpage
\section{A leaf}How to make a \textbf{leaf} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.38 ounces of brown
\item 
19.55 ounces of lettuce
\item 
43 spinaches
\item 
41.41 spoonful of fig
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{43 spinaches} into the rotating centrifuge.
\item 
Put \textbf{41.41 spoonful of fig} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Put \textbf{6.38 ounces of brown} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{6.3 ounces of centrifuged mixture "spinach, fig and brown"}.
\item 
Put \textbf{19.55 ounces of lettuce} into the rotating centrifuge.
\item 
Dump the \textbf{6.3 ounces of centrifuged mixture "spinach, fig and brown"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{leaf}.
\end{enumerate}
\newpage
\section{A liberal}How to make a \textbf{liberal} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 democrats
\item 
9.79 ounces of arts
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4 democrats} into the rotating centrifuge.
\item 
Put \textbf{9.79 ounces of arts} into the fireplace.
\item 
Retrieve the \textbf{6.49 ounces of ashes of "arts"} from the fireplace.
\item 
Put \textbf{6.49 ounces of ashes of "arts"} into the fireplace.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{2.17 spoonful of centrifuged mixture "democrat"}.
\item 
Purify \textbf{2.17 spoonful of centrifuged mixture "democrat"} with the purifier.
\item 
Put \textbf{2.17 spoonful of purified centrifuged mixture "democrat"} into the rotating centrifuge.
\item 
Wait for a day.
\item 
Stop the centrifuge and retrieve the \textbf{4.25 ounces of centrifuged mixture "purified centrifuged mixture "democrat""}.
\item 
Retrieve the \textbf{26.72 ounces of ashes of "ashes of "arts""} from the fireplace.
\item 
Fold the \textbf{4.25 ounces of centrifuged mixture "purified centrifuged mixture "democrat""} and \textbf{26.72 ounces of ashes of "ashes of "arts""} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{liberal}.
\end{enumerate}
\newpage
\section{A limb}How to make a \textbf{limb} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
43 arms
\item 
3.18 spoonful of stub
\item 
6.54 spoonful of appendage
\item 
4 trees
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Put \textbf{3.18 spoonful of stub} into the cauldron.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Wait for a second.
\item 
Pour out the mixture from the cauldron to get the \textbf{1.36 spoonful of cauldron mixture "stub"}.
\item 
Stir the cauldron.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{43 arms}, \textbf{6.54 spoonful of appendage}, \textbf{4 trees} and \textbf{1.36 spoonful of cauldron mixture "stub"} on each corner.
\item 
Whisper the following spell: "Cucuria bicumvirion!"
\item 
Reluctantly, a \textbf{limb} will appear inside the circle.
\end{enumerate}
\newpage
\section{A limit}How to make a \textbf{limit} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 ideas of being extreme
\item 
3 restrictions
\item 
45.8 spoonful of capacity
\item 
4.28 ounces of speed
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Familiar chinchilla
\item 
Container
\item 
Purifier
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{3 restrictions} with the purifier.
\item 
Feed \textbf{3 purified restrictions} to your familiar chinchilla.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Put \textbf{9 ideas of being extreme} into the container.
\item 
Feed \textbf{45.8 spoonful of capacity} to your familiar chinchilla.
\item 
Let your familiar chinchilla sniff at \textbf{4.28 ounces of speed}.
\item 
Heat the container.
\item 
Wait until your familiar chinchilla poops. Receive \textbf{4.63 ounces of a very dirty pile of "purified restriction and capacity"}.
\item 
Put \textbf{4.63 ounces of a very dirty pile of "purified restriction and capacity"} into the container.
\item 
Pour out the mixture from the container to get the \textbf{5.18 ounces of container mixture "being extreme and a very dirty pile of "purified restriction and capacity""}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a line into the circle and place \textbf{4.28 ounces of speed} and \textbf{5.18 ounces of container mixture "being extreme and a very dirty pile of "purified restriction and capacity""} on each end.
\item 
Chant the following spell: "Collelico inthonus sentia! Inter invice cite, sicius! Aus invice! Mono adstris! Tendomilla!"
\item 
Slowly, a \textbf{limit} will appear inside the circle.
\end{enumerate}
\newpage
\section{A loaf}How to make a \textbf{loaf} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
19 meats
\item 
4.15 ounces of bread
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{4.15 ounces of bread} with the hammer.
\item 
Crack \textbf{4.15 ounces of smashed bread} with the hammer.
\item 
Grind a little bit of bat wings to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Wait.
\item 
Crack \textbf{19 meats} with the hammer.
\item 
Fold the \textbf{19 cracked meats} and \textbf{4.15 ounces of smashed and cracked bread} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{loaf}.
\end{enumerate}
\newpage
\section{A lobe}How to make a \textbf{lobe} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
29.5 ounces of ear
\item 
6.51 ounces of earring
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{6.51 ounces of earring} into the rotating centrifuge.
\item 
Wait for a short time.
\item 
Pick up \textbf{29.5 ounces of ear}. Turn them around. Look at them from every every side. Shake your head dissatisfied. Put them back.
\item 
Speed up the centrifuge.
\item 
Put \textbf{29.5 ounces of ear} into the rotating centrifuge.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{19.16 spoonful of centrifuged mixture "earring and ear"}.
\item 
Dump the \textbf{19.16 spoonful of centrifuged mixture "earring and ear"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{lobe}.
\end{enumerate}
\newpage
\section{A lollipop}How to make a \textbf{lollipop} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 clear concepts of suck
\item 
4.72 spoonful of succor
\item 
8.38 spoonful of lap
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8.38 spoonful of lap} into the rotating centrifuge.
\item 
Put \textbf{3 clear concepts of suck} into the rotating centrifuge.
\item 
Purify \textbf{4.72 spoonful of succor} with the purifier.
\item 
Stop the centrifuge and retrieve the \textbf{15.27 ounces of centrifuged mixture "lap and suck"}.
\item 
Put \textbf{15.27 ounces of centrifuged mixture "lap and suck"} into the rotating centrifuge.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{1.48 spoonful of centrifuged mixture "centrifuged mixture "lap and suck""}.
\item 
Fold the \textbf{4.72 spoonful of purified succor} and \textbf{1.48 spoonful of centrifuged mixture "centrifuged mixture "lap and suck""} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{lollipop}.
\end{enumerate}
\newpage
\section{A lubricate}How to make a \textbf{lubricate} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 greases
\item 
3.33 spoonful of oil
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{3 greases} with the mortar.
\item 
Use the saw to slice \textbf{3 cracked greases} into bits.
\item 
Smash \textbf{3 cracked and sliced greases} with the mortar.
\item 
Crack \textbf{3 cracked, sliced and smashed greases} with the mortar.
\item 
Use the saw to slice \textbf{3 crushed, sliced and smashed greases} into bits.
\item 
Smash \textbf{3.33 spoonful of oil} with the mortar.
\item 
Crack \textbf{3.33 spoonful of smashed oil} with the mortar.
\item 
Wait for a very short time.
\item 
Smash \textbf{3 crushed, fragmented and smashed greases} with the mortar.
\item 
Use the saw to slice \textbf{3.33 spoonful of smashed and cracked oil} into bits.
\item 
Dump the \textbf{3 crushed, fragmented and pulverized greases} and \textbf{3.33 spoonful of smashed, cracked and sliced oil} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{lubricate}.
\end{enumerate}
\newpage
\section{A luxury}How to make a \textbf{luxury} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 pleasures
\item 
8.84 spoonful of wealth
\item 
6.46 spoonful of limousine
\item 
9.28 ounces of elegance
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Purifier
\item 
Container
\item 
Bonfire
\item 
Centrifuge
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3 pleasures} into the freezer for a while.
\item 
Put \textbf{6.46 spoonful of limousine} into the bonfire.
\item 
Smash \textbf{8.84 spoonful of wealth} with the hammer.
\item 
Put \textbf{9.28 ounces of elegance} into the bonfire.
\item 
Put \textbf{8.84 spoonful of smashed wealth} into the rotating centrifuge.
\item 
Hold \textbf{3 cooled pleasures} briefly into the bonfire to burn them a bit.
\item 
Let the container cool down.
\item 
Purify \textbf{3 cooled and slightly burned pleasures} with the purifier.
\item 
Put \textbf{3 cooled, slightly burned and purified pleasures} into the freezer for a while.
\item 
Retrieve the \textbf{3.38 spoonful of ashes of "limousine and elegance"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{5.09 spoonful of centrifuged mixture "smashed wealth"}.
\item 
Fold the \textbf{3 frozen, slightly burned and purified pleasures}, \textbf{3.38 spoonful of ashes of "limousine and elegance"} and \textbf{5.09 spoonful of centrifuged mixture "smashed wealth"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{luxury}.
\end{enumerate}
\newpage
\section{A majority}How to make a \textbf{majority} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.96 spoonful of minority
\item 
12 mosts
\item 
11 vague notions of being vast
\item 
28 democracies
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Bucket with clean liquid
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{12 mosts} into bits.
\item 
Crack \textbf{28 democracies} with the hammer.
\item 
Dip \textbf{8.96 spoonful of minority} into the bucket with clean liquid.
\item 
Use the saw to slice \textbf{8.96 spoonful of wet minority} into bits.
\item 
Crack \textbf{12 sliced mosts} with the hammer.
\item 
Smash \textbf{11 vague notions of being vast} with the hammer.
\item 
Fold the \textbf{8.96 spoonful of wet and sliced minority}, \textbf{12 sliced and cracked mosts}, \textbf{11 smashed vague notions of being vast} and \textbf{28 cracked democracies} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{majority}.
\end{enumerate}
\newpage
\section{A margin}How to make a \textbf{margin} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 profits
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Let the cauldron cool down.
\item 
Put \textbf{10 profits} into the cauldron.
\item 
Wait for 3 seconds.
\item 
Pour out the mixture from the cauldron to get the \textbf{28.01 spoonful of cauldron mixture "profit"}.
\item 
Use screws to join the \textbf{28.01 spoonful of cauldron mixture "profit"} together into the shape of a perfectly functional \textbf{margin}.
\end{enumerate}
\newpage
\section{A market}How to make a \textbf{market} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12 stores
\item 
1 stock
\item 
33.63 ounces of sales
\item 
10 fashions
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Freezer
\item 
Centrifuge
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{12 stores} into the freezer for a while.
\item 
Put \textbf{10 fashions} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{3.11 ounces of centrifuged mixture "fashion"}.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a square into the circle and place \textbf{12 cooled stores}, \textbf{1 stock}, \textbf{33.63 ounces of sales} and \textbf{3.11 ounces of centrifuged mixture "fashion"} on each corner.
\item 
Whisper the following spell: "Pros prodio accatarius, paristivus!"
\item 
Reluctantly, a \textbf{market} will appear inside the circle.
\end{enumerate}
\newpage
\section{A meet}How to make a \textbf{meet} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.68 ounces of place
\item 
7.18 ounces of engagement
\item 
5 attenders
\item 
10 strangers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Mortar
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{5 attenders} with the mortar.
\item 
Smash \textbf{7.18 ounces of engagement} with the mortar.
\item 
Put \textbf{6.68 ounces of place} into the cauldron.
\item 
Let the cauldron cool down.
\item 
Pour out the mixture from the cauldron to get the \textbf{6.3 spoonful of cauldron mixture "place"}.
\item 
Fold the \textbf{7.18 ounces of smashed engagement}, \textbf{5 cracked attenders}, \textbf{10 strangers} and \textbf{6.3 spoonful of cauldron mixture "place"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{meet}.
\end{enumerate}
\newpage
\section{A method}How to make a \textbf{method} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.66 ounces of plan
\item 
5 sciences
\item 
16.76 spoonful of system
\item 
4.99 spoonful of how
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Vessel
\item 
Freezer
\item 
Bucket with hot liquid
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4.99 spoonful of how} into the freezer for a while.
\item 
Put \textbf{4.99 spoonful of cooled how} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.38 ounces of centrifuged mixture "cooled how"}.
\item 
Put \textbf{5 sciences} into the freezer for a while.
\item 
Fan the flames of the bonfire.
\item 
Dip \textbf{16.76 spoonful of system} into the bucket with hot liquid.
\item 
Put \textbf{16.76 spoonful of wet system} into the rotating centrifuge.
\item 
Put \textbf{5 cooled sciences} into the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{6.69 ounces of centrifuged mixture "wet system"}.
\item 
Pour out the mixture from the vessel to get the \textbf{9.62 ounces of vessel mixture "cooled science"}.
\item 
Fold the \textbf{2.66 ounces of plan}, \textbf{4.38 ounces of centrifuged mixture "cooled how"}, \textbf{6.69 ounces of centrifuged mixture "wet system"} and \textbf{9.62 ounces of vessel mixture "cooled science"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{method}.
\end{enumerate}
\newpage
\section{A metric}How to make a \textbf{metric} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.15 spoonful of kilometer
\item 
17 measurements
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Purifier
\item 
Centrifuge
\item 
Vessel
\item 
Hammer
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3.15 spoonful of kilometer} into the rotating centrifuge.
\item 
Purify \textbf{17 measurements} with the purifier.
\item 
Wait for an hour.
\item 
Use the saw to slice \textbf{17 purified measurements} into bits.
\item 
Heat the vessel.
\item 
Crack \textbf{17 purified and sliced measurements} with the hammer.
\item 
Stop the centrifuge and retrieve the \textbf{44.61 ounces of centrifuged mixture "kilometer"}.
\item 
Use glue to join the \textbf{17 purified, sliced and cracked measurements} and \textbf{44.61 ounces of centrifuged mixture "kilometer"} together into the form of a perfectly functional \textbf{metric}.
\end{enumerate}
\newpage
\section{A microwave}How to make a \textbf{microwave} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17.63 spoonful of refrigerator
\item 
3.07 spoonful of oven
\item 
10 appliances
\item 
9.42 spoonful of tupperware
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Centrifuge
\item 
Bonfire
\item 
Pet mouse
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{10 appliances} with the purifier.
\item 
Hold \textbf{9.42 spoonful of tupperware} briefly into the bonfire to burn them a bit.
\item 
Let your pet mouse sniff at \textbf{10 purified appliances}.
\item 
Put \textbf{9.42 spoonful of slightly burned tupperware} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{4.6 spoonful of centrifuged mixture "slightly burned tupperware"}.
\item 
Dump the \textbf{17.63 spoonful of refrigerator}, \textbf{3.07 spoonful of oven}, \textbf{10 purified appliances} and \textbf{4.6 spoonful of centrifuged mixture "slightly burned tupperware"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{microwave}.
\end{enumerate}
\newpage
\section{A might}How to make a \textbf{might} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 maybes
\item 
3.21 spoonful of inclination
\item 
4 probabilities
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4 probabilities} into the rotating centrifuge.
\item 
Put \textbf{3.21 spoonful of inclination} into the rotating centrifuge.
\item 
Wait.
\item 
Pick up \textbf{9 maybes}. Turn them around. Look at them from every every side. Shake your head with disgust. Put them back.
\item 
Purify \textbf{9 maybes} with the purifier.
\item 
Put \textbf{9 purified maybes} into the rotating centrifuge.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{9.73 spoonful of centrifuged mixture "probability, inclination and purified maybe"}.
\item 
Put \textbf{9.73 spoonful of centrifuged mixture "probability, inclination and purified maybe"} into the rotating centrifuge.
\item 
Turn around. You will find that a \textbf{might} was there all along.
\end{enumerate}
\newpage
\section{A migraine}How to make a \textbf{migraine} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.62 spoonful of headache
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\item 
Pet ape
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Stir the vessel.
\item 
Put \textbf{4.62 spoonful of headache} into the fireplace.
\item 
Pet your pet ape.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Fan the flames of the fireplace.
\item 
Pet your pet ape.
\item 
Retrieve the \textbf{8.16 ounces of ashes of "headache"} from the fireplace.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Place \textbf{8.16 ounces of ashes of "headache"} into the circle.
\item 
Whisper the following spell: "Treus resco!"
\item 
Slowly, a \textbf{migraine} will appear inside the circle.
\end{enumerate}
\newpage
\section{A mile}How to make a \textbf{mile} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
19.6 spoonful of marker
\item 
1.6 ounces of kilometer
\item 
9 distances
\item 
48 yards
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Purifier
\item 
Freezer
\item 
Bucket with clean liquid
\item 
Mortar
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{19.6 spoonful of marker} into the freezer for a while.
\item 
Crack \textbf{1.6 ounces of kilometer} with the mortar.
\item 
Purify \textbf{9 distances} with the purifier.
\item 
Smash \textbf{19.6 spoonful of cooled marker} with the mortar.
\item 
Crack \textbf{48 yards} with the mortar.
\item 
Use the saw to slice \textbf{9 purified distances} into bits.
\item 
Dip \textbf{19.6 spoonful of cooled and smashed marker} into the bucket with clean liquid.
\item 
Purify \textbf{19.6 spoonful of cooled, smashed and wet marker} with the purifier.
\item 
Crack \textbf{48 cracked yards} with the mortar.
\item 
Use tape to join the \textbf{19.6 spoonful of cooled, smashed, wet and purified marker}, \textbf{1.6 ounces of cracked kilometer}, \textbf{9 purified and sliced distances} and \textbf{48 crushed yards} together into the form of a usable \textbf{mile}.
\end{enumerate}
\newpage
\section{A misses}How to make a \textbf{misses} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 misses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Centrifuge
\item 
Bonfire
\item 
Familiar cat
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let your familiar cat sniff at \textbf{10 misses}.
\item 
Smash \textbf{10 misses} with the mortar.
\item 
Put \textbf{10 smashed misses} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Wait.
\item 
Pet your familiar cat.
\item 
Fan the flames of the bonfire.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{38.52 ounces of centrifuged mixture "smashed miss"}.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Place \textbf{38.52 ounces of centrifuged mixture "smashed miss"} into the circle.
\item 
Whisper the following spell: "Dedulter!"
\item 
Reluctantly, a \textbf{misses} will appear inside the circle.
\end{enumerate}
\newpage
\section{A mom}How to make a \textbf{mom} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17 vague notions of being lenient
\item 
9 clear concepts of cooking
\item 
4.04 ounces of pop
\item 
6 vague notions of sue
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ice-cold water
\item 
Centrifuge
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for an hour.
\item 
Put \textbf{6 vague notions of sue} into the rotating centrifuge.
\item 
Dip \textbf{9 clear concepts of cooking} into the bucket with ice-cold water.
\item 
Purify \textbf{9 wet clear concepts of cooking} with the purifier.
\item 
Stop the centrifuge and retrieve the \textbf{22.08 spoonful of centrifuged mixture "sue"}.
\item 
Wait.
\item 
Put \textbf{22.08 spoonful of centrifuged mixture "sue"} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{13.8 ounces of centrifuged mixture "centrifuged mixture "sue""}.
\item 
Dump the \textbf{17 vague notions of being lenient}, \textbf{9 wet and purified clear concepts of cooking}, \textbf{4.04 ounces of pop} and \textbf{13.8 ounces of centrifuged mixture "centrifuged mixture "sue""} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{mom}.
\end{enumerate}
\newpage
\section{A mood}How to make a \textbf{mood} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.36 spoonful of hostility
\item 
8 depressions
\item 
15.14 spoonful of attitude
\item 
6.19 ounces of behavior
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Bucket with liquid
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{8 depressions} into the bucket with liquid.
\item 
Put \textbf{6.19 ounces of behavior} into the rotating centrifuge.
\item 
Put \textbf{8.36 spoonful of hostility} into the rotating centrifuge.
\item 
Hold \textbf{15.14 spoonful of attitude} briefly into the bonfire to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{9.1 ounces of centrifuged mixture "behavior and hostility"}.
\item 
Dump the \textbf{8 wet depressions}, \textbf{15.14 spoonful of slightly burned attitude} and \textbf{9.1 ounces of centrifuged mixture "behavior and hostility"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{mood}.
\end{enumerate}
\newpage
\section{A moose}How to make a \textbf{moose} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
27.76 spoonful of elk
\item 
11.92 ounces of antlers
\item 
1.95 spoonful of lodge
\item 
8.6 ounces of bison
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Purifier
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{27.76 spoonful of elk} into the rotating centrifuge.
\item 
Purify \textbf{8.6 ounces of bison} with the purifier.
\item 
Speed up the centrifuge.
\item 
Put \textbf{8.6 ounces of purified bison} into the rotating centrifuge.
\item 
Hold \textbf{1.95 spoonful of lodge} briefly into the bonfire to burn them a bit.
\item 
Purify \textbf{11.92 ounces of antlers} with the purifier.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.47 ounces of centrifuged mixture "elk and purified bison"}.
\item 
Dump the \textbf{11.92 ounces of purified antlers}, \textbf{1.95 spoonful of slightly burned lodge} and \textbf{1.47 ounces of centrifuged mixture "elk and purified bison"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{moose}.
\end{enumerate}
\newpage
\section{A muck}How to make a \textbf{muck} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 marshes
\item 
8.27 spoonful of swamp
\item 
9.47 ounces of goo
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with liquid
\item 
Purifier
\item 
Freezer
\item 
Cauldron
\item 
Stone
\item 
Bonfire
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the cauldron cool down.
\item 
Dip \textbf{9.47 ounces of goo} into the bucket with liquid.
\item 
Fan the flames of the bonfire.
\item 
Smash \textbf{6 marshes} with the stone.
\item 
Put \textbf{8.27 spoonful of swamp} into the rotating centrifuge.
\item 
Put \textbf{9.47 ounces of wet goo} into the cauldron.
\item 
Stir the cauldron.
\item 
Purify \textbf{6 smashed marshes} with the purifier.
\item 
Put \textbf{6 smashed and purified marshes} into the freezer for a while.
\item 
Stop the centrifuge and retrieve the \textbf{1.83 ounces of centrifuged mixture "swamp"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{3.18 ounces of cauldron mixture "wet goo"}.
\item 
Use screws to join the \textbf{6 smashed, purified and cooled marshes}, \textbf{1.83 ounces of centrifuged mixture "swamp"} and \textbf{3.18 ounces of cauldron mixture "wet goo"} together into the form of a perfectly functional \textbf{muck}.
\end{enumerate}
\newpage
\section{A mummy}How to make a \textbf{mummy} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
62 curses
\item 
31 tombs
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised liquid
\item 
Centrifuge
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{31 tombs} into the bucket with ionised liquid.
\item 
Wait.
\item 
Put \textbf{62 curses} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{117.08 spoonful of centrifuged mixture "curse"}.
\item 
Dip \textbf{117.08 spoonful of centrifuged mixture "curse"} into the bucket with ionised liquid.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a line into the circle and place \textbf{31 wet tombs} and \textbf{117.08 spoonful of wet centrifuged mixture "curse"} on each end.
\item 
Whisper the following spell: "Inetrabilis officieo acquiribo, anniterullus!"
\item 
Slowly, a \textbf{mummy} will appear inside the circle.
\end{enumerate}
\newpage
\section{A neglect}How to make a \textbf{neglect} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.29 spoonful of care
\item 
4 diligences
\item 
1 renunciation
\item 
52 disregards
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Fireplace
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 renunciation} into the fireplace.
\item 
Put \textbf{5.29 spoonful of care} into the rotating centrifuge.
\item 
Wait.
\item 
Retrieve the \textbf{30.45 spoonful of ashes of "renunciation"} from the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Crack \textbf{30.45 spoonful of ashes of "renunciation"} with the mortar.
\item 
Smash \textbf{4 diligences} with the mortar.
\item 
Put \textbf{30.45 spoonful of cracked ashes of "renunciation"} into the rotating centrifuge.
\item 
Put \textbf{4 smashed diligences} into the fireplace.
\item 
Put \textbf{52 disregards} into the rotating centrifuge.
\item 
Retrieve the \textbf{1.19 ounces of ashes of "smashed diligence"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{1.53 spoonful of centrifuged mixture "care, cracked ashes of "renunciation" and disregard"}.
\item 
Dump the \textbf{1.19 ounces of ashes of "smashed diligence"} and \textbf{1.53 spoonful of centrifuged mixture "care, cracked ashes of "renunciation" and disregard"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{neglect}.
\end{enumerate}
\newpage
\section{A negotiation}How to make a \textbf{negotiation} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
63.02 spoonful of contract
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Bucket with hot water
\item 
Freezer
\item 
Centrifuge
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{63.02 spoonful of contract} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Wait for 7 seconds.
\item 
Stop the centrifuge and retrieve the \textbf{4.47 ounces of centrifuged mixture "contract"}.
\item 
Dip \textbf{4.47 ounces of centrifuged mixture "contract"} into the bucket with hot water.
\item 
Put \textbf{4.47 ounces of wet centrifuged mixture "contract"} into the freezer for a while.
\item 
Smash \textbf{4.47 ounces of wet and cooled centrifuged mixture "contract"} with the hammer.
\item 
Use nails to join the \textbf{4.47 ounces of wet, cooled and smashed centrifuged mixture "contract"} together into the shape of a perfectly functional \textbf{negotiation}.
\end{enumerate}
\newpage
\section{A nest}How to make a \textbf{nest} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
42.51 ounces of emptiness
\item 
4.57 ounces of haven
\item 
97 robins
\item 
3 eagles
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Centrifuge
\item 
Saw
\item 
Bonfire
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{4.57 ounces of haven} with the hammer.
\item 
Use the saw to slice \textbf{3 eagles} into bits.
\item 
Put \textbf{97 robins} into the bonfire.
\item 
Put \textbf{4.57 ounces of cracked haven} into the bonfire.
\item 
Wait for a rather short time.
\item 
Put \textbf{3 sliced eagles} into the rotating centrifuge.
\item 
Put \textbf{42.51 ounces of emptiness} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{12.33 ounces of centrifuged mixture "sliced eagle and emptiness"}.
\item 
Put \textbf{12.33 ounces of centrifuged mixture "sliced eagle and emptiness"} into the bonfire.
\item 
Retrieve the \textbf{20.34 ounces of ashes of "robin, cracked haven and centrifuged mixture "sliced eagle and emptiness""} from the bonfire.
\item 
Use screws to join the \textbf{20.34 ounces of ashes of "robin, cracked haven and centrifuged mixture "sliced eagle and emptiness""} together into the shape of a passable \textbf{nest}.
\end{enumerate}
\newpage
\section{A novice}How to make a \textbf{novice} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 experts
\item 
7.53 spoonful of mastery
\item 
17 vague notions of being professional
\item 
9 beginners
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot liquid
\item 
Fireplace
\item 
Centrifuge
\item 
Vessel
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{9 beginners} into the bucket with hot liquid.
\item 
Use the saw to slice \textbf{7.53 spoonful of mastery} into bits.
\item 
Put \textbf{7.53 spoonful of sliced mastery} into the fireplace.
\item 
Dip \textbf{9 wet beginners} into the bucket with hot liquid.
\item 
Wait.
\item 
Put \textbf{17 vague notions of being professional} into the rotating centrifuge.
\item 
Dip \textbf{9 very wet beginners} into the bucket with hot liquid.
\item 
Heat the vessel.
\item 
Retrieve the \textbf{9.39 spoonful of ashes of "sliced mastery"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{4.72 ounces of centrifuged mixture "being professional"}.
\item 
Fold the \textbf{5 experts}, \textbf{9 extremely wet beginners}, \textbf{9.39 spoonful of ashes of "sliced mastery"} and \textbf{4.72 ounces of centrifuged mixture "being professional"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{novice}.
\end{enumerate}
\newpage
\section{An offense}How to make an \textbf{offense} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
15.84 ounces of defense
\item 
3.98 ounces of capital
\item 
13 clear concepts of being federal
\item 
14.9 spoonful of violation
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Bonfire
\item 
Bucket with ice-cold water
\item 
Cauldron
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Dip \textbf{3.98 ounces of capital} into the bucket with ice-cold water.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{13 clear concepts of being federal} into the freezer for a while.
\item 
Wait for a very long time.
\item 
Use tape to join the \textbf{15.84 ounces of defense}, \textbf{3.98 ounces of wet capital}, \textbf{13 cooled clear concepts of being federal} and \textbf{14.9 spoonful of violation} together into the shape of a usable \textbf{offense}.
\end{enumerate}
\newpage
\section{An orthodontist}How to make an \textbf{orthodontist} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.8 ounces of dentist
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{6.8 ounces of dentist} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Heat the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{6.54 ounces of centrifuged mixture "dentist"}.
\item 
Stir the vessel.
\item 
Wait.
\item 
Heat the vessel.
\item 
Fold the \textbf{6.54 ounces of centrifuged mixture "dentist"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in an \textbf{orthodontist}.
\end{enumerate}
\newpage
\section{An otter}How to make an \textbf{otter} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
73.67 spoonful of possum
\item 
42.33 ounces of beaver
\item 
2.37 spoonful of seal
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Bucket with ionised water
\item 
Purifier
\item 
Stone
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Dip \textbf{42.33 ounces of beaver} into the bucket with ionised water.
\item 
Purify \textbf{42.33 ounces of wet beaver} with the purifier.
\item 
Crack \textbf{42.33 ounces of wet and purified beaver} with the stone.
\item 
Wait for a very short time.
\item 
Smash \textbf{73.67 spoonful of possum} with the stone.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{42.33 ounces of wet, purified and cracked beaver} into the rotating centrifuge.
\item 
Hold \textbf{73.67 spoonful of smashed possum} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{73.67 spoonful of smashed and slightly burned possum} into the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{3.6 spoonful of centrifuged mixture "wet, purified and cracked beaver"}.
\item 
Retrieve the \textbf{8.45 spoonful of ashes of "smashed and slightly burned possum"} from the fireplace.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a triangle into the circle and place \textbf{2.37 spoonful of seal}, \textbf{3.6 spoonful of centrifuged mixture "wet, purified and cracked beaver"} and \textbf{8.45 spoonful of ashes of "smashed and slightly burned possum"} on each corner.
\item 
Intone the following spell: "Miscentitus decalis faciator calebrior additia certo restimus!"
\item 
Slowly, an \textbf{otter} will appear inside the circle.
\end{enumerate}
\newpage
\section{A pancakes}How to make a \textbf{pancakes} in 3 easy steps:

\subsection{Materials}\begin{itemize}
\item 
70.81 spoonful of blueberry
\item 
8.66 spoonful of waffles
\item 
4.13 spoonful of maple
\item 
20.7 spoonful of stack
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Freezer
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the container.
\item 
Put \textbf{8.66 spoonful of waffles} into the freezer for a while.
\item 
Use tape to join the \textbf{70.81 spoonful of blueberry}, \textbf{8.66 spoonful of cooled waffles}, \textbf{4.13 spoonful of maple} and \textbf{20.7 spoonful of stack} together into the shape of a usable \textbf{pancakes}.
\end{enumerate}
\newpage
\section{A pantyhose}How to make a \textbf{pantyhose} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 sock
\item 
2.43 ounces of legs
\item 
1 vague notion of shearing
\item 
3 nylon
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Freezer
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 vague notion of shearing} into the container.
\item 
Put \textbf{2.43 ounces of legs} into the freezer for a while.
\item 
Stir the container.
\item 
Pour out the mixture from the container to get the \textbf{7.42 spoonful of container mixture "shearing"}.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a cross into the circle and place \textbf{10 sock}, \textbf{2.43 ounces of cooled legs}, \textbf{3 nylon} and \textbf{7.42 spoonful of container mixture "shearing"} on each corner.
\item 
Chant the following spell: "Dir! Aurotartio exsultrucus coicositor allium prospicus pareor, excidationo! Arium perfurnula sublio! Thecatus!"
\item 
Reluctantly, a \textbf{pantyhose} will appear inside the circle.
\end{enumerate}
\newpage
\section{A paragraph}How to make a \textbf{paragraph} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 essays
\item 
3.07 spoonful of passage
\item 
31.99 ounces of margin
\item 
33.8 spoonful of prose
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Cauldron
\item 
Hammer
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{33.8 spoonful of prose} with the purifier.
\item 
Crack \textbf{5 essays} with the hammer.
\item 
Put \textbf{31.99 ounces of margin} into the bonfire.
\item 
Fan the flames of the bonfire.
\item 
Hold \textbf{5 cracked essays} briefly into the bonfire to burn them a bit.
\item 
Hold \textbf{3.07 spoonful of passage} briefly into the bonfire to burn them a bit.
\item 
Heat the cauldron.
\item 
Wait.
\item 
Stir the cauldron.
\item 
Crack \textbf{33.8 spoonful of purified prose} with the hammer.
\item 
Retrieve the \textbf{71.88 spoonful of ashes of "margin"} from the bonfire.
\item 
Fold the \textbf{5 cracked and slightly burned essays}, \textbf{3.07 spoonful of slightly burned passage}, \textbf{33.8 spoonful of purified and cracked prose} and \textbf{71.88 spoonful of ashes of "margin"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{paragraph}.
\end{enumerate}
\newpage
\section{A pastry}How to make a \textbf{pastry} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 ideas of being french
\item 
73.33 spoonful of dough
\item 
25 vague notions of being tart
\item 
3.15 spoonful of baker
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Saw
\item 
Freezer
\item 
Bucket with clean water
\item 
Fireplace
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{4 ideas of being french} with the mortar.
\item 
Put \textbf{25 vague notions of being tart} into the freezer for a while.
\item 
Smash \textbf{3.15 spoonful of baker} with the mortar.
\item 
Dip \textbf{73.33 spoonful of dough} into the bucket with clean water.
\item 
Put \textbf{4 cracked ideas of being french} into the container.
\item 
Use the saw to slice \textbf{73.33 spoonful of wet dough} into bits.
\item 
Put \textbf{73.33 spoonful of wet and sliced dough} into the fireplace.
\item 
Retrieve the \textbf{20.76 spoonful of ashes of "wet and sliced dough"} from the fireplace.
\item 
Pour out the mixture from the container to get the \textbf{42.05 spoonful of container mixture "cracked being french"}.
\item 
Fold the \textbf{25 cooled vague notions of being tart}, \textbf{3.15 spoonful of smashed baker}, \textbf{20.76 spoonful of ashes of "wet and sliced dough"} and \textbf{42.05 spoonful of container mixture "cracked being french"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{pastry}.
\end{enumerate}
\newpage
\section{A pedestrian}How to make a \textbf{pedestrian} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
34 vague notions of crossing
\item 
4 walkways
\item 
17 walkers
\item 
26.54 ounces of sidewalk
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Hammer
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a minute.
\item 
Stir the cauldron.
\item 
Put \textbf{4 walkways} into the cauldron.
\item 
Heat the cauldron.
\item 
Let the cauldron cool down.
\item 
Stir the cauldron.
\item 
Crack \textbf{17 walkers} with the hammer.
\item 
Use the saw to slice \textbf{17 cracked walkers} into bits.
\item 
Let the cauldron cool down.
\item 
Pour out the mixture from the cauldron to get the \textbf{1.43 spoonful of cauldron mixture "walkway"}.
\item 
Dump the \textbf{34 vague notions of crossing}, \textbf{17 cracked and sliced walkers}, \textbf{26.54 ounces of sidewalk} and \textbf{1.43 spoonful of cauldron mixture "walkway"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{pedestrian}.
\end{enumerate}
\newpage
\section{A penguin}How to make a \textbf{penguin} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
19 tuxedoes
\item 
7.7 ounces of birds
\item 
6.11 ounces of seal
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Hammer
\item 
Container
\item 
Fireplace
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Put \textbf{6.11 ounces of seal} into the rotating centrifuge.
\item 
Crack \textbf{19 tuxedoes} with the hammer.
\item 
Put \textbf{7.7 ounces of birds} into the fireplace.
\item 
Put \textbf{19 cracked tuxedoes} into the container.
\item 
Heat the container.
\item 
Stir the container.
\item 
Pour out the mixture from the container to get the \textbf{8.29 spoonful of container mixture "cracked tuxedo"}.
\item 
Put \textbf{8.29 spoonful of container mixture "cracked tuxedo"} into the container.
\item 
Retrieve the \textbf{1.23 spoonful of ashes of "birds"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{32.58 spoonful of centrifuged mixture "seal"}.
\item 
Pour out the mixture from the container to get the \textbf{16.83 spoonful of container mixture "container mixture "cracked tuxedo""}.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a triangle into the circle and place \textbf{1.23 spoonful of ashes of "birds"}, \textbf{32.58 spoonful of centrifuged mixture "seal"} and \textbf{16.83 spoonful of container mixture "container mixture "cracked tuxedo""} on each corner.
\item 
Chant the following spell: "Municus agnanterio sarans umbo sica, adium mastor!"
\item 
Reluctantly, a \textbf{penguin} will appear inside the circle.
\end{enumerate}
\newpage
\section{A perception}How to make a \textbf{perception} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
18.34 spoonful of awareness
\item 
35 deceptions
\item 
3.01 spoonful of insight
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Bucket with clean water
\item 
Hammer
\item 
Freezer
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{3.01 spoonful of insight} with the purifier.
\item 
Put \textbf{35 deceptions} into the freezer for a while.
\item 
Dip \textbf{3.01 spoonful of purified insight} into the bucket with clean water.
\item 
Smash \textbf{35 cooled deceptions} with the hammer.
\item 
Wait for a long time.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a triangle into the circle and place \textbf{18.34 spoonful of awareness}, \textbf{35 cooled and smashed deceptions} and \textbf{3.01 spoonful of purified and wet insight} on each corner.
\item 
Whisper the following spell: "Deviolatius candor conis domitas, irideophonum! Arus protum inhibertuor metributio! Auteologitto acceleola sparcutus conscen!"
\item 
Reluctantly, a \textbf{perception} will appear inside the circle.
\end{enumerate}
\newpage
\section{A physiology}How to make a \textbf{physiology} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.83 spoonful of anatomy
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{6.83 spoonful of anatomy} into the freezer for a while.
\item 
Wait.
\item 
Throw \textbf{6.83 spoonful of cooled anatomy} away.
\item 
Fan the flames of the fireplace.
\item 
Wait.
\item 
Grind a little bit of troll teeth to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Realise that you never really needed a \textbf{physiology}.
\end{enumerate}
\newpage
\section{A pie}How to make a \textbf{pie} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 peaches
\item 
1 humility
\item 
8.81 ounces of pizza
\item 
78 ideas of baked
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Container
\item 
Bonfire
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{1 humility} with the purifier.
\item 
Heat the container.
\item 
Put \textbf{78 ideas of baked} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.6 ounces of centrifuged mixture "baked"}.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{2 peaches} into the rotating centrifuge.
\item 
Put \textbf{8.81 ounces of pizza} into the freezer for a while.
\item 
Stop the centrifuge and retrieve the \textbf{6.87 ounces of centrifuged mixture "peach"}.
\item 
Dump the \textbf{1 purified humility}, \textbf{8.81 ounces of cooled pizza}, \textbf{1.6 ounces of centrifuged mixture "baked"} and \textbf{6.87 ounces of centrifuged mixture "peach"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{pie}.
\end{enumerate}
\newpage
\section{A piece}How to make a \textbf{piece} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12 parts
\item 
7.2 spoonful of conversation
\item 
1.27 spoonful of sliver
\item 
2.5 spoonful of puzzle
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Freezer
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.2 spoonful of conversation} into the freezer for a while.
\item 
Put \textbf{2.5 spoonful of puzzle} into the container.
\item 
Put \textbf{12 parts} into the fireplace.
\item 
Pour out the mixture from the container to get the \textbf{9.88 spoonful of container mixture "puzzle"}.
\item 
Retrieve the \textbf{28.06 spoonful of ashes of "part"} from the fireplace.
\item 
Dump the \textbf{7.2 spoonful of cooled conversation}, \textbf{1.27 spoonful of sliver}, \textbf{9.88 spoonful of container mixture "puzzle"} and \textbf{28.06 spoonful of ashes of "part"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{piece}.
\end{enumerate}
\newpage
\section{A pine}How to make a \textbf{pine} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.78 spoonful of tree
\item 
1.1 ounces of trees
\item 
5 oaks
\item 
104.42 spoonful of sap
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Centrifuge
\item 
Bucket with liquid
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3.78 spoonful of tree} into the rotating centrifuge.
\item 
Dip \textbf{5 oaks} into the bucket with liquid.
\item 
Put \textbf{1.1 ounces of trees} into the rotating centrifuge.
\item 
Purify \textbf{5 wet oaks} with the purifier.
\item 
Put \textbf{5 wet and purified oaks} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.68 ounces of centrifuged mixture "tree, trees and wet and purified oak"}.
\item 
Use glue to join the \textbf{104.42 spoonful of sap} and \textbf{7.68 ounces of centrifuged mixture "tree, trees and wet and purified oak"} together into the shape of a perfectly functional \textbf{pine}.
\end{enumerate}
\newpage
\section{A plan}How to make a \textbf{plan} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.1 spoonful of preparation
\item 
8 ideas
\item 
4 objectives
\item 
10.77 ounces of secretive
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Cauldron
\item 
Bucket with hot liquid
\item 
Freezer
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8 ideas} into the bonfire.
\item 
Retrieve the \textbf{5.21 spoonful of ashes of "idea"} from the bonfire.
\item 
Heat the cauldron.
\item 
Put \textbf{5.1 spoonful of preparation} into the rotating centrifuge.
\item 
Put \textbf{5.21 spoonful of ashes of "idea"} into the freezer for a while.
\item 
Put \textbf{5.21 spoonful of cooled ashes of "idea"} into the cauldron.
\item 
Dip \textbf{10.77 ounces of secretive} into the bucket with hot liquid.
\item 
Heat the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{55.48 ounces of centrifuged mixture "preparation"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{9.66 spoonful of cauldron mixture "cooled ashes of "idea""}.
\item 
Use glue to join the \textbf{4 objectives}, \textbf{10.77 ounces of wet secretive}, \textbf{55.48 ounces of centrifuged mixture "preparation"} and \textbf{9.66 spoonful of cauldron mixture "cooled ashes of "idea""} together into the form of a perfectly functional \textbf{plan}.
\end{enumerate}
\newpage
\section{A policeman}How to make a \textbf{policeman} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.52 spoonful of fireman
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Bonfire
\item 
Vessel
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the vessel.
\item 
Put \textbf{6.52 spoonful of fireman} into the vessel.
\item 
Fan the flames of the bonfire.
\item 
Pour out the mixture from the vessel to get the \textbf{1.72 spoonful of vessel mixture "fireman"}.
\item 
Wait.
\item 
Smash \textbf{1.72 spoonful of vessel mixture "fireman"} with the hammer.
\item 
Stir the vessel.
\item 
Put \textbf{1.72 spoonful of smashed vessel mixture "fireman"} into the vessel.
\item 
Fan the flames of the bonfire.
\item 
Pour out the mixture from the vessel to get the \textbf{9.19 spoonful of vessel mixture "smashed vessel mixture "fireman""}.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Place \textbf{9.19 spoonful of vessel mixture "smashed vessel mixture "fireman""} into the circle.
\item 
Chant the following spell: "Condus!"
\item 
Suddendly, a \textbf{policeman} will appear inside the circle.
\end{enumerate}
\newpage
\section{A policy}How to make a \textbf{policy} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 rule
\item 
21.13 ounces of company
\item 
10.96 ounces of attendance
\item 
1.88 ounces of honesty
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Fireplace
\item 
Stone
\item 
Familiar chinchilla
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{21.13 ounces of company} with the stone.
\item 
Heat the container.
\item 
Put \textbf{1 rule} into the fireplace.
\item 
Feed \textbf{10.96 ounces of attendance} to your familiar chinchilla.
\item 
Wait until your familiar chinchilla poops. Receive \textbf{2.06 ounces of a very dirty pile of "attendance"}.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{21.13 ounces of smashed company} into the fireplace.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Retrieve the \textbf{2.18 ounces of ashes of "rule and smashed company"} from the fireplace.
\item 
Dump the \textbf{1.88 ounces of honesty}, \textbf{2.06 ounces of a very dirty pile of "attendance"} and \textbf{2.18 ounces of ashes of "rule and smashed company"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{policy}.
\end{enumerate}
\newpage
\section{A pony}How to make a \textbf{pony} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.51 ounces of colt
\item 
2 vague notions of ride
\item 
7.85 spoonful of horse
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Hammer
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{7.85 spoonful of horse} with the hammer.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{9.51 ounces of colt} into the cauldron.
\item 
Smash \textbf{7.85 spoonful of cracked horse} with the hammer.
\item 
Pour out the mixture from the cauldron to get the \textbf{7.77 ounces of cauldron mixture "colt"}.
\item 
Fold the \textbf{2 vague notions of ride}, \textbf{7.85 spoonful of cracked and smashed horse} and \textbf{7.77 ounces of cauldron mixture "colt"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{pony}.
\end{enumerate}
\newpage
\section{A predator}How to make a \textbf{predator} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 preys
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\item 
Mortar
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{7 preys} with the mortar.
\item 
Put \textbf{7 smashed preys} into the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Retrieve the \textbf{33.15 spoonful of ashes of "smashed prey"} from the fireplace.
\item 
Fold the \textbf{33.15 spoonful of ashes of "smashed prey"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{predator}.
\end{enumerate}
\newpage
\section{A pronoun}How to make a \textbf{pronoun} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.11 spoonful of noun
\item 
3.28 ounces of subjectivity
\item 
4.58 spoonful of adjective
\item 
22 verbs
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\item 
Bucket with water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3.28 ounces of subjectivity} into the rotating centrifuge.
\item 
Dip \textbf{3.11 spoonful of noun} into the bucket with water.
\item 
Stir the container.
\item 
Wait for a short time.
\item 
Dip \textbf{22 verbs} into the bucket with water.
\item 
Stop the centrifuge and retrieve the \textbf{6.49 ounces of centrifuged mixture "subjectivity"}.
\item 
Dump the \textbf{3.11 spoonful of wet noun}, \textbf{4.58 spoonful of adjective}, \textbf{22 wet verbs} and \textbf{6.49 ounces of centrifuged mixture "subjectivity"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{pronoun}.
\end{enumerate}
\newpage
\section{A protractor}How to make a \textbf{protractor} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 angles
\item 
4 compasses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\item 
Hammer
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the container cool down.
\item 
Put \textbf{6 angles} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.24 spoonful of centrifuged mixture "angle"}.
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Crack \textbf{4 compasses} with the hammer.
\item 
Purify \textbf{4 cracked compasses} with the purifier.
\item 
Dump the \textbf{4 cracked and purified compasses} and \textbf{1.24 spoonful of centrifuged mixture "angle"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{protractor}.
\end{enumerate}
\newpage
\section{A quest}How to make a \textbf{quest} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.48 spoonful of mission
\item 
46.49 ounces of vision
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Container
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{3.48 spoonful of mission} into bits.
\item 
Stir the container.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a line into the circle and place \textbf{3.48 spoonful of sliced mission} and \textbf{46.49 ounces of vision} on each end.
\item 
Whisper the following spell: "Orditus circulmeus cha! Larium!"
\item 
Reluctantly, a \textbf{quest} will appear inside the circle.
\end{enumerate}
\newpage
\section{A quiz}How to make a \textbf{quiz} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
18.7 ounces of test
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{18.7 ounces of test} with the mortar.
\item 
Wait for a rather long time.
\item 
Put \textbf{18.7 ounces of smashed test} into the cauldron.
\item 
Let the cauldron cool down.
\item 
Pour out the mixture from the cauldron to get the \textbf{5.61 spoonful of cauldron mixture "smashed test"}.
\item 
Fold the \textbf{5.61 spoonful of cauldron mixture "smashed test"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{quiz}.
\end{enumerate}
\newpage
\section{A radish}How to make a \textbf{radish} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.93 ounces of beet
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised water
\item 
Fireplace
\item 
Centrifuge
\item 
Cauldron
\item 
Hammer
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.93 ounces of beet} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Heat the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{3.48 spoonful of centrifuged mixture "beet"}.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Smash \textbf{3.48 spoonful of centrifuged mixture "beet"} with the hammer.
\item 
Hold \textbf{3.48 spoonful of smashed centrifuged mixture "beet"} briefly into the fireplace to burn them a bit.
\item 
Dip \textbf{3.48 spoonful of smashed and slightly burned centrifuged mixture "beet"} into the bucket with ionised water.
\item 
Put \textbf{3.48 spoonful of smashed, slightly burned and wet centrifuged mixture "beet"} into the fireplace.
\item 
Retrieve the \textbf{36.67 ounces of ashes of "smashed, slightly burned and wet centrifuged mixture "beet""} from the fireplace.
\item 
Use nails to join the \textbf{36.67 ounces of ashes of "smashed, slightly burned and wet centrifuged mixture "beet""} together into the shape of a beautiful \textbf{radish}.
\end{enumerate}
\newpage
\section{A rag}How to make a \textbf{rag} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
29 rugs
\item 
8.8 ounces of damper
\item 
36.74 ounces of critic
\item 
28.5 spoonful of doll
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Put \textbf{28.5 spoonful of doll} into the cauldron.
\item 
Purify \textbf{36.74 ounces of critic} with the purifier.
\item 
Pour out the mixture from the cauldron to get the \textbf{8.33 spoonful of cauldron mixture "doll"}.
\item 
Stir the cauldron.
\item 
Heat the cauldron.
\item 
Fold the \textbf{29 rugs}, \textbf{8.8 ounces of damper}, \textbf{36.74 ounces of purified critic} and \textbf{8.33 spoonful of cauldron mixture "doll"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{rag}.
\end{enumerate}
\newpage
\section{A ram}How to make a \textbf{ram} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.88 ounces of antler
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Hammer
\item 
Centrifuge
\item 
Familiar ape
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{9.88 ounces of antler} with the hammer.
\item 
Let your familiar ape sniff at \textbf{9.88 ounces of cracked antler}.
\item 
Pet your familiar ape.
\item 
Stir the container.
\item 
Let your familiar ape lick \textbf{9.88 ounces of cracked antler}.
\item 
Put \textbf{9.88 ounces of cracked and licked antler} into the rotating centrifuge.
\item 
Heat the container.
\item 
Stop the centrifuge and retrieve the \textbf{9.95 spoonful of centrifuged mixture "cracked and licked antler"}.
\item 
Use nails to join the \textbf{9.95 spoonful of centrifuged mixture "cracked and licked antler"} together into the form of a passable \textbf{ram}.
\end{enumerate}
\newpage
\section{A reaction}How to make a \textbf{reaction} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.44 spoonful of chemical
\item 
3 delays
\item 
60 instincts
\item 
12 effects
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with ionised liquid
\item 
Purifier
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{3 delays} into the bucket with ionised liquid.
\item 
Put \textbf{3 wet delays} into the rotating centrifuge.
\item 
Purify \textbf{60 instincts} with the purifier.
\item 
Speed up the centrifuge.
\item 
Put \textbf{4.44 spoonful of chemical} into the rotating centrifuge.
\item 
Put \textbf{12 effects} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{5.7 spoonful of centrifuged mixture "wet delay, chemical and effect"}.
\item 
Put \textbf{60 purified instincts} into the rotating centrifuge.
\item 
Dip \textbf{5.7 spoonful of centrifuged mixture "wet delay, chemical and effect"} into the bucket with ionised liquid.
\item 
Stop the centrifuge and retrieve the \textbf{4.77 spoonful of centrifuged mixture "purified instinct"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a line into the circle and place \textbf{5.7 spoonful of wet centrifuged mixture "wet delay, chemical and effect"} and \textbf{4.77 spoonful of centrifuged mixture "purified instinct"} on each end.
\item 
Chant the following spell: "Adpellus!"
\item 
Slowly, a \textbf{reaction} will appear inside the circle.
\end{enumerate}
\newpage
\section{A reason}How to make a \textbf{reason} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
20 explanations
\item 
6.54 ounces of cause
\item 
23 principles
\item 
9 moments
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Put \textbf{9 moments} into the bonfire.
\item 
Wait for a rather short time.
\item 
Fan the flames of the bonfire.
\item 
Hold \textbf{20 explanations} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{20 slightly burned explanations} into the bonfire.
\item 
Retrieve the \textbf{4.48 ounces of ashes of "moment and slightly burned explanation"} from the bonfire.
\item 
Dump the \textbf{6.54 ounces of cause}, \textbf{23 principles} and \textbf{4.48 ounces of ashes of "moment and slightly burned explanation"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{reason}.
\end{enumerate}
\newpage
\section{A recall}How to make a \textbf{recall} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.07 ounces of memory
\item 
12.57 spoonful of remembrance
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Container
\item 
Centrifuge
\item 
Bucket with clean water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.07 ounces of memory} into the bonfire.
\item 
Dip \textbf{12.57 spoonful of remembrance} into the bucket with clean water.
\item 
Put \textbf{12.57 spoonful of wet remembrance} into the rotating centrifuge.
\item 
Heat the container.
\item 
Retrieve the \textbf{5.75 spoonful of ashes of "memory"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{16.34 spoonful of centrifuged mixture "wet remembrance"}.
\item 
Dump the \textbf{5.75 spoonful of ashes of "memory"} and \textbf{16.34 spoonful of centrifuged mixture "wet remembrance"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{recall}.
\end{enumerate}
\newpage
\section{A repair}How to make a \textbf{repair} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.14 ounces of mechanic
\item 
30.61 spoonful of replacement
\item 
4 vague notions of broken
\item 
10 technicians
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Vessel
\item 
Bucket with ionised liquid
\item 
Centrifuge
\item 
Stone
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.14 ounces of mechanic} into the freezer for a while.
\item 
Dip \textbf{4 vague notions of broken} into the bucket with ionised liquid.
\item 
Smash \textbf{30.61 spoonful of replacement} with the stone.
\item 
Put \textbf{30.61 spoonful of smashed replacement} into the vessel.
\item 
Put \textbf{4 wet vague notions of broken} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.72 spoonful of centrifuged mixture "wet broken"}.
\item 
Pour out the mixture from the vessel to get the \textbf{5.57 ounces of vessel mixture "smashed replacement"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{9.14 ounces of cooled mechanic}, \textbf{10 technicians}, \textbf{7.72 spoonful of centrifuged mixture "wet broken"} and \textbf{5.57 ounces of vessel mixture "smashed replacement"} on each corner.
\item 
Chant the following spell: "Titus falis serplurca!"
\item 
Reluctantly, a \textbf{repair} will appear inside the circle.
\end{enumerate}
\newpage
\section{Research}How to make \textbf{research} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.1 spoonful of thesis
\item 
5 outlines
\item 
32.58 ounces of statistics
\item 
2.42 spoonful of report
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Saw
\item 
Centrifuge
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2.42 spoonful of report} into the rotating centrifuge.
\item 
Smash \textbf{9.1 spoonful of thesis} with the hammer.
\item 
Use the saw to slice \textbf{32.58 ounces of statistics} into bits.
\item 
Crack \textbf{9.1 spoonful of smashed thesis} with the hammer.
\item 
Smash \textbf{5 outlines} with the hammer.
\item 
Use the saw to slice \textbf{5 smashed outlines} into bits.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.86 spoonful of centrifuged mixture "report"}.
\item 
Use nails to join the \textbf{9.1 spoonful of smashed and cracked thesis}, \textbf{5 smashed and sliced outlines}, \textbf{32.58 ounces of sliced statistics} and \textbf{4.86 spoonful of centrifuged mixture "report"} together into the shape of a beautiful \textbf{research}.
\end{enumerate}
\newpage
\section{A rib}How to make a \textbf{rib} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 sparers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ice-cold liquid
\item 
Purifier
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{6 sparers} into the bucket with ice-cold liquid.
\item 
Use the saw to slice \textbf{6 wet sparers} into bits.
\item 
Wait for 9 minutes.
\item 
Dip \textbf{6 wet and sliced sparers} into the bucket with ice-cold liquid.
\item 
Purify \textbf{6 very wet and sliced sparers} with the purifier.
\item 
Use the saw to slice \textbf{6 very wet, sliced and purified sparers} into bits.
\item 
Dump the \textbf{6 very wet, fragmented and purified sparers} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{rib}.
\end{enumerate}
\newpage
\section{A rifle}How to make a \textbf{rifle} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 idea of shooting
\item 
1 gun
\item 
6.1 spoonful of butt
\item 
3.45 spoonful of range
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Pet chinchilla
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the container.
\item 
Put \textbf{1 gun} into the rotating centrifuge.
\item 
Put \textbf{3.45 spoonful of range} into the container.
\item 
Feed \textbf{1 idea of shooting} to your pet chinchilla.
\item 
Pour out the mixture from the container to get the \textbf{5.61 ounces of container mixture "range"}.
\item 
Wait until your pet chinchilla poops. Receive \textbf{19.6 spoonful of a very dirty pile of "shooting"}.
\item 
Stop the centrifuge and retrieve the \textbf{12.34 spoonful of centrifuged mixture "gun"}.
\item 
Dump the \textbf{6.1 spoonful of butt}, \textbf{5.61 ounces of container mixture "range"}, \textbf{19.6 spoonful of a very dirty pile of "shooting"} and \textbf{12.34 spoonful of centrifuged mixture "gun"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{rifle}.
\end{enumerate}
\newpage
\section{A rinse}How to make a \textbf{rinse} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 vague notions of being flush
\item 
20.45 spoonful of lather
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Bucket with clean liquid
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{20.45 spoonful of lather} with the stone.
\item 
Purify \textbf{20.45 spoonful of cracked lather} with the purifier.
\item 
Dip \textbf{20.45 spoonful of cracked and purified lather} into the bucket with clean liquid.
\item 
Crack \textbf{20.45 spoonful of cracked, purified and wet lather} with the stone.
\item 
Smash \textbf{4 vague notions of being flush} with the stone.
\item 
Dump the \textbf{4 smashed vague notions of being flush} and \textbf{20.45 spoonful of crushed, purified and wet lather} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{rinse}.
\end{enumerate}
\newpage
\section{A rise}How to make a \textbf{rise} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
26 ideas of climb
\item 
8.98 ounces of ascension
\item 
8.39 ounces of growth
\item 
21 clear concepts of lift
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{21 clear concepts of lift} into the rotating centrifuge.
\item 
Wait.
\item 
Put \textbf{26 ideas of climb} into the rotating centrifuge.
\item 
Put \textbf{8.39 ounces of growth} into the rotating centrifuge.
\item 
Put \textbf{8.98 ounces of ascension} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{6.66 spoonful of centrifuged mixture "lift, climb, growth and ascension"}.
\item 
Dump the \textbf{6.66 spoonful of centrifuged mixture "lift, climb, growth and ascension"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{rise}.
\end{enumerate}
\newpage
\section{A risk}How to make a \textbf{risk} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.55 spoonful of chance
\item 
62 ideas of dare
\item 
20 dangers
\item 
8 clear concepts of being dangerous
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Fireplace
\item 
Cauldron
\item 
Pet ape
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a minute.
\item 
Fan the flames of the fireplace.
\item 
Throw \textbf{3.55 spoonful of chance} away.
\item 
Put \textbf{20 dangers} into the fireplace.
\item 
Wait.
\item 
Heat the cauldron.
\item 
Purify \textbf{8 clear concepts of being dangerous} with the purifier.
\item 
Let your pet ape sniff at \textbf{8 purified clear concepts of being dangerous}.
\item 
Retrieve the \textbf{21.31 ounces of ashes of "danger"} from the fireplace.
\item 
Use nails to join the \textbf{62 ideas of dare}, \textbf{8 purified clear concepts of being dangerous} and \textbf{21.31 ounces of ashes of "danger"} together into the shape of a perfectly functional \textbf{risk}.
\end{enumerate}
\newpage
\section{A ritual}How to make a \textbf{ritual} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.49 spoonful of tradition
\item 
51.46 ounces of custom
\item 
5.5 spoonful of daily
\item 
1.63 spoonful of ceremony
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Purifier
\item 
Centrifuge
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{5.5 spoonful of daily} into bits.
\item 
Purify \textbf{51.46 ounces of custom} with the purifier.
\item 
Put \textbf{6.49 spoonful of tradition} into the rotating centrifuge.
\item 
Put \textbf{1.63 spoonful of ceremony} into the rotating centrifuge.
\item 
Put \textbf{51.46 ounces of purified custom} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{19.32 ounces of centrifuged mixture "tradition, ceremony and purified custom"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a line into the circle and place \textbf{5.5 spoonful of sliced daily} and \textbf{19.32 ounces of centrifuged mixture "tradition, ceremony and purified custom"} on each end.
\item 
Intone the following spell: "Inrecus! Connector inter! Exculosius archanaan quialiper, consolea commera!"
\item 
Suddendly, a \textbf{ritual} will appear inside the circle.
\end{enumerate}
\newpage
\section{A robber}How to make a \textbf{robber} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 bandits
\item 
9 banks
\item 
6.79 ounces of slip
\item 
7.79 spoonful of crook
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ice-cold water
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the vessel.
\item 
Put \textbf{7.79 spoonful of crook} into the vessel.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{9.1 spoonful of vessel mixture "crook"}.
\item 
Put \textbf{9.1 spoonful of vessel mixture "crook"} into the vessel.
\item 
Let the vessel cool down.
\item 
Wait for a second.
\item 
Dip \textbf{9 banks} into the bucket with ice-cold water.
\item 
Pour out the mixture from the vessel to get the \textbf{3.15 spoonful of vessel mixture "vessel mixture "crook""}.
\item 
Dump the \textbf{3 bandits}, \textbf{9 wet banks}, \textbf{6.79 ounces of slip} and \textbf{3.15 spoonful of vessel mixture "vessel mixture "crook""} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{robber}.
\end{enumerate}
\newpage
\section{A robot}How to make a \textbf{robot} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 mechanic
\item 
9 clear concepts of being human
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot liquid
\item 
Purifier
\item 
Fireplace
\item 
Centrifuge
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Dip \textbf{9 clear concepts of being human} into the bucket with hot liquid.
\item 
Wait for a short time.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{9 wet clear concepts of being human} into the freezer for a while.
\item 
Purify \textbf{6 mechanic} with the purifier.
\item 
Put \textbf{6 purified mechanic} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{24.49 spoonful of centrifuged mixture "purified mechanics"}.
\item 
Dump the \textbf{9 wet and cooled clear concepts of being human} and \textbf{24.49 spoonful of centrifuged mixture "purified mechanics"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{robot}.
\end{enumerate}
\newpage
\section{A rocks}How to make a \textbf{rocks} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 cannons
\item 
5.52 spoonful of erosion
\item 
71 gravels
\item 
7.81 spoonful of waterfall
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{71 gravels} with the purifier.
\item 
Put \textbf{5.52 spoonful of erosion} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{9.23 ounces of vessel mixture "erosion"}.
\item 
Let the vessel cool down.
\item 
Heat the vessel.
\item 
Stir the vessel.
\item 
Dump the \textbf{8 cannons}, \textbf{71 purified gravels}, \textbf{7.81 spoonful of waterfall} and \textbf{9.23 ounces of vessel mixture "erosion"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{rocks}.
\end{enumerate}
\newpage
\section{A rot}How to make a \textbf{rot} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
47.62 ounces of deterioration
\item 
7.68 spoonful of mildew
\item 
1.72 ounces of erosion
\item 
7.37 spoonful of decomposition
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Freezer
\item 
Mortar
\item 
Container
\item 
Centrifuge
\item 
Pet dog
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the fireplace.
\item 
Pet your pet dog.
\item 
Put \textbf{47.62 ounces of deterioration} into the container.
\item 
Wait for 10 minutes.
\item 
Put \textbf{7.37 spoonful of decomposition} into the rotating centrifuge.
\item 
Let your pet dog lick \textbf{1.72 ounces of erosion}.
\item 
Pour out the mixture from the container to get the \textbf{2.79 ounces of container mixture "deterioration"}.
\item 
Crack \textbf{1.72 ounces of licked erosion} with the mortar.
\item 
Stir the container.
\item 
Put \textbf{2.79 ounces of container mixture "deterioration"} into the freezer for a while.
\item 
Stop the centrifuge and retrieve the \textbf{6.67 ounces of centrifuged mixture "decomposition"}.
\item 
Use glue to join the \textbf{7.68 spoonful of mildew}, \textbf{1.72 ounces of licked and cracked erosion}, \textbf{2.79 ounces of cooled container mixture "deterioration"} and \textbf{6.67 ounces of centrifuged mixture "decomposition"} together into the shape of a passable \textbf{rot}.
\end{enumerate}
\newpage
\section{A ruin}How to make a \textbf{ruin} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5 demolitions
\item 
3.92 ounces of wreck
\item 
9 condemnations
\item 
10 vague notions of being ancient
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Freezer
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{5 demolitions} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{3.92 ounces of wreck} into the bonfire.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{6.89 spoonful of ashes of "wreck"} from the bonfire.
\item 
Hold \textbf{5 slightly burned demolitions} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{6.89 spoonful of ashes of "wreck"} into the freezer for a while.
\item 
Hold \textbf{9 condemnations} briefly into the bonfire to burn them a bit.
\item 
Wait for 9 seconds.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{5 burned demolitions}, \textbf{9 slightly burned condemnations}, \textbf{10 vague notions of being ancient} and \textbf{6.89 spoonful of cooled ashes of "wreck"} on each corner.
\item 
Intone the following spell: "Chius!"
\item 
Reluctantly, a \textbf{ruin} will appear inside the circle.
\end{enumerate}
\newpage
\section{A rules}How to make a \textbf{rules} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.36 spoonful of dictator
\item 
11.76 ounces of directions
\item 
24.17 spoonful of authority
\item 
6 legislatures
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Vessel
\item 
Hammer
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{11.76 ounces of directions} into the vessel.
\item 
Smash \textbf{6.36 spoonful of dictator} with the hammer.
\item 
Wait.
\item 
Pour out the mixture from the vessel to get the \textbf{1.0 ounce of vessel mixture "directions"}.
\item 
Put \textbf{24.17 spoonful of authority} into the rotating centrifuge.
\item 
Put \textbf{6.36 spoonful of smashed dictator} into the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{2.19 ounces of centrifuged mixture "authority"}.
\item 
Pour out the mixture from the vessel to get the \textbf{5.73 spoonful of vessel mixture "smashed dictator"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a cross into the circle and place \textbf{6 legislatures}, \textbf{1.0 ounce of vessel mixture "directions"}, \textbf{2.19 ounces of centrifuged mixture "authority"} and \textbf{5.73 spoonful of vessel mixture "smashed dictator"} on each corner.
\item 
Whisper the following spell: "Convola lus!"
\item 
Reluctantly, a \textbf{rules} will appear inside the circle.
\end{enumerate}
\newpage
\section{Safety}How to make \textbf{safety} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17.52 spoonful of lock
\item 
5 policemen
\item 
1.69 ounces of patrol
\item 
5.19 spoonful of insurance
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{5.19 spoonful of insurance} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{17.52 spoonful of lock} into the fireplace.
\item 
Retrieve the \textbf{2.41 ounces of ashes of "lock"} from the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{1.69 ounces of patrol} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{5 policemen} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{5 slightly burned policemen} into the freezer for a while.
\item 
Put \textbf{1.69 ounces of slightly burned patrol} into the fireplace.
\item 
Retrieve the \textbf{44.81 spoonful of ashes of "slightly burned patrol"} from the fireplace.
\item 
Dump the \textbf{5 slightly burned and cooled policemen}, \textbf{5.19 spoonful of slightly burned insurance}, \textbf{2.41 ounces of ashes of "lock"} and \textbf{44.81 spoonful of ashes of "slightly burned patrol"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{safety}.
\end{enumerate}
\newpage
\section{A sale}How to make a \textbf{sale} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
39.65 ounces of salesman
\item 
2.86 ounces of product
\item 
6.39 ounces of yard
\item 
6.82 ounces of tax
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Pet mouse
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{2.86 ounces of product} briefly into the bonfire to burn them a bit.
\item 
Feed \textbf{6.82 ounces of tax} to your pet mouse.
\item 
Wait until your pet mouse poops. Receive \textbf{38.97 spoonful of a very dirty pile of "tax"}.
\item 
Hold \textbf{38.97 spoonful of a very dirty pile of "tax"} briefly into the bonfire to burn them a bit.
\item 
Fold the \textbf{39.65 ounces of salesman}, \textbf{2.86 ounces of slightly burned product}, \textbf{6.39 ounces of yard} and \textbf{38.97 spoonful of slightly burned a very dirty pile of "tax"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{sale}.
\end{enumerate}
\newpage
\section{A same}How to make a \textbf{same} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 vague notions of match
\item 
7 changes
\item 
8.43 spoonful of norm
\item 
16 vague notions of stay
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot water
\item 
Freezer
\item 
Purifier
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{8.43 spoonful of norm} with the purifier.
\item 
Dip \textbf{10 vague notions of match} into the bucket with hot water.
\item 
Put \textbf{10 wet vague notions of match} into the freezer for a while.
\item 
Wait.
\item 
Purify \textbf{10 wet and cooled vague notions of match} with the purifier.
\item 
Put \textbf{7 changes} into the freezer for a while.
\item 
Dip \textbf{16 vague notions of stay} into the bucket with hot water.
\item 
Wait.
\item 
Purify \textbf{16 wet vague notions of stay} with the purifier.
\item 
Use nails to join the \textbf{10 wet, cooled and purified vague notions of match}, \textbf{7 cooled changes}, \textbf{8.43 spoonful of purified norm} and \textbf{16 wet and purified vague notions of stay} together into the shape of a perfectly functional \textbf{same}.
\end{enumerate}
\newpage
\section{Sand}How to make \textbf{sand} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
11 castles
\item 
5 clays
\item 
2.53 spoonful of egypt
\item 
2.66 spoonful of mud
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised liquid
\item 
Purifier
\item 
Stone
\item 
Pet unicorn
\item 
Freezer
\item 
Fireplace
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{11 castles} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{2.66 spoonful of mud} into the freezer for a while.
\item 
Let your pet unicorn sniff at \textbf{5 clays}.
\item 
Wait.
\item 
Purify \textbf{2.53 spoonful of egypt} with the purifier.
\item 
Crack \textbf{5 clays} with the stone.
\item 
Dip \textbf{2.66 spoonful of cooled mud} into the bucket with ionised liquid.
\item 
Smash \textbf{5 cracked clays} with the stone.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{11 slightly burned castles}, \textbf{5 cracked and smashed clays}, \textbf{2.53 spoonful of purified egypt} and \textbf{2.66 spoonful of cooled and wet mud} on each corner.
\item 
Chant the following spell: "Inmoros augus! Devo macutio!"
\item 
Slowly, \textbf{sand} will appear inside the circle.
\end{enumerate}
\newpage
\section{A santa}How to make a \textbf{santa} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.54 spoonful of chimney
\item 
10.36 ounces of stock
\item 
1.11 ounces of beard
\item 
10 helpers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2.54 spoonful of chimney} into the rotating centrifuge.
\item 
Put \textbf{10 helpers} into the rotating centrifuge.
\item 
Hold \textbf{1.11 ounces of beard} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{1.11 ounces of slightly burned beard} into the rotating centrifuge.
\item 
Heat the container.
\item 
Stop the centrifuge and retrieve the \textbf{9.64 spoonful of centrifuged mixture "chimney, helper and slightly burned beard"}.
\item 
Fold the \textbf{10.36 ounces of stock} and \textbf{9.64 spoonful of centrifuged mixture "chimney, helper and slightly burned beard"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{santa}.
\end{enumerate}
\newpage
\section{A scallop}How to make a \textbf{scallop} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 mussels
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Bucket with clean liquid
\item 
Centrifuge
\item 
Bonfire
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{8 mussels} into the bucket with clean liquid.
\item 
Hold \textbf{8 wet mussels} briefly into the bonfire to burn them a bit.
\item 
Stir the vessel.
\item 
Hold \textbf{8 wet and slightly burned mussels} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{8 wet and burned mussels} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Let the vessel cool down.
\item 
Stop the centrifuge and retrieve the \textbf{3.22 ounces of centrifuged mixture "wet and burned mussel"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Place \textbf{3.22 ounces of centrifuged mixture "wet and burned mussel"} into the circle.
\item 
Intone the following spell: "Intego! Dihesperusta! Ambulatio posciduod que aetatus caluterius mitas tericopium ampuniculos!"
\item 
Reluctantly, a \textbf{scallop} will appear inside the circle.
\end{enumerate}
\newpage
\section{A scuba}How to make a \textbf{scuba} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
20 tanks
\item 
1 flipper
\item 
5 snorkels
\item 
2.29 spoonful of mask
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Centrifuge
\item 
Fireplace
\item 
Container
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 flipper} into the container.
\item 
Pour out the mixture from the container to get the \textbf{12.59 spoonful of container mixture "flipper"}.
\item 
Hold \textbf{2.29 spoonful of mask} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{12.59 spoonful of container mixture "flipper"} into the fireplace.
\item 
Retrieve the \textbf{12.45 ounces of ashes of "container mixture "flipper""} from the fireplace.
\item 
Let the container cool down.
\item 
Put \textbf{12.45 ounces of ashes of "container mixture "flipper""} into the rotating centrifuge.
\item 
Purify \textbf{2.29 spoonful of slightly burned mask} with the purifier.
\item 
Hold \textbf{20 tanks} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{2.29 spoonful of slightly burned and purified mask} into the container.
\item 
Stop the centrifuge and retrieve the \textbf{15.4 spoonful of centrifuged mixture "ashes of "container mixture "flipper"""}.
\item 
Pour out the mixture from the container to get the \textbf{5.2 ounces of container mixture "slightly burned and purified mask"}.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a square into the circle and place \textbf{20 slightly burned tanks}, \textbf{5 snorkels}, \textbf{15.4 spoonful of centrifuged mixture "ashes of "container mixture "flipper"""} and \textbf{5.2 ounces of container mixture "slightly burned and purified mask"} on each corner.
\item 
Intone the following spell: "Tumentum accereo indum melotorius! Anatefinium!"
\item 
Slowly, a \textbf{scuba} will appear inside the circle.
\end{enumerate}
\newpage
\section{Seafood}How to make \textbf{seafood} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 oysters
\item 
99.48 ounces of scallop
\item 
30.93 spoonful of clam
\item 
27.01 spoonful of squid
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Centrifuge
\item 
Stone
\item 
Bucket with ionised liquid
\item 
Familiar chinchilla
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{30.93 spoonful of clam} into the bucket with ionised liquid.
\item 
Wait.
\item 
Smash \textbf{99.48 ounces of scallop} with the stone.
\item 
Put \textbf{99.48 ounces of smashed scallop} into the cauldron.
\item 
Put \textbf{4 oysters} into the rotating centrifuge.
\item 
Crack \textbf{27.01 spoonful of squid} with the stone.
\item 
Let your familiar chinchilla lick \textbf{27.01 spoonful of cracked squid}.
\item 
Pet your familiar chinchilla.
\item 
Crack \textbf{30.93 spoonful of wet clam} with the stone.
\item 
Pour out the mixture from the cauldron to get the \textbf{16.82 spoonful of cauldron mixture "smashed scallop"}.
\item 
Stop the centrifuge and retrieve the \textbf{16.09 ounces of centrifuged mixture "oyster"}.
\item 
Use tape to join the \textbf{30.93 spoonful of wet and cracked clam}, \textbf{27.01 spoonful of cracked and licked squid}, \textbf{16.82 spoonful of cauldron mixture "smashed scallop"} and \textbf{16.09 ounces of centrifuged mixture "oyster"} together into the form of a passable \textbf{seafood}.
\end{enumerate}
\newpage
\section{A serial}How to make a \textbf{serial} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 killers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Vessel
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8 killers} into the vessel.
\item 
Fan the flames of the fireplace.
\item 
Let the vessel cool down.
\item 
Heat the vessel.
\item 
Fan the flames of the fireplace.
\item 
Stir the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{32.63 spoonful of vessel mixture "killer"}.
\item 
Put \textbf{32.63 spoonful of vessel mixture "killer"} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{2.63 spoonful of centrifuged mixture "vessel mixture "killer""}.
\item 
Fold the \textbf{2.63 spoonful of centrifuged mixture "vessel mixture "killer""} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{serial}.
\end{enumerate}
\newpage
\section{A several}How to make a \textbf{several} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12.72 ounces of fewness
\item 
5 ideas of being numerous
\item 
6 manies
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Bucket with ionised liquid
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Purify \textbf{12.72 ounces of fewness} with the purifier.
\item 
Dip \textbf{12.72 ounces of purified fewness} into the bucket with ionised liquid.
\item 
Wait for a short time.
\item 
Purify \textbf{6 manies} with the purifier.
\item 
Fold the \textbf{12.72 ounces of purified and wet fewness}, \textbf{5 ideas of being numerous} and \textbf{6 purified manies} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{several}.
\end{enumerate}
\newpage
\section{A shell}How to make a \textbf{shell} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
13.15 ounces of coral
\item 
41.44 spoonful of tortoise
\item 
2.19 ounces of cocoon
\item 
9 eggs
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Cauldron
\item 
Centrifuge
\item 
Bonfire
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{41.44 spoonful of tortoise} into the bonfire.
\item 
Put \textbf{2.19 ounces of cocoon} into the cauldron.
\item 
Put \textbf{9 eggs} into the bonfire.
\item 
Put \textbf{13.15 ounces of coral} into the rotating centrifuge.
\item 
Stir the cauldron.
\item 
Stop the centrifuge and retrieve the \textbf{14.61 ounces of centrifuged mixture "coral"}.
\item 
Retrieve the \textbf{6.45 spoonful of ashes of "tortoise and egg"} from the bonfire.
\item 
Use the saw to slice \textbf{6.45 spoonful of ashes of "tortoise and egg"} into bits.
\item 
Put \textbf{6.45 spoonful of sliced ashes of "tortoise and egg"} into the rotating centrifuge.
\item 
Pour out the mixture from the cauldron to get the \textbf{4.27 ounces of cauldron mixture "cocoon"}.
\item 
Stop the centrifuge and retrieve the \textbf{143.07 spoonful of centrifuged mixture "sliced ashes of "tortoise and egg""}.
\item 
Use glue to join the \textbf{14.61 ounces of centrifuged mixture "coral"}, \textbf{4.27 ounces of cauldron mixture "cocoon"} and \textbf{143.07 spoonful of centrifuged mixture "sliced ashes of "tortoise and egg""} together into the shape of a perfectly functional \textbf{shell}.
\end{enumerate}
\newpage
\section{A shiver}How to make a \textbf{shiver} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 clear concepts of shake
\item 
9.48 spoonful of quiver
\item 
9 ideas of being cold
\item 
5.53 ounces of shutter
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with clean liquid
\item 
Vessel
\item 
Saw
\item 
Freezer
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Stir the vessel.
\item 
Use the saw to slice \textbf{9 ideas of being cold} into bits.
\item 
Put \textbf{9.48 spoonful of quiver} into the vessel.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{5.53 ounces of shutter} into the bonfire.
\item 
Put \textbf{4 clear concepts of shake} into the freezer for a while.
\item 
Dip \textbf{9 sliced ideas of being cold} into the bucket with clean liquid.
\item 
Pour out the mixture from the vessel to get the \textbf{9.97 ounces of vessel mixture "quiver"}.
\item 
Retrieve the \textbf{12.38 spoonful of ashes of "shutter"} from the bonfire.
\item 
Fold the \textbf{4 cooled clear concepts of shake}, \textbf{9 sliced and wet ideas of being cold}, \textbf{9.97 ounces of vessel mixture "quiver"} and \textbf{12.38 spoonful of ashes of "shutter"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{shiver}.
\end{enumerate}
\newpage
\section{A shoelace}How to make a \textbf{shoelace} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.16 ounces of knot
\item 
20.98 ounces of lace
\item 
33.62 ounces of sneaker
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Mortar
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Smash \textbf{20.98 ounces of lace} with the mortar.
\item 
Stir the vessel.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Use tape to join the \textbf{4.16 ounces of knot}, \textbf{20.98 ounces of smashed lace} and \textbf{33.62 ounces of sneaker} together into the shape of a passable \textbf{shoelace}.
\end{enumerate}
\newpage
\section{A sign}How to make a \textbf{sign} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
22 pickets
\item 
6.76 ounces of register
\item 
5.01 ounces of name
\item 
5 leos
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Cauldron
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a rather short time.
\item 
Put \textbf{5.01 ounces of name} into the rotating centrifuge.
\item 
Put \textbf{6.76 ounces of register} into the cauldron.
\item 
Heat the cauldron.
\item 
Let the cauldron cool down.
\item 
Stop the centrifuge and retrieve the \textbf{26.73 spoonful of centrifuged mixture "name"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{7.93 spoonful of cauldron mixture "register"}.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a cross into the circle and place \textbf{22 pickets}, \textbf{5 leos}, \textbf{26.73 spoonful of centrifuged mixture "name"} and \textbf{7.93 spoonful of cauldron mixture "register"} on each corner.
\item 
Whisper the following spell: "Captiosus complatim astalites, clysterula virabiliteo! Graphiro!"
\item 
Slowly, a \textbf{sign} will appear inside the circle.
\end{enumerate}
\newpage
\section{A signature}How to make a \textbf{signature} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
44.07 spoonful of sign
\item 
46 contracts
\item 
10 ideas of being initial
\item 
4.69 ounces of name
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{10 ideas of being initial} into the fireplace.
\item 
Heat the container.
\item 
Put \textbf{4.69 ounces of name} into the fireplace.
\item 
Wait for a minute.
\item 
Put \textbf{46 contracts} into the container.
\item 
Put \textbf{44.07 spoonful of sign} into the fireplace.
\item 
Wait for 3 days.
\item 
Fan the flames of the fireplace.
\item 
Let the container cool down.
\item 
Retrieve the \textbf{7.17 ounces of ashes of "being initial, name and sign"} from the fireplace.
\item 
Pour out the mixture from the container to get the \textbf{28.95 ounces of container mixture "contract"}.
\item 
Dump the \textbf{7.17 ounces of ashes of "being initial, name and sign"} and \textbf{28.95 ounces of container mixture "contract"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{signature}.
\end{enumerate}
\newpage
\section{A slick}How to make a \textbf{slick} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.56 ounces of otter
\item 
38.26 spoonful of vaseline
\item 
7 oils
\item 
9.99 ounces of slimy
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with hot water
\item 
Fireplace
\item 
Purifier
\item 
Cauldron
\item 
Centrifuge
\item 
Pet ape
\item 
Freezer
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7 oils} into the freezer for a while.
\item 
Purify \textbf{7 cooled oils} with the purifier.
\item 
Stir the cauldron.
\item 
Dip \textbf{38.26 spoonful of vaseline} into the bucket with hot water.
\item 
Put \textbf{38.26 spoonful of wet vaseline} into the rotating centrifuge.
\item 
Heat the cauldron.
\item 
Let your pet ape sniff at \textbf{9.99 ounces of slimy}.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{3.46 ounces of centrifuged mixture "wet vaseline"}.
\item 
Use tape to join the \textbf{2.56 ounces of otter}, \textbf{7 cooled and purified oils}, \textbf{9.99 ounces of slimy} and \textbf{3.46 ounces of centrifuged mixture "wet vaseline"} together into the form of a beautiful \textbf{slick}.
\end{enumerate}
\newpage
\section{A slither}How to make a \textbf{slither} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.93 ounces of snail
\item 
10 snakes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Purifier
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{10 snakes} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Purify \textbf{8.93 ounces of snail} with the purifier.
\item 
Put \textbf{8.93 ounces of purified snail} into the freezer for a while.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{4.89 ounces of centrifuged mixture "snake"}.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a line into the circle and place \textbf{8.93 ounces of purified and cooled snail} and \textbf{4.89 ounces of centrifuged mixture "snake"} on each end.
\item 
Whisper the following spell: "Saticus petus!"
\item 
Suddendly, a \textbf{slither} will appear inside the circle.
\end{enumerate}
\newpage
\section{A smudge}How to make a \textbf{smudge} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
24.55 spoonful of smear
\item 
5 blots
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\item 
Bonfire
\item 
Bucket with hot water
\item 
Pet ape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let your pet ape sniff at \textbf{24.55 spoonful of smear}.
\item 
Feed \textbf{24.55 spoonful of smear} to your pet ape.
\item 
Fan the flames of the bonfire.
\item 
Wait until your pet ape poops. Receive \textbf{7.02 ounces of a very dirty pile of "smear"}.
\item 
Wait.
\item 
Heat the container.
\item 
Dip \textbf{5 blots} into the bucket with hot water.
\item 
Put \textbf{7.02 ounces of a very dirty pile of "smear"} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{9.19 ounces of centrifuged mixture "a very dirty pile of "smear""}.
\item 
Fold the \textbf{5 wet blots} and \textbf{9.19 ounces of centrifuged mixture "a very dirty pile of "smear""} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{smudge}.
\end{enumerate}
\newpage
\section{Soap}How to make \textbf{soap} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 cleaner
\item 
1 bathtub
\item 
3 ropes
\item 
5 lavas
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Container
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 bathtub} into the fireplace.
\item 
Let the container cool down.
\item 
Retrieve the \textbf{5.18 spoonful of ashes of "bathtub"} from the fireplace.
\item 
Stir the container.
\item 
Hold \textbf{1 cleaner} briefly into the fireplace to burn it a bit.
\item 
Put \textbf{3 ropes} into the fireplace.
\item 
Let the container cool down.
\item 
Put \textbf{5.18 spoonful of ashes of "bathtub"} into the container.
\item 
Pour out the mixture from the container to get the \textbf{9.87 ounces of container mixture "ashes of "bathtub""}.
\item 
Hold \textbf{1 slightly burned cleaner} briefly into the fireplace to burn it a bit.
\item 
Retrieve the \textbf{1.19 ounces of ashes of "rope"} from the fireplace.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{1 burned cleaner}, \textbf{5 lavas}, \textbf{9.87 ounces of container mixture "ashes of "bathtub""} and \textbf{1.19 ounces of ashes of "rope"} on each corner.
\item 
Intone the following spell: "Cominarius crucor!"
\item 
Slowly, \textbf{soap} will appear inside the circle.
\end{enumerate}
\newpage
\section{A soccer}How to make a \textbf{soccer} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
48.4 ounces of sports
\item 
6 victories
\item 
3 kicks
\item 
6 indoor
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Container
\item 
Bucket with clean water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{6 victories} into the rotating centrifuge.
\item 
Dip \textbf{3 kicks} into the bucket with clean water.
\item 
Heat the container.
\item 
Stir the container.
\item 
Stop the centrifuge and retrieve the \textbf{4.31 spoonful of centrifuged mixture "victory"}.
\item 
Fold the \textbf{48.4 ounces of sports}, \textbf{3 wet kicks}, \textbf{6 indoor} and \textbf{4.31 spoonful of centrifuged mixture "victory"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{soccer}.
\end{enumerate}
\newpage
\section{Something adorable}How to make \textbf{something adorable} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 clear concepts of being cute
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Container
\item 
Freezer
\item 
Saw
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{9 clear concepts of being cute} into bits.
\item 
Put \textbf{9 sliced clear concepts of being cute} into the container.
\item 
Let the container cool down.
\item 
Fan the flames of the fireplace.
\item 
Heat the container.
\item 
Pour out the mixture from the container to get the \textbf{5.57 spoonful of container mixture "sliced being cute"}.
\item 
Let the container cool down.
\item 
Put \textbf{5.57 spoonful of container mixture "sliced being cute"} into the freezer for a while.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Place \textbf{5.57 spoonful of cooled container mixture "sliced being cute"} into the circle.
\item 
Intone the following spell: "Turalia bonus stus, ostero!"
\item 
Reluctantly, \textbf{something adorable} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something cheerful}How to make \textbf{something cheerful} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
30 optimisms
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Container
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the container.
\item 
Heat the container.
\item 
Purify \textbf{30 optimisms} with the purifier.
\item 
Put \textbf{30 purified optimisms} into the container.
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Heat the container.
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Heat the container.
\item 
Pour out the mixture from the container to get the \textbf{7.18 spoonful of container mixture "purified optimism"}.
\item 
Use nails to join the \textbf{7.18 spoonful of container mixture "purified optimism"} together into the form of a passable \textbf{something cheerful}.
\end{enumerate}
\newpage
\section{Something cocky}How to make \textbf{something cocky} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
18.59 spoonful of conceited
\item 
114.55 ounces of attitude
\item 
9 clear concepts of being arrogant
\item 
22 modestnesses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Bonfire
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{9 clear concepts of being arrogant} into the freezer for a while.
\item 
Hold \textbf{22 modestnesses} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{114.55 ounces of attitude} into the rotating centrifuge.
\item 
Hold \textbf{22 slightly burned modestnesses} briefly into the bonfire to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{39.34 ounces of centrifuged mixture "attitude"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a cross into the circle and place \textbf{18.59 spoonful of conceited}, \textbf{9 cooled clear concepts of being arrogant}, \textbf{22 burned modestnesses} and \textbf{39.34 ounces of centrifuged mixture "attitude"} on each corner.
\item 
Whisper the following spell: "Coelestus! Caeceps laceus conludo cus, syrmamus! Depula aediens exprocubitus exscipium, vors! Apostro! Assivus octo caestratio circuitas ullua!"
\item 
Reluctantly, \textbf{something cocky} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something corrupt}How to make \textbf{something corrupt} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
37.34 spoonful of crookedness
\item 
10 senators
\item 
44.89 ounces of senate
\item 
2 governments
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Familiar hummingbird
\item 
Fireplace
\item 
Freezer
\item 
Vessel
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Put \textbf{2 governments} into the freezer for a while.
\item 
Put \textbf{44.89 ounces of senate} into the fireplace.
\item 
Feed \textbf{37.34 spoonful of crookedness} to your familiar hummingbird.
\item 
Wait until your familiar hummingbird poops. Receive \textbf{11.61 spoonful of a very dirty pile of "crookedness"}.
\item 
Retrieve the \textbf{9.54 spoonful of ashes of "senate"} from the fireplace.
\item 
Let the vessel cool down.
\item 
Crack \textbf{9.54 spoonful of ashes of "senate"} with the hammer.
\item 
Put \textbf{2 cooled governments} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{8.47 ounces of vessel mixture "cooled government"}.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a square into the circle and place \textbf{10 senators}, \textbf{11.61 spoonful of a very dirty pile of "crookedness"}, \textbf{9.54 spoonful of cracked ashes of "senate"} and \textbf{8.47 ounces of vessel mixture "cooled government"} on each corner.
\item 
Whisper the following spell: "Ciccesiticus!"
\item 
Slowly, \textbf{something corrupt} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something difficult}How to make \textbf{something difficult} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 challenge
\item 
10 roughnesses
\item 
4 confusions
\item 
6 ideas of being basic
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Cauldron
\item 
Stone
\item 
Pet mouse
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{4 confusions} with the stone.
\item 
Hold \textbf{4 smashed confusions} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{4 smashed and slightly burned confusions} into the rotating centrifuge.
\item 
Let the cauldron cool down.
\item 
Let your pet mouse sniff at \textbf{1 challenge}.
\item 
Pet your pet mouse.
\item 
Stop the centrifuge and retrieve the \textbf{9.1 ounces of centrifuged mixture "smashed and slightly burned confusion"}.
\item 
Let the cauldron cool down.
\item 
Dump the \textbf{1 challenge}, \textbf{10 roughnesses}, \textbf{6 ideas of being basic} and \textbf{9.1 ounces of centrifuged mixture "smashed and slightly burned confusion"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something difficult}.
\end{enumerate}
\newpage
\section{Something distinct}How to make \textbf{something distinct} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
23 vague notions of being specific
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{23 vague notions of being specific} into the freezer for a while.
\item 
Wait for a second.
\item 
Use the saw to slice \textbf{23 cooled vague notions of being specific} into bits.
\item 
Put \textbf{23 cooled and sliced vague notions of being specific} into the freezer for a while.
\item 
Wait.
\item 
Use the saw to slice \textbf{23 frozen and sliced vague notions of being specific} into bits.
\item 
Throw \textbf{23 frozen and fragmented vague notions of being specific} away.
\item 
Wait for a rather long time.
\item 
Grind a little bit of antler of the extinct flying stag to dust. It's not strictly needed, but doesn't hurt I guess?
\item 
Turn around. You will find that \textbf{something distinct} was there all along.
\end{enumerate}
\newpage
\section{Something everyday}How to make \textbf{something everyday} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 idea of being common
\item 
9.45 spoonful of routine
\item 
4 norms
\item 
5 clear concepts of being standard
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the vessel.
\item 
Hold \textbf{1 idea of being common} briefly into the fireplace to burn it a bit.
\item 
Let the vessel cool down.
\item 
Fan the flames of the fireplace.
\item 
Dump the \textbf{1 slightly burned idea of being common}, \textbf{9.45 spoonful of routine}, \textbf{4 norms} and \textbf{5 clear concepts of being standard} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something everyday}.
\end{enumerate}
\newpage
\section{Something exciting}How to make \textbf{something exciting} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
20 ideas of being adventurous
\item 
15.41 spoonful of thriller
\item 
36.59 ounces of interestingness
\item 
1.76 spoonful of olympics
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Container
\item 
Centrifuge
\item 
Saw
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{36.59 ounces of interestingness} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{15.41 spoonful of thriller} into the container.
\item 
Use the saw to slice \textbf{1.76 spoonful of olympics} into bits.
\item 
Heat the container.
\item 
Pour out the mixture from the container to get the \textbf{20.57 ounces of container mixture "thriller"}.
\item 
Stop the centrifuge and retrieve the \textbf{6.97 spoonful of centrifuged mixture "interestingness"}.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a square into the circle and place \textbf{20 ideas of being adventurous}, \textbf{1.76 spoonful of sliced olympics}, \textbf{20.57 ounces of container mixture "thriller"} and \textbf{6.97 spoonful of centrifuged mixture "interestingness"} on each corner.
\item 
Whisper the following spell: "Opulor! Masi adgressalo nubo!"
\item 
Reluctantly, \textbf{something exciting} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something foul}How to make \textbf{something foul} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17 clear concepts of being vulgar
\item 
9.87 spoonful of unpleasantness
\item 
4 vague notions of being silly
\item 
1 curse
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Saw
\item 
Bucket with water
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a rather long time.
\item 
Use the saw to slice \textbf{9.87 spoonful of unpleasantness} into bits.
\item 
Crack \textbf{4 vague notions of being silly} with the mortar.
\item 
Dip \textbf{9.87 spoonful of sliced unpleasantness} into the bucket with water.
\item 
Use the saw to slice \textbf{17 clear concepts of being vulgar} into bits.
\item 
Wait.
\item 
Smash \textbf{4 cracked vague notions of being silly} with the mortar.
\item 
Crack \textbf{4 cracked and smashed vague notions of being silly} with the mortar.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a cross into the circle and place \textbf{17 sliced clear concepts of being vulgar}, \textbf{9.87 spoonful of sliced and wet unpleasantness}, \textbf{4 crushed and smashed vague notions of being silly} and \textbf{1 curse} on each corner.
\item 
Chant the following spell: "Coena exandus chritas gens!"
\item 
Suddendly, \textbf{something foul} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something frequent}How to make \textbf{something frequent} in 4 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16.21 spoonful of often
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{16.21 spoonful of often} into the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Retrieve the \textbf{37.71 ounces of ashes of "often"} from the fireplace.
\item 
Use screws to join the \textbf{37.71 ounces of ashes of "often"} together into the shape of a perfectly functional \textbf{something frequent}.
\end{enumerate}
\newpage
\section{Something genuine}How to make \textbf{something genuine} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 sincerities
\item 
10 vague notions of being fake
\item 
8.0 ounces of reality
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Fireplace
\item 
Container
\item 
Purifier
\item 
Pet mouse
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the container cool down.
\item 
Pet your pet mouse.
\item 
Use the saw to slice \textbf{2 sincerities} into bits.
\item 
Purify \textbf{2 sliced sincerities} with the purifier.
\item 
Put \textbf{8.0 ounces of reality} into the fireplace.
\item 
Let the container cool down.
\item 
Hold \textbf{10 vague notions of being fake} briefly into the fireplace to burn them a bit.
\item 
Heat the container.
\item 
Put \textbf{2 sliced and purified sincerities} into the fireplace.
\item 
Stir the container.
\item 
Retrieve the \textbf{3.09 ounces of ashes of "reality and sliced and purified sincerity"} from the fireplace.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a line into the circle and place \textbf{10 slightly burned vague notions of being fake} and \textbf{3.09 ounces of ashes of "reality and sliced and purified sincerity"} on each end.
\item 
Intone the following spell: "Exico qua postimus conster!"
\item 
Reluctantly, \textbf{something genuine} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something gifted}How to make \textbf{something gifted} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 vague notions of being special
\item 
6 clear concepts of being exceptional
\item 
17.33 spoonful of genius
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Stone
\item 
Purifier
\item 
Freezer
\item 
Bucket with hot liquid
\item 
Familiar chinchilla
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{10 vague notions of being special} with the purifier.
\item 
Dip \textbf{10 purified vague notions of being special} into the bucket with hot liquid.
\item 
Smash \textbf{10 purified and wet vague notions of being special} with the stone.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Smash \textbf{17.33 spoonful of genius} with the stone.
\item 
Purify \textbf{6 clear concepts of being exceptional} with the purifier.
\item 
Dip \textbf{10 purified, wet and smashed vague notions of being special} into the bucket with hot liquid.
\item 
Feed \textbf{10 purified, very wet and smashed vague notions of being special} to your familiar chinchilla.
\item 
Put \textbf{6 purified clear concepts of being exceptional} into the freezer for a while.
\item 
Wait until your familiar chinchilla poops. Receive \textbf{16.74 spoonful of a very dirty pile of "purified, very wet and smashed being special"}.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a triangle into the circle and place \textbf{6 purified and cooled clear concepts of being exceptional}, \textbf{17.33 spoonful of smashed genius} and \textbf{16.74 spoonful of a very dirty pile of "purified, very wet and smashed being special"} on each corner.
\item 
Intone the following spell: "Tum ana pela, scaenarismus! Immerculus adceleritus convocamum teus sena botrio mas! Praetecto autoricus orius!"
\item 
Reluctantly, \textbf{something gifted} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something golden}How to make \textbf{something golden} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
25 clear concepts of being tan
\item 
3.77 spoonful of rule
\item 
17.34 spoonful of opportunity
\item 
4.75 ounces of silence
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Purifier
\item 
Hammer
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{25 clear concepts of being tan} with the hammer.
\item 
Wait.
\item 
Fan the flames of the fireplace.
\item 
Smash \textbf{3.77 spoonful of rule} with the hammer.
\item 
Purify \textbf{4.75 ounces of silence} with the purifier.
\item 
Crack \textbf{3.77 spoonful of smashed rule} with the hammer.
\item 
Put \textbf{17.34 spoonful of opportunity} into the fireplace.
\item 
Smash \textbf{4.75 ounces of purified silence} with the hammer.
\item 
Crack \textbf{25 smashed clear concepts of being tan} with the hammer.
\item 
Retrieve the \textbf{5.28 ounces of ashes of "opportunity"} from the fireplace.
\item 
Use nails to join the \textbf{25 smashed and cracked clear concepts of being tan}, \textbf{3.77 spoonful of smashed and cracked rule}, \textbf{4.75 ounces of purified and smashed silence} and \textbf{5.28 ounces of ashes of "opportunity"} together into the form of a usable \textbf{something golden}.
\end{enumerate}
\newpage
\section{Something haughty}How to make \textbf{something haughty} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
44.41 ounces of conceit
\item 
49 clear concepts of being arrogant
\item 
39 clear concepts of being proud
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Purifier
\item 
Silverpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{44.41 ounces of conceit} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{44.41 ounces of slightly burned conceit} into the fireplace.
\item 
Retrieve the \textbf{95.12 ounces of ashes of "slightly burned conceit"} from the fireplace.
\item 
Purify \textbf{95.12 ounces of ashes of "slightly burned conceit"} with the purifier.
\item 
Draw a magic circle on the floor using the silverpoint pen.
\item 
Draw a triangle into the circle and place \textbf{49 clear concepts of being arrogant}, \textbf{39 clear concepts of being proud} and \textbf{95.12 ounces of purified ashes of "slightly burned conceit"} on each corner.
\item 
Chant the following spell: "Inpettallior graphus foedispecus! Nec cestinum!"
\item 
Suddendly, \textbf{something haughty} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something lean}How to make \textbf{something lean} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 tendencies
\item 
1.22 spoonful of crutch
\item 
30 clear concepts of being slender
\item 
4 shoulders
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Familiar unicorn
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let your familiar unicorn sniff at \textbf{1.22 spoonful of crutch}.
\item 
Pet your familiar unicorn.
\item 
Let your familiar unicorn lick \textbf{4 shoulders}.
\item 
Feed \textbf{1.22 spoonful of crutch} to your familiar unicorn.
\item 
Hold \textbf{7 tendencies} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{4 licked shoulders} into the fireplace.
\item 
Pet your familiar unicorn.
\item 
Retrieve the \textbf{1.88 ounces of ashes of "licked shoulder"} from the fireplace.
\item 
Wait until your familiar unicorn poops. Receive \textbf{9.39 spoonful of a very dirty pile of "crutch"}.
\item 
Fold the \textbf{7 slightly burned tendencies}, \textbf{30 clear concepts of being slender}, \textbf{1.88 ounces of ashes of "licked shoulder"} and \textbf{9.39 spoonful of a very dirty pile of "crutch"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in \textbf{something lean}.
\end{enumerate}
\newpage
\section{Something loud}How to make \textbf{something loud} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.95 spoonful of voice
\item 
6.92 ounces of thunder
\item 
9 announcers
\item 
4.48 ounces of yell
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Purifier
\item 
Centrifuge
\item 
Stone
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{4.48 ounces of yell} with the purifier.
\item 
Smash \textbf{9 announcers} with the stone.
\item 
Hold \textbf{4.48 ounces of purified yell} briefly into the fireplace to burn them a bit.
\item 
Wait.
\item 
Put \textbf{9 smashed announcers} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{10.84 spoonful of centrifuged mixture "smashed announcer"}.
\item 
Use glue to join the \textbf{4.95 spoonful of voice}, \textbf{6.92 ounces of thunder}, \textbf{4.48 ounces of purified and slightly burned yell} and \textbf{10.84 spoonful of centrifuged mixture "smashed announcer"} together into the shape of a perfectly functional \textbf{something loud}.
\end{enumerate}
\newpage
\section{Something naive}How to make \textbf{something naive} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12.58 ounces of teenager
\item 
6.76 spoonful of guiltlessness
\item 
12 vulnerabilities
\item 
6.61 spoonful of innocence
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Saw
\item 
Centrifuge
\item 
Bucket with hot liquid
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{12 vulnerabilities} into the fireplace.
\item 
Wait for a short time.
\item 
Put \textbf{12.58 ounces of teenager} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{6.61 spoonful of innocence} into bits.
\item 
Speed up the centrifuge.
\item 
Dip \textbf{6.61 spoonful of sliced innocence} into the bucket with hot liquid.
\item 
Hold \textbf{6.61 spoonful of sliced and wet innocence} briefly into the fireplace to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{26.35 ounces of centrifuged mixture "teenager"}.
\item 
Retrieve the \textbf{8.23 ounces of ashes of "vulnerability"} from the fireplace.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{6.76 spoonful of guiltlessness}, \textbf{6.61 spoonful of sliced, wet and slightly burned innocence}, \textbf{26.35 ounces of centrifuged mixture "teenager"} and \textbf{8.23 ounces of ashes of "vulnerability"} on each corner.
\item 
Whisper the following spell: "Dabundustim dirigo curu! Scutillus!"
\item 
Slowly, \textbf{something naive} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something natural}How to make \textbf{something natural} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 vague notions of being vivid
\item 
27.58 ounces of herb
\item 
7 woods
\item 
9.93 spoonful of abnormality
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a long time.
\item 
Put \textbf{8 vague notions of being vivid} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{3.42 ounces of centrifuged mixture "being vivid"}.
\item 
Wait for a rather short time.
\item 
Throw \textbf{27.58 ounces of herb} away.
\item 
Put \textbf{3.42 ounces of centrifuged mixture "being vivid"} into the rotating centrifuge.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{2.92 ounces of centrifuged mixture "centrifuged mixture "being vivid""}.
\item 
Use glue to join the \textbf{7 woods}, \textbf{9.93 spoonful of abnormality} and \textbf{2.92 ounces of centrifuged mixture "centrifuged mixture "being vivid""} together into the form of a perfectly functional \textbf{something natural}.
\end{enumerate}
\newpage
\section{Something nuclear}How to make \textbf{something nuclear} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.68 spoonful of energy
\item 
42 nuclei
\item 
9.55 spoonful of microwave
\item 
5 atoms
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Container
\item 
Saw
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{5 atoms} into the rotating centrifuge.
\item 
Stir the container.
\item 
Use the saw to slice \textbf{9.55 spoonful of microwave} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{13.54 spoonful of centrifuged mixture "atom"}.
\item 
Put \textbf{9.55 spoonful of sliced microwave} into the rotating centrifuge.
\item 
Put \textbf{13.54 spoonful of centrifuged mixture "atom"} into the container.
\item 
Stop the centrifuge and retrieve the \textbf{4.95 spoonful of centrifuged mixture "sliced microwave"}.
\item 
Pour out the mixture from the container to get the \textbf{1.79 ounces of container mixture "centrifuged mixture "atom""}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a cross into the circle and place \textbf{8.68 spoonful of energy}, \textbf{42 nuclei}, \textbf{4.95 spoonful of centrifuged mixture "sliced microwave"} and \textbf{1.79 ounces of container mixture "centrifuged mixture "atom""} on each corner.
\item 
Whisper the following spell: "Latoria pericus!"
\item 
Reluctantly, \textbf{something nuclear} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something odd}How to make \textbf{something odd} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7 uncommonnesses
\item 
7 clear concepts of being weird
\item 
7 vague notions of being unique
\item 
8 strangenesses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bucket with clean liquid
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7 uncommonnesses} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Dip \textbf{7 clear concepts of being weird} into the bucket with clean liquid.
\item 
Wait for a very short time.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{26.92 ounces of centrifuged mixture "uncommonness"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a cross into the circle and place \textbf{7 wet clear concepts of being weird}, \textbf{7 vague notions of being unique}, \textbf{8 strangenesses} and \textbf{26.92 ounces of centrifuged mixture "uncommonness"} on each corner.
\item 
Whisper the following spell: "Matulus auto bipercum! Bre! Calco hartum indensim consiona opsequus consum inctus succio!"
\item 
Suddendly, \textbf{something odd} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something passive}How to make \textbf{something passive} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.05 spoonful of aggressiveness
\item 
13 forcefulnesses
\item 
1.44 ounces of indirectness
\item 
10 vague notions of being active
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Mortar
\item 
Centrifuge
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a very long time.
\item 
Smash \textbf{2.05 spoonful of aggressiveness} with the mortar.
\item 
Crack \textbf{10 vague notions of being active} with the mortar.
\item 
Put \textbf{1.44 ounces of indirectness} into the rotating centrifuge.
\item 
Put \textbf{13 forcefulnesses} into the container.
\item 
Stop the centrifuge and retrieve the \textbf{7.35 spoonful of centrifuged mixture "indirectness"}.
\item 
Use the saw to slice \textbf{7.35 spoonful of centrifuged mixture "indirectness"} into bits.
\item 
Wait for a very short time.
\item 
Put \textbf{2.05 spoonful of smashed aggressiveness} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{36.87 ounces of centrifuged mixture "smashed aggressiveness"}.
\item 
Pour out the mixture from the container to get the \textbf{16.79 spoonful of container mixture "forcefulness"}.
\item 
Dump the \textbf{10 cracked vague notions of being active}, \textbf{7.35 spoonful of sliced centrifuged mixture "indirectness"}, \textbf{36.87 ounces of centrifuged mixture "smashed aggressiveness"} and \textbf{16.79 spoonful of container mixture "forcefulness"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something passive}.
\end{enumerate}
\newpage
\section{Something possible}How to make \textbf{something possible} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.25 spoonful of maybe
\item 
114 impossiblenesses
\item 
5 mights
\item 
10 negotiations
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Fireplace
\item 
Centrifuge
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{5 mights} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{3.02 spoonful of vessel mixture "might"}.
\item 
Hold \textbf{114 impossiblenesses} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{10 negotiations} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{3.02 spoonful of vessel mixture "might"} into the vessel.
\item 
Heat the vessel.
\item 
Put \textbf{114 slightly burned impossiblenesses} into the rotating centrifuge.
\item 
Pour out the mixture from the vessel to get the \textbf{25.34 spoonful of vessel mixture "vessel mixture "might""}.
\item 
Stop the centrifuge and retrieve the \textbf{4.43 ounces of centrifuged mixture "slightly burned impossibleness"}.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a square into the circle and place \textbf{5.25 spoonful of maybe}, \textbf{10 slightly burned negotiations}, \textbf{25.34 spoonful of vessel mixture "vessel mixture "might""} and \textbf{4.43 ounces of centrifuged mixture "slightly burned impossibleness"} on each corner.
\item 
Chant the following spell: "Nudus insecretia crufus plens!"
\item 
Suddendly, \textbf{something possible} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something pure}How to make \textbf{something pure} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
29 vague notions of being white
\item 
7.56 ounces of innocence
\item 
13 essences
\item 
8 virtues
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Vessel
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.56 ounces of innocence} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Hold \textbf{29 vague notions of being white} briefly into the bonfire to burn them a bit.
\item 
Stir the vessel.
\item 
Put \textbf{29 slightly burned vague notions of being white} into the rotating centrifuge.
\item 
Let the vessel cool down.
\item 
Stop the centrifuge and retrieve the \textbf{5.91 spoonful of centrifuged mixture "innocence and slightly burned being white"}.
\item 
Use tape to join the \textbf{13 essences}, \textbf{8 virtues} and \textbf{5.91 spoonful of centrifuged mixture "innocence and slightly burned being white"} together into the shape of a passable \textbf{something pure}.
\end{enumerate}
\newpage
\section{Something raw}How to make \textbf{something raw} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
34.66 ounces of uncooked
\item 
69 cooks
\item 
11 oysters
\item 
119.92 ounces of tenderness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised liquid
\item 
Centrifuge
\item 
Hammer
\item 
Saw
\item 
Purifier
\item 
Vessel
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the vessel cool down.
\item 
Purify \textbf{11 oysters} with the purifier.
\item 
Use the saw to slice \textbf{34.66 ounces of uncooked} into bits.
\item 
Put \textbf{11 purified oysters} into the bonfire.
\item 
Dip \textbf{34.66 ounces of sliced uncooked} into the bucket with ionised liquid.
\item 
Smash \textbf{69 cooks} with the hammer.
\item 
Heat the vessel.
\item 
Wait for an hour.
\item 
Put \textbf{119.92 ounces of tenderness} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{5.92 spoonful of centrifuged mixture "tenderness"}.
\item 
Retrieve the \textbf{29.04 spoonful of ashes of "purified oyster"} from the bonfire.
\item 
Fold the \textbf{34.66 ounces of sliced and wet uncooked}, \textbf{69 smashed cooks}, \textbf{5.92 spoonful of centrifuged mixture "tenderness"} and \textbf{29.04 spoonful of ashes of "purified oyster"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{something raw}.
\end{enumerate}
\newpage
\section{Something shy}How to make \textbf{something shy} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 vulnerabilities
\item 
10.12 spoonful of sensitiveness
\item 
7 discreetnesses
\item 
3 introversions
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Hammer
\item 
Centrifuge
\item 
Bucket with water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the container.
\item 
Smash \textbf{2 vulnerabilities} with the hammer.
\item 
Put \textbf{10.12 spoonful of sensitiveness} into the rotating centrifuge.
\item 
Let the container cool down.
\item 
Dip \textbf{2 smashed vulnerabilities} into the bucket with water.
\item 
Stir the container.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.74 ounces of centrifuged mixture "sensitiveness"}.
\item 
Dump the \textbf{2 smashed and wet vulnerabilities}, \textbf{7 discreetnesses}, \textbf{3 introversions} and \textbf{7.74 ounces of centrifuged mixture "sensitiveness"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something shy}.
\end{enumerate}
\newpage
\section{Something that can bother}How to make \textbf{something that can bother} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
32 frustrations
\item 
7.45 ounces of irritation
\item 
6.07 ounces of hamper
\item 
49 aggravations
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Mortar
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{6.07 ounces of hamper} with the mortar.
\item 
Smash \textbf{7.45 ounces of irritation} with the mortar.
\item 
Wait.
\item 
Purify \textbf{49 aggravations} with the purifier.
\item 
Smash \textbf{6.07 ounces of cracked hamper} with the mortar.
\item 
Wait for a rather long time.
\item 
Purify \textbf{7.45 ounces of smashed irritation} with the purifier.
\item 
Crack \textbf{7.45 ounces of smashed and purified irritation} with the mortar.
\item 
Smash \textbf{32 frustrations} with the mortar.
\item 
Dump the \textbf{32 smashed frustrations}, \textbf{7.45 ounces of smashed, purified and cracked irritation}, \textbf{6.07 ounces of cracked and smashed hamper} and \textbf{49 purified aggravations} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something that can bother}.
\end{enumerate}
\newpage
\section{Something that can breathe}How to make \textbf{something that can breathe} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
34.9 spoonful of air
\item 
8 breaths
\item 
1.4 spoonful of aliveness
\item 
9 oxygens
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the vessel.
\item 
Put \textbf{9 oxygens} into the rotating centrifuge.
\item 
Let the vessel cool down.
\item 
Stir the vessel.
\item 
Put \textbf{8 breaths} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.25 spoonful of centrifuged mixture "oxygen and breath"}.
\item 
Dump the \textbf{34.9 spoonful of air}, \textbf{1.4 spoonful of aliveness} and \textbf{4.25 spoonful of centrifuged mixture "oxygen and breath"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something that can breathe}.
\end{enumerate}
\newpage
\section{Something that can choke}How to make \textbf{something that can choke} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.72 spoonful of asphyxiation
\item 
2 vague notions of cough
\item 
4 breaths
\item 
1 clear concept of swallow
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Cauldron
\item 
Saw
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 clear concept of swallow} into the rotating centrifuge.
\item 
Use the saw to slice \textbf{4 breaths} into bits.
\item 
Put \textbf{2 vague notions of cough} into the cauldron.
\item 
Let the cauldron cool down.
\item 
Put \textbf{2.72 spoonful of asphyxiation} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{3.1 spoonful of centrifuged mixture "swallow and asphyxiation"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{9.1 ounces of cauldron mixture "cough"}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a triangle into the circle and place \textbf{4 sliced breaths}, \textbf{3.1 spoonful of centrifuged mixture "swallow and asphyxiation"} and \textbf{9.1 ounces of cauldron mixture "cough"} on each corner.
\item 
Intone the following spell: "Beatus accido!"
\item 
Slowly, \textbf{something that can choke} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something that can compose}How to make \textbf{something that can compose} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17.01 spoonful of sentence
\item 
5.91 spoonful of writer
\item 
9.99 ounces of decomposition
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Freezer
\item 
Mortar
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{5.91 spoonful of writer} into the freezer for a while.
\item 
Smash \textbf{17.01 spoonful of sentence} with the mortar.
\item 
Put \textbf{17.01 spoonful of smashed sentence} into the bonfire.
\item 
Put \textbf{9.99 ounces of decomposition} into the bonfire.
\item 
Retrieve the \textbf{5.56 ounces of ashes of "smashed sentence and decomposition"} from the bonfire.
\item 
Fold the \textbf{5.91 spoonful of cooled writer} and \textbf{5.56 ounces of ashes of "smashed sentence and decomposition"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{something that can compose}.
\end{enumerate}
\newpage
\section{Something that can confess}How to make \textbf{something that can confess} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
25.55 ounces of admission
\item 
11.08 ounces of testimony
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{11.08 ounces of testimony} into the rotating centrifuge.
\item 
Wait for a very short time.
\item 
Hold \textbf{25.55 ounces of admission} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{25.55 ounces of slightly burned admission} into the fireplace.
\item 
Speed up the centrifuge.
\item 
Retrieve the \textbf{7.14 ounces of ashes of "slightly burned admission"} from the fireplace.
\item 
Put \textbf{7.14 ounces of ashes of "slightly burned admission"} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.63 spoonful of centrifuged mixture "testimony and ashes of "slightly burned admission""}.
\item 
Fold the \textbf{7.63 spoonful of centrifuged mixture "testimony and ashes of "slightly burned admission""} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in \textbf{something that can confess}.
\end{enumerate}
\newpage
\section{Something that can convince}How to make \textbf{something that can convince} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 clear concept of urge
\item 
9.66 ounces of persuader
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Hammer
\item 
Paintbrush
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{1 clear concept of urge} with the hammer.
\item 
Smash \textbf{1 cracked clear concept of urge} with the hammer.
\item 
Purify \textbf{9.66 ounces of persuader} with the purifier.
\item 
Crack \textbf{9.66 ounces of purified persuader} with the hammer.
\item 
Draw a magic circle on the floor using the paintbrush.
\item 
Draw a line into the circle and place \textbf{1 cracked and smashed clear concept of urge} and \textbf{9.66 ounces of purified and cracked persuader} on each end.
\item 
Whisper the following spell: "Caties!"
\item 
Reluctantly, \textbf{something that can convince} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something that can despise}How to make \textbf{something that can despise} in 3 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 vague notions of hate
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Stone
\item 
Familiar ape
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Pet your familiar ape.
\item 
Crack \textbf{6 vague notions of hate} with the stone.
\item 
Use glue to join the \textbf{6 cracked vague notions of hate} together into the shape of a beautiful \textbf{something that can despise}.
\end{enumerate}
\newpage
\section{Something that can dismiss}How to make \textbf{something that can dismiss} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
24 denials
\item 
1 adjournment
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Freezer
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 adjournment} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Put \textbf{24 denials} into the freezer for a while.
\item 
Eat \textbf{24 cooled denials}.
\item 
Fan the flames of the fireplace.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{3.29 spoonful of centrifuged mixture "adjournment"}.
\item 
Dump the \textbf{3.29 spoonful of centrifuged mixture "adjournment"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something that can dismiss}.
\end{enumerate}
\newpage
\section{Something that can disown}How to make \textbf{something that can disown} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 renunciations
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\item 
Container
\item 
Saw
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2 renunciations} into the rotating centrifuge.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Stop the centrifuge and retrieve the \textbf{1.92 spoonful of centrifuged mixture "renunciation"}.
\item 
Purify \textbf{1.92 spoonful of centrifuged mixture "renunciation"} with the purifier.
\item 
Use the saw to slice \textbf{1.92 spoonful of purified centrifuged mixture "renunciation"} into bits.
\item 
Stir the container.
\item 
Fold the \textbf{1.92 spoonful of purified and sliced centrifuged mixture "renunciation"} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in \textbf{something that can disown}.
\end{enumerate}
\newpage
\section{Something that can enter}How to make \textbf{something that can enter} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
12.48 spoonful of doorway
\item 
7 returns
\item 
35.63 ounces of entrance
\item 
15 vague notions of admit
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Cauldron
\item 
Centrifuge
\item 
Purifier
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Put \textbf{35.63 ounces of entrance} into the rotating centrifuge.
\item 
Purify \textbf{7 returns} with the purifier.
\item 
Put \textbf{15 vague notions of admit} into the cauldron.
\item 
Pour out the mixture from the cauldron to get the \textbf{8.51 ounces of cauldron mixture "admit"}.
\item 
Crack \textbf{12.48 spoonful of doorway} with the hammer.
\item 
Put \textbf{12.48 spoonful of cracked doorway} into the cauldron.
\item 
Pour out the mixture from the cauldron to get the \textbf{2.79 ounces of cauldron mixture "cracked doorway"}.
\item 
Stop the centrifuge and retrieve the \textbf{1.67 ounces of centrifuged mixture "entrance"}.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a cross into the circle and place \textbf{7 purified returns}, \textbf{8.51 ounces of cauldron mixture "admit"}, \textbf{2.79 ounces of cauldron mixture "cracked doorway"} and \textbf{1.67 ounces of centrifuged mixture "entrance"} on each corner.
\item 
Chant the following spell: "Nymus num obvectus! Defrigo tus petia! Crinarium!"
\item 
Suddendly, \textbf{something that can enter} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something that can erupt}How to make \textbf{something that can erupt} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.25 ounces of explosion
\item 
8.83 ounces of volcano
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Saw
\item 
Container
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the container.
\item 
Use the saw to slice \textbf{9.25 ounces of explosion} into bits.
\item 
Let the container cool down.
\item 
Put \textbf{8.83 ounces of volcano} into the container.
\item 
Wait.
\item 
Put \textbf{9.25 ounces of sliced explosion} into the freezer for a while.
\item 
Use the saw to slice \textbf{9.25 ounces of sliced and cooled explosion} into bits.
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Put \textbf{9.25 ounces of fragmented and cooled explosion} into the freezer for a while.
\item 
Pour out the mixture from the container to get the \textbf{9.6 spoonful of container mixture "volcano"}.
\item 
Use glue to join the \textbf{9.25 ounces of fragmented and frozen explosion} and \textbf{9.6 spoonful of container mixture "volcano"} together into the shape of a perfectly functional \textbf{something that can erupt}.
\end{enumerate}
\newpage
\section{Something that can instruct}How to make \textbf{something that can instruct} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10.77 spoonful of command
\item 
6.5 spoonful of teacher
\item 
7.91 spoonful of information
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Hammer
\item 
Bonfire
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{6.5 spoonful of teacher} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{10.77 spoonful of command} into the rotating centrifuge.
\item 
Crack \textbf{7.91 spoonful of information} with the hammer.
\item 
Put \textbf{6.5 spoonful of slightly burned teacher} into the bonfire.
\item 
Wait for a day.
\item 
Retrieve the \textbf{1.77 ounces of ashes of "slightly burned teacher"} from the bonfire.
\item 
Crack \textbf{7.91 spoonful of cracked information} with the hammer.
\item 
Smash \textbf{1.77 ounces of ashes of "slightly burned teacher"} with the hammer.
\item 
Stop the centrifuge and retrieve the \textbf{1.14 spoonful of centrifuged mixture "command"}.
\item 
Use nails to join the \textbf{7.91 spoonful of crushed information}, \textbf{1.77 ounces of smashed ashes of "slightly burned teacher"} and \textbf{1.14 spoonful of centrifuged mixture "command"} together into the shape of a perfectly functional \textbf{something that can instruct}.
\end{enumerate}
\newpage
\section{Something that can listen}How to make \textbf{something that can listen} in 15 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.5 ounces of music
\item 
4.21 ounces of narration
\item 
21 clear concepts of look
\item 
5.24 spoonful of sympathy
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Stone
\item 
Fireplace
\item 
Centrifuge
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{5.24 spoonful of sympathy} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{1.53 spoonful of centrifuged mixture "sympathy"}.
\item 
Put \textbf{5.5 ounces of music} into the fireplace.
\item 
Put \textbf{1.53 spoonful of centrifuged mixture "sympathy"} into the rotating centrifuge.
\item 
Crack \textbf{21 clear concepts of look} with the stone.
\item 
Put \textbf{21 cracked clear concepts of look} into the fireplace.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Crack \textbf{4.21 ounces of narration} with the stone.
\item 
Retrieve the \textbf{4.74 spoonful of ashes of "music and cracked look"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{2.74 spoonful of centrifuged mixture "centrifuged mixture "sympathy""}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a triangle into the circle and place \textbf{4.21 ounces of cracked narration}, \textbf{4.74 spoonful of ashes of "music and cracked look"} and \textbf{2.74 spoonful of centrifuged mixture "centrifuged mixture "sympathy""} on each corner.
\item 
Chant the following spell: "Sublio injunctus petizo, despecunctio! Sufficor heratus stabitut! Demoro circuatus! Minus celego botundiesco, calturaris!"
\item 
Slowly, \textbf{something that can listen} will appear inside the circle.
\end{enumerate}
\newpage
\section{Something that can minded}How to make \textbf{something that can minded} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 vague notion of closing
\item 
8.18 ounces of absence
\item 
22 vague notions of being pleasant
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Purifier
\item 
Bonfire
\item 
Saw
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{1 vague notion of closing} briefly into the bonfire to burn it a bit.
\item 
Put \textbf{8.18 ounces of absence} into the vessel.
\item 
Purify \textbf{1 slightly burned vague notion of closing} with the purifier.
\item 
Fan the flames of the bonfire.
\item 
Let the vessel cool down.
\item 
Heat the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{164.61 spoonful of vessel mixture "absence"}.
\item 
Stir the vessel.
\item 
Put \textbf{1 slightly burned and purified vague notion of closing} into the vessel.
\item 
Use the saw to slice \textbf{164.61 spoonful of vessel mixture "absence"} into bits.
\item 
Pour out the mixture from the vessel to get the \textbf{12.01 ounces of vessel mixture "slightly burned and purified closing"}.
\item 
Use tape to join the \textbf{22 vague notions of being pleasant}, \textbf{164.61 spoonful of sliced vessel mixture "absence"} and \textbf{12.01 ounces of vessel mixture "slightly burned and purified closing"} together into the form of a beautiful \textbf{something that can minded}.
\end{enumerate}
\newpage
\section{Something that can notify}How to make \textbf{something that can notify} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
20 informations
\item 
1 vague notion of being alert
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Mortar
\item 
Vessel
\item 
Centrifuge
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{20 informations} into the bonfire.
\item 
Smash \textbf{1 vague notion of being alert} with the mortar.
\item 
Put \textbf{1 smashed vague notion of being alert} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Speed up the centrifuge.
\item 
Retrieve the \textbf{4.39 spoonful of ashes of "information"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{6.77 ounces of centrifuged mixture "smashed being alert"}.
\item 
Use tape to join the \textbf{4.39 spoonful of ashes of "information"} and \textbf{6.77 ounces of centrifuged mixture "smashed being alert"} together into the form of a usable \textbf{something that can notify}.
\end{enumerate}
\newpage
\section{Something that can prefer}How to make \textbf{something that can prefer} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 ideas of being favorite
\item 
14.62 ounces of favor
\item 
1.17 ounces of preference
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Vessel
\item 
Pet hummingbird
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{14.62 ounces of favor} into the vessel.
\item 
Put \textbf{8 ideas of being favorite} into the rotating centrifuge.
\item 
Put \textbf{1.17 ounces of preference} into the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Let the vessel cool down.
\item 
Pet your pet hummingbird.
\item 
Stop the centrifuge and retrieve the \textbf{8.35 ounces of centrifuged mixture "being favorite"}.
\item 
Retrieve the \textbf{3.77 spoonful of ashes of "preference"} from the fireplace.
\item 
Pour out the mixture from the vessel to get the \textbf{7.91 spoonful of vessel mixture "favor"}.
\item 
Use nails to join the \textbf{8.35 ounces of centrifuged mixture "being favorite"}, \textbf{3.77 spoonful of ashes of "preference"} and \textbf{7.91 spoonful of vessel mixture "favor"} together into the shape of a perfectly functional \textbf{something that can prefer}.
\end{enumerate}
\newpage
\section{Something that can prosper}How to make \textbf{something that can prosper} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.91 ounces of harvest
\item 
24 successors
\item 
7.47 ounces of growth
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Stir the cauldron.
\item 
Put \textbf{7.47 ounces of growth} into the rotating centrifuge.
\item 
Put \textbf{4.91 ounces of harvest} into the cauldron.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{12.19 ounces of centrifuged mixture "growth"}.
\item 
Pour out the mixture from the cauldron to get the \textbf{41.33 spoonful of cauldron mixture "harvest"}.
\item 
Fold the \textbf{24 successors}, \textbf{12.19 ounces of centrifuged mixture "growth"} and \textbf{41.33 spoonful of cauldron mixture "harvest"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{something that can prosper}.
\end{enumerate}
\newpage
\section{Something that can snatch}How to make \textbf{something that can snatch} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
17 vague notions of grab
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Cauldron
\item 
Fireplace
\item 
Bucket with ice-cold liquid
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{17 vague notions of grab} with the purifier.
\item 
Dip \textbf{17 purified vague notions of grab} into the bucket with ice-cold liquid.
\item 
Hold \textbf{17 purified and wet vague notions of grab} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{17 purified, wet and slightly burned vague notions of grab} into the cauldron.
\item 
Heat the cauldron.
\item 
Wait.
\item 
Fan the flames of the fireplace.
\item 
Pour out the mixture from the cauldron to get the \textbf{29.49 spoonful of cauldron mixture "purified, wet and slightly burned grab"}.
\item 
Fold the \textbf{29.49 spoonful of cauldron mixture "purified, wet and slightly burned grab"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{something that can snatch}.
\end{enumerate}
\newpage
\section{Something that can soothe}How to make \textbf{something that can soothe} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 ideas of caress
\item 
8.03 ounces of comfort
\item 
9 clear concepts of rub
\item 
18.8 ounces of solace
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\item 
Fireplace
\item 
Stone
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8.03 ounces of comfort} into the rotating centrifuge.
\item 
Crack \textbf{18.8 ounces of solace} with the stone.
\item 
Heat the container.
\item 
Put \textbf{9 clear concepts of rub} into the fireplace.
\item 
Crack \textbf{18.8 ounces of cracked solace} with the stone.
\item 
Stop the centrifuge and retrieve the \textbf{9.28 spoonful of centrifuged mixture "comfort"}.
\item 
Retrieve the \textbf{8.04 spoonful of ashes of "rub"} from the fireplace.
\item 
Fold the \textbf{3 ideas of caress}, \textbf{18.8 ounces of crushed solace}, \textbf{9.28 spoonful of centrifuged mixture "comfort"} and \textbf{8.04 spoonful of ashes of "rub"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in \textbf{something that can soothe}.
\end{enumerate}
\newpage
\section{Something that can stolen}How to make \textbf{something that can stolen} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.09 spoonful of wallet
\item 
1 slip
\item 
28.55 ounces of purse
\item 
7 bases
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bonfire
\item 
Vessel
\item 
Mortar
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7 bases} into the rotating centrifuge.
\item 
Wait for a minute.
\item 
Put \textbf{28.55 ounces of purse} into the vessel.
\item 
Hold \textbf{8.09 spoonful of wallet} briefly into the bonfire to burn them a bit.
\item 
Smash \textbf{1 slip} with the mortar.
\item 
Fan the flames of the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{6.79 spoonful of centrifuged mixture "base"}.
\item 
Pour out the mixture from the vessel to get the \textbf{7.72 spoonful of vessel mixture "purse"}.
\item 
Dump the \textbf{8.09 spoonful of slightly burned wallet}, \textbf{1 smashed slip}, \textbf{6.79 spoonful of centrifuged mixture "base"} and \textbf{7.72 spoonful of vessel mixture "purse"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{something that can stolen}.
\end{enumerate}
\newpage
\section{Something that can swap}How to make \textbf{something that can swap} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
34.26 spoonful of exchange
\item 
6 trades
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Bonfire
\item 
Cauldron
\item 
Pet dog
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{6 trades} into the cauldron.
\item 
Hold \textbf{34.26 spoonful of exchange} briefly into the bonfire to burn them a bit.
\item 
Put \textbf{34.26 spoonful of slightly burned exchange} into the rotating centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Heat the cauldron.
\item 
Let the cauldron cool down.
\item 
Pet your pet dog.
\item 
Pour out the mixture from the cauldron to get the \textbf{12.83 ounces of cauldron mixture "trade"}.
\item 
Stop the centrifuge and retrieve the \textbf{9.26 ounces of centrifuged mixture "slightly burned exchange"}.
\item 
Use tape to join the \textbf{12.83 ounces of cauldron mixture "trade"} and \textbf{9.26 ounces of centrifuged mixture "slightly burned exchange"} together into the form of a usable \textbf{something that can swap}.
\end{enumerate}
\newpage
\section{Something that can testify}How to make \textbf{something that can testify} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
26 witnesses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Bucket with hot liquid
\item 
Centrifuge
\item 
Familiar dog
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{26 witnesses} into the bucket with hot liquid.
\item 
Put \textbf{26 wet witnesses} into the rotating centrifuge.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Wait.
\item 
Stir the cauldron.
\item 
Pet your familiar dog.
\item 
Heat the cauldron.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{23.61 ounces of centrifuged mixture "wet witness"}.
\item 
Fold the \textbf{23.61 ounces of centrifuged mixture "wet witness"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{something that can testify}.
\end{enumerate}
\newpage
\section{Something untrue}How to make \textbf{something untrue} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
14.13 ounces of not
\item 
5.14 spoonful of myth
\item 
2 vague notions of being true
\item 
33.83 ounces of disbelief
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Fireplace
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{33.83 ounces of disbelief} into the freezer for a while.
\item 
Wait for 5 minutes.
\item 
Purify \textbf{2 vague notions of being true} with the purifier.
\item 
Put \textbf{2 purified vague notions of being true} into the freezer for a while.
\item 
Hold \textbf{5.14 spoonful of myth} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{2 purified and cooled vague notions of being true} into the fireplace.
\item 
Put \textbf{33.83 ounces of cooled disbelief} into the freezer for a while.
\item 
Hold \textbf{33.83 ounces of frozen disbelief} briefly into the fireplace to burn them a bit.
\item 
Retrieve the \textbf{14.77 spoonful of ashes of "purified and cooled being true"} from the fireplace.
\item 
Fold the \textbf{14.13 ounces of not}, \textbf{5.14 spoonful of slightly burned myth}, \textbf{33.83 ounces of frozen and slightly burned disbelief} and \textbf{14.77 spoonful of ashes of "purified and cooled being true"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in \textbf{something untrue}.
\end{enumerate}
\newpage
\section{Something wild}How to make \textbf{something wild} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16.49 spoonful of buck
\item 
6 clear concepts of being abstract
\item 
14.42 spoonful of raccoon
\item 
4 clear concepts of being west
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Mortar
\item 
Purifier
\item 
Centrifuge
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a very long time.
\item 
Let the vessel cool down.
\item 
Put \textbf{16.49 spoonful of buck} into the rotating centrifuge.
\item 
Heat the vessel.
\item 
Purify \textbf{4 clear concepts of being west} with the purifier.
\item 
Stir the vessel.
\item 
Smash \textbf{6 clear concepts of being abstract} with the mortar.
\item 
Stop the centrifuge and retrieve the \textbf{7.33 spoonful of centrifuged mixture "buck"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a cross into the circle and place \textbf{6 smashed clear concepts of being abstract}, \textbf{14.42 spoonful of raccoon}, \textbf{4 purified clear concepts of being west} and \textbf{7.33 spoonful of centrifuged mixture "buck"} on each corner.
\item 
Intone the following spell: "Abscenteria xylos uno! Factor volus! Cet adtulus!"
\item 
Reluctantly, \textbf{something wild} will appear inside the circle.
\end{enumerate}
\newpage
\section{A soul}How to make a \textbf{soul} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
31 ideas of die
\item 
21.87 ounces of heart
\item 
24 ideas of being brave
\item 
7.67 ounces of essence
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{21.87 ounces of heart} into the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Hold \textbf{7.67 ounces of essence} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{31 ideas of die} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Retrieve the \textbf{21.48 spoonful of ashes of "heart"} from the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{5.71 ounces of centrifuged mixture "die"}.
\item 
Dump the \textbf{24 ideas of being brave}, \textbf{7.67 ounces of slightly burned essence}, \textbf{21.48 spoonful of ashes of "heart"} and \textbf{5.71 ounces of centrifuged mixture "die"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{soul}.
\end{enumerate}
\newpage
\section{A spatula}How to make a \textbf{spatula} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.76 spoonful of utensil
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Freezer
\item 
Cauldron
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4.76 spoonful of utensil} into the freezer for a while.
\item 
Wait for a short time.
\item 
Put \textbf{4.76 spoonful of cooled utensil} into the rotating centrifuge.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Speed up the centrifuge.
\item 
Stir the cauldron.
\item 
Wait.
\item 
Let the cauldron cool down.
\item 
Stop the centrifuge and retrieve the \textbf{5.2 ounces of centrifuged mixture "cooled utensil"}.
\item 
Use glue to join the \textbf{5.2 ounces of centrifuged mixture "cooled utensil"} together into the shape of a usable \textbf{spatula}.
\end{enumerate}
\newpage
\section{A splash}How to make a \textbf{splash} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9 puddles
\item 
51.03 spoonful of waves
\item 
44 vague notions of spill
\item 
5 clear concepts of diving
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Mortar
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{5 clear concepts of diving} with the mortar.
\item 
Put \textbf{44 vague notions of spill} into the bonfire.
\item 
Stir the cauldron.
\item 
Hold \textbf{9 puddles} briefly into the bonfire to burn them a bit.
\item 
Retrieve the \textbf{145.26 ounces of ashes of "spill"} from the bonfire.
\item 
Fold the \textbf{9 slightly burned puddles}, \textbf{51.03 spoonful of waves}, \textbf{5 smashed clear concepts of diving} and \textbf{145.26 ounces of ashes of "spill"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{splash}.
\end{enumerate}
\newpage
\section{A sprinkle}How to make a \textbf{sprinkle} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.24 ounces of dash
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Vessel
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{3.24 ounces of dash} into the vessel.
\item 
Fan the flames of the bonfire.
\item 
Heat the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{11.3 ounces of vessel mixture "dash"}.
\item 
Use glue to join the \textbf{11.3 ounces of vessel mixture "dash"} together into the shape of a perfectly functional \textbf{sprinkle}.
\end{enumerate}
\newpage
\section{A stairway}How to make a \textbf{stairway} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.7 ounces of steps
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.7 ounces of steps} into the bonfire.
\item 
Fan the flames of the bonfire.
\item 
Retrieve the \textbf{89.76 spoonful of ashes of "steps"} from the bonfire.
\item 
Fold the \textbf{89.76 spoonful of ashes of "steps"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{stairway}.
\end{enumerate}
\newpage
\section{A stars}How to make a \textbf{stars} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
13 horoscopes
\item 
7.11 ounces of midnight
\item 
1.18 ounces of mythology
\item 
7 venuses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with ionised water
\item 
Saw
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{7 venuses} into the bucket with ionised water.
\item 
Wait.
\item 
Use the saw to slice \textbf{1.18 ounces of mythology} into bits.
\item 
Dip \textbf{13 horoscopes} into the bucket with ionised water.
\item 
Wait.
\item 
Use the saw to slice \textbf{1.18 ounces of sliced mythology} into bits.
\item 
Purify \textbf{1.18 ounces of fragmented mythology} with the purifier.
\item 
Wait for a short time.
\item 
Dip \textbf{7.11 ounces of midnight} into the bucket with ionised water.
\item 
Use the saw to slice \textbf{13 wet horoscopes} into bits.
\item 
Dump the \textbf{13 wet and sliced horoscopes}, \textbf{7.11 ounces of wet midnight}, \textbf{1.18 ounces of fragmented and purified mythology} and \textbf{7 wet venuses} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{stars}.
\end{enumerate}
\newpage
\section{A steak}How to make a \textbf{steak} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.21 spoonful of ribs
\item 
2 meats
\item 
6.39 ounces of barbecue
\item 
23.15 spoonful of beef
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Pet mouse
\item 
Crayon
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2 meats} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{4.02 spoonful of centrifuged mixture "meat"}.
\item 
Let your pet mouse sniff at \textbf{7.21 spoonful of ribs}.
\item 
Put \textbf{23.15 spoonful of beef} into the rotating centrifuge.
\item 
Pet your pet mouse.
\item 
Stop the centrifuge and retrieve the \textbf{4.18 spoonful of centrifuged mixture "beef"}.
\item 
Draw a magic circle on the floor using the crayon.
\item 
Draw a cross into the circle and place \textbf{7.21 spoonful of ribs}, \textbf{6.39 ounces of barbecue}, \textbf{4.02 spoonful of centrifuged mixture "meat"} and \textbf{4.18 spoonful of centrifuged mixture "beef"} on each corner.
\item 
Chant the following spell: "Dicto! Tratio! Ingurigo colatio herotatio!"
\item 
Reluctantly, a \textbf{steak} will appear inside the circle.
\end{enumerate}
\newpage
\section{Steam}How to make \textbf{steam} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 mists
\item 
3 clear concepts of boil
\item 
27.65 ounces of vapor
\item 
3.45 ounces of geyser
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Saw
\item 
Bucket with hot liquid
\item 
Vessel
\item 
Purifier
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{3.45 ounces of geyser} into bits.
\item 
Let the vessel cool down.
\item 
Put \textbf{6 mists} into the rotating centrifuge.
\item 
Put \textbf{27.65 ounces of vapor} into the vessel.
\item 
Speed up the centrifuge.
\item 
Pour out the mixture from the vessel to get the \textbf{11.51 spoonful of vessel mixture "vapor"}.
\item 
Purify \textbf{3.45 ounces of sliced geyser} with the purifier.
\item 
Dip \textbf{11.51 spoonful of vessel mixture "vapor"} into the bucket with hot liquid.
\item 
Stop the centrifuge and retrieve the \textbf{6.62 spoonful of centrifuged mixture "mist"}.
\item 
Use nails to join the \textbf{3 clear concepts of boil}, \textbf{3.45 ounces of sliced and purified geyser}, \textbf{11.51 spoonful of wet vessel mixture "vapor"} and \textbf{6.62 spoonful of centrifuged mixture "mist"} together into the shape of a passable \textbf{steam}.
\end{enumerate}
\newpage
\section{A stem}How to make a \textbf{stem} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.33 spoonful of branch
\item 
10 cherries
\item 
10.07 spoonful of flower
\item 
29 roots
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Centrifuge
\item 
Saw
\item 
Cauldron
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{5.33 spoonful of branch} into bits.
\item 
Hold \textbf{10 cherries} briefly into the fireplace to burn them a bit.
\item 
Heat the cauldron.
\item 
Stir the cauldron.
\item 
Let the cauldron cool down.
\item 
Put \textbf{5.33 spoonful of sliced branch} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{5.53 ounces of centrifuged mixture "sliced branch"}.
\item 
Use screws to join the \textbf{10 slightly burned cherries}, \textbf{10.07 spoonful of flower}, \textbf{29 roots} and \textbf{5.53 ounces of centrifuged mixture "sliced branch"} together into the form of a beautiful \textbf{stem}.
\end{enumerate}
\newpage
\section{A stink}How to make a \textbf{stink} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
10 smells
\item 
19.95 spoonful of lurch
\item 
25.18 spoonful of sardine
\item 
9.44 spoonful of odor
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Saw
\item 
Bucket with ionised water
\item 
Hammer
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{25.18 spoonful of sardine} with the hammer.
\item 
Wait.
\item 
Hold \textbf{25.18 spoonful of smashed sardine} briefly into the bonfire to burn them a bit.
\item 
Use the saw to slice \textbf{9.44 spoonful of odor} into bits.
\item 
Dip \textbf{19.95 spoonful of lurch} into the bucket with ionised water.
\item 
Use glue to join the \textbf{10 smells}, \textbf{19.95 spoonful of wet lurch}, \textbf{25.18 spoonful of smashed and slightly burned sardine} and \textbf{9.44 spoonful of sliced odor} together into the shape of a passable \textbf{stink}.
\end{enumerate}
\newpage
\section{A stone}How to make a \textbf{stone} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.67 ounces of pebble
\item 
36.98 ounces of lime
\item 
15.05 spoonful of emerald
\item 
45.88 spoonful of cobbler
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Centrifuge
\item 
Mortar
\item 
Saw
\item 
Fireplace
\item 
Pet dog
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{6.67 ounces of pebble} with the mortar.
\item 
Feed \textbf{15.05 spoonful of emerald} to your pet dog.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{36.98 ounces of lime} into the rotating centrifuge.
\item 
Put \textbf{45.88 spoonful of cobbler} into the freezer for a while.
\item 
Feed \textbf{45.88 spoonful of cooled cobbler} to your pet dog.
\item 
Crack \textbf{6.67 ounces of cracked pebble} with the mortar.
\item 
Smash \textbf{6.67 ounces of crushed pebble} with the mortar.
\item 
Use the saw to slice \textbf{6.67 ounces of crushed and smashed pebble} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{4.45 spoonful of centrifuged mixture "lime"}.
\item 
Wait until your pet dog poops. Receive \textbf{14.14 ounces of a very dirty pile of "emerald and cooled cobbler"}.
\item 
Use screws to join the \textbf{6.67 ounces of crushed, smashed and sliced pebble}, \textbf{4.45 spoonful of centrifuged mixture "lime"} and \textbf{14.14 ounces of a very dirty pile of "emerald and cooled cobbler"} together into the shape of a beautiful \textbf{stone}.
\end{enumerate}
\newpage
\section{A strategy}How to make a \textbf{strategy} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.23 ounces of plan
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a rather short time.
\item 
Put \textbf{6.23 ounces of plan} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Wait.
\item 
Stop the centrifuge and retrieve the \textbf{15.95 ounces of centrifuged mixture "plan"}.
\item 
Put \textbf{15.95 ounces of centrifuged mixture "plan"} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{2.71 spoonful of centrifuged mixture "centrifuged mixture "plan""}.
\item 
Fold the \textbf{2.71 spoonful of centrifuged mixture "centrifuged mixture "plan""} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{strategy}.
\end{enumerate}
\newpage
\section{A structure}How to make a \textbf{structure} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.96 ounces of architecture
\item 
23 sentences
\item 
14 ideas of build
\item 
21 buildings
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{14 ideas of build} into the vessel.
\item 
Wait.
\item 
Stir the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{4.61 spoonful of vessel mixture "build"}.
\item 
Wait.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Put \textbf{7.96 ounces of architecture} into the freezer for a while.
\item 
Heat the vessel.
\item 
Fold the \textbf{7.96 ounces of cooled architecture}, \textbf{23 sentences}, \textbf{21 buildings} and \textbf{4.61 spoonful of vessel mixture "build"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{structure}.
\end{enumerate}
\newpage
\section{A sub}How to make a \textbf{sub} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
21 vague notions of being italian
\item 
3.65 spoonful of meatballs
\item 
8.77 ounces of subway
\item 
8.47 spoonful of below
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Container
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{8.77 ounces of subway} into bits.
\item 
Stir the container.
\item 
Put \textbf{8.77 ounces of sliced subway} into the container.
\item 
Heat the container.
\item 
Stir the container.
\item 
Wait for 6 days.
\item 
Pour out the mixture from the container to get the \textbf{7.33 ounces of container mixture "sliced subway"}.
\item 
Fold the \textbf{21 vague notions of being italian}, \textbf{3.65 spoonful of meatballs}, \textbf{8.47 spoonful of below} and \textbf{7.33 ounces of container mixture "sliced subway"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{sub}.
\end{enumerate}
\newpage
\section{A subway}How to make a \textbf{subway} in 16 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.45 ounces of sub
\item 
2.63 spoonful of submarine
\item 
20 clear concepts of being underground
\item 
2.55 spoonful of tunnel
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Vessel
\item 
Fireplace
\item 
Fountain pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{20 clear concepts of being underground} into the rotating centrifuge.
\item 
Put \textbf{2.63 spoonful of submarine} into the rotating centrifuge.
\item 
Fan the flames of the fireplace.
\item 
Put \textbf{7.45 ounces of sub} into the fireplace.
\item 
Stop the centrifuge and retrieve the \textbf{1.8 ounces of centrifuged mixture "being underground and submarine"}.
\item 
Put \textbf{2.55 spoonful of tunnel} into the fireplace.
\item 
Put \textbf{1.8 ounces of centrifuged mixture "being underground and submarine"} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{16.74 ounces of centrifuged mixture "centrifuged mixture "being underground and submarine""}.
\item 
Put \textbf{16.74 ounces of centrifuged mixture "centrifuged mixture "being underground and submarine""} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{75.95 spoonful of vessel mixture "centrifuged mixture "centrifuged mixture "being underground and submarine"""}.
\item 
Retrieve the \textbf{5.22 spoonful of ashes of "sub and tunnel"} from the fireplace.
\item 
Draw a magic circle on the floor using the fountain pen.
\item 
Draw a line into the circle and place \textbf{75.95 spoonful of vessel mixture "centrifuged mixture "centrifuged mixture "being underground and submarine"""} and \textbf{5.22 spoonful of ashes of "sub and tunnel"} on each end.
\item 
Whisper the following spell: "Bur!"
\item 
Reluctantly, a \textbf{subway} will appear inside the circle.
\end{enumerate}
\newpage
\section{Success}How to make \textbf{success} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8 professions
\item 
7.9 ounces of achiever
\item 
9.06 ounces of failure
\item 
7 vague notions of turn
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with clean liquid
\item 
Container
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.06 ounces of failure} into the container.
\item 
Put \textbf{8 professions} into the freezer for a while.
\item 
Dip \textbf{8 cooled professions} into the bucket with clean liquid.
\item 
Wait.
\item 
Put \textbf{7 vague notions of turn} into the container.
\item 
Dip \textbf{7.9 ounces of achiever} into the bucket with clean liquid.
\item 
Pour out the mixture from the container to get the \textbf{3.39 spoonful of container mixture "failure and turn"}.
\item 
Put \textbf{3.39 spoonful of container mixture "failure and turn"} into the freezer for a while.
\item 
Put \textbf{8 cooled and wet professions} into the container.
\item 
Pour out the mixture from the container to get the \textbf{6.22 spoonful of container mixture "cooled and wet profession"}.
\item 
Dump the \textbf{7.9 ounces of wet achiever}, \textbf{3.39 spoonful of cooled container mixture "failure and turn"} and \textbf{6.22 spoonful of container mixture "cooled and wet profession"} into a pile on the floor.
\item 
Wait until they magically transform into \textbf{success}.
\end{enumerate}
\newpage
\section{A suck}How to make a \textbf{suck} in 4 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.21 ounces of lap
\item 
5.26 spoonful of lollipop
\item 
18.21 spoonful of slurp
\item 
16.64 ounces of succor
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1.21 ounces of lap} into the fireplace.
\item 
Put \textbf{16.64 ounces of succor} into the fireplace.
\item 
Retrieve the \textbf{9.25 ounces of ashes of "lap and succor"} from the fireplace.
\item 
Use glue to join the \textbf{5.26 spoonful of lollipop}, \textbf{18.21 spoonful of slurp} and \textbf{9.25 ounces of ashes of "lap and succor"} together into the shape of a usable \textbf{suck}.
\end{enumerate}
\newpage
\section{Sugar}How to make \textbf{sugar} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 clear concepts of dissolve
\item 
28 spoons
\item 
3.45 spoonful of flour
\item 
196 syrups
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Fireplace
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{3.45 spoonful of flour} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{28 spoons} into the fireplace.
\item 
Retrieve the \textbf{3.09 ounces of ashes of "spoon"} from the fireplace.
\item 
Put \textbf{2 clear concepts of dissolve} into the fireplace.
\item 
Wait for a very long time.
\item 
Crack \textbf{3.09 ounces of ashes of "spoon"} with the hammer.
\item 
Retrieve the \textbf{1.61 spoonful of ashes of "dissolve"} from the fireplace.
\item 
Fold the \textbf{3.45 spoonful of slightly burned flour}, \textbf{196 syrups}, \textbf{3.09 ounces of cracked ashes of "spoon"} and \textbf{1.61 spoonful of ashes of "dissolve"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in \textbf{sugar}.
\end{enumerate}
\newpage
\section{A suitcase}How to make a \textbf{suitcase} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.06 ounces of trunk
\item 
36 cases
\item 
4.34 ounces of luggage
\item 
8 briefcases
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with clean liquid
\item 
Bonfire
\item 
Centrifuge
\item 
Freezer
\item 
Container
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for a short time.
\item 
Put \textbf{5.06 ounces of trunk} into the bonfire.
\item 
Let the container cool down.
\item 
Put \textbf{8 briefcases} into the freezer for a while.
\item 
Put \textbf{4.34 ounces of luggage} into the bonfire.
\item 
Wait.
\item 
Put \textbf{36 cases} into the rotating centrifuge.
\item 
Dip \textbf{8 cooled briefcases} into the bucket with clean liquid.
\item 
Put \textbf{8 cooled and wet briefcases} into the container.
\item 
Retrieve the \textbf{4.26 ounces of ashes of "trunk and luggage"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{6.71 spoonful of centrifuged mixture "case"}.
\item 
Pour out the mixture from the container to get the \textbf{24.42 spoonful of container mixture "cooled and wet briefcase"}.
\item 
Use nails to join the \textbf{4.26 ounces of ashes of "trunk and luggage"}, \textbf{6.71 spoonful of centrifuged mixture "case"} and \textbf{24.42 spoonful of container mixture "cooled and wet briefcase"} together into the shape of a perfectly functional \textbf{suitcase}.
\end{enumerate}
\newpage
\section{A surgery}How to make a \textbf{surgery} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.8 ounces of scalpel
\item 
2.83 spoonful of operation
\item 
18 glove
\item 
2.33 ounces of surgeon
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Bonfire
\item 
Purifier
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{18 glove} into the rotating centrifuge.
\item 
Purify \textbf{2.83 spoonful of operation} with the purifier.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{4.8 ounces of scalpel} into the bonfire.
\item 
Use the saw to slice \textbf{2.33 ounces of surgeon} into bits.
\item 
Speed up the centrifuge.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{2.83 spoonful of purified operation} into the bonfire.
\item 
Retrieve the \textbf{34.64 ounces of ashes of "scalpel and purified operation"} from the bonfire.
\item 
Stop the centrifuge and retrieve the \textbf{10.96 spoonful of centrifuged mixture "gloves"}.
\item 
Dump the \textbf{2.33 ounces of sliced surgeon}, \textbf{34.64 ounces of ashes of "scalpel and purified operation"} and \textbf{10.96 spoonful of centrifuged mixture "gloves"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{surgery}.
\end{enumerate}
\newpage
\section{A surroundings}How to make a \textbf{surroundings} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.58 spoonful of circumstance
\item 
43.62 spoonful of environment
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Vessel
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2.58 spoonful of circumstance} into the vessel.
\item 
Put \textbf{43.62 spoonful of environment} into the freezer for a while.
\item 
Wait for an hour.
\item 
Fan the flames of the fireplace.
\item 
Let the vessel cool down.
\item 
Pour out the mixture from the vessel to get the \textbf{1.35 ounces of vessel mixture "circumstance"}.
\item 
Fold the \textbf{43.62 spoonful of cooled environment} and \textbf{1.35 ounces of vessel mixture "circumstance"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{surroundings}.
\end{enumerate}
\newpage
\section{A swallow}How to make a \textbf{swallow} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 vague notions of spit
\item 
8.95 ounces of drink
\item 
9.46 ounces of death
\item 
9.41 spoonful of gulp
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Fireplace
\item 
Vessel
\item 
Hammer
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{9.46 ounces of death} into the rotating centrifuge.
\item 
Hold \textbf{8.95 ounces of drink} briefly into the fireplace to burn them a bit.
\item 
Smash \textbf{6 vague notions of spit} with the hammer.
\item 
Stop the centrifuge and retrieve the \textbf{147.84 spoonful of centrifuged mixture "death"}.
\item 
Put \textbf{8.95 ounces of slightly burned drink} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stir the vessel.
\item 
Stop the centrifuge and retrieve the \textbf{3.54 spoonful of centrifuged mixture "slightly burned drink"}.
\item 
Use tape to join the \textbf{6 smashed vague notions of spit}, \textbf{9.41 spoonful of gulp}, \textbf{147.84 spoonful of centrifuged mixture "death"} and \textbf{3.54 spoonful of centrifuged mixture "slightly burned drink"} together into the form of a beautiful \textbf{swallow}.
\end{enumerate}
\newpage
\section{A swan}How to make a \textbf{swan} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2.08 spoonful of grace
\item 
1 geese
\item 
3 ideas of duck
\item 
5.03 spoonful of gracefulness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Saw
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Heat the vessel.
\item 
Wait.
\item 
Use the saw to slice \textbf{1 geese} into bits.
\item 
Stir the vessel.
\item 
Put \textbf{1 sliced geese} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{7.43 spoonful of vessel mixture "sliced geese"}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a cross into the circle and place \textbf{2.08 spoonful of grace}, \textbf{3 ideas of duck}, \textbf{5.03 spoonful of gracefulness} and \textbf{7.43 spoonful of vessel mixture "sliced geese"} on each corner.
\item 
Intone the following spell: "Coemidilis cens aemerodosus! Quarius subviator antia! Relleum tratio!"
\item 
Reluctantly, a \textbf{swan} will appear inside the circle.
\end{enumerate}
\newpage
\section{A swiss}How to make a \textbf{swiss} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.42 ounces of cheddar
\item 
7.72 ounces of cheese
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Cauldron
\item 
Graphite pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Stir the cauldron.
\item 
Hold \textbf{7.72 ounces of cheese} briefly into the bonfire to burn them a bit.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Put \textbf{7.72 ounces of slightly burned cheese} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{13.77 ounces of centrifuged mixture "slightly burned cheese"}.
\item 
Draw a magic circle on the floor using the graphite pencil.
\item 
Draw a line into the circle and place \textbf{1.42 ounces of cheddar} and \textbf{13.77 ounces of centrifuged mixture "slightly burned cheese"} on each end.
\item 
Whisper the following spell: "Zizyfumerium proro lantumnis, coctritor!"
\item 
Suddendly, a \textbf{swiss} will appear inside the circle.
\end{enumerate}
\newpage
\section{A tear}How to make a \textbf{tear} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 ideas of sobbing
\item 
6 clear concepts of break
\item 
6.91 spoonful of damage
\item 
7.25 spoonful of sadness
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Saw
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{6.91 spoonful of damage} into bits.
\item 
Purify \textbf{6.91 spoonful of sliced damage} with the purifier.
\item 
Wait for a short time.
\item 
Use the saw to slice \textbf{3 ideas of sobbing} into bits.
\item 
Purify \textbf{6 clear concepts of break} with the purifier.
\item 
Wait for a rather long time.
\item 
Use the saw to slice \textbf{7.25 spoonful of sadness} into bits.
\item 
Throw \textbf{6.91 spoonful of sliced and purified damage} away.
\item 
Purify \textbf{3 sliced ideas of sobbing} with the purifier.
\item 
Use nails to join the \textbf{3 sliced and purified ideas of sobbing}, \textbf{6 purified clear concepts of break} and \textbf{7.25 spoonful of sliced sadness} together into the shape of a beautiful \textbf{tear}.
\end{enumerate}
\newpage
\section{A theme}How to make a \textbf{theme} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 subject
\item 
3.02 spoonful of slogan
\item 
11.14 ounces of plot
\item 
7 topics
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Saw
\item 
Freezer
\item 
Bucket with ionised liquid
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{11.14 ounces of plot} into the bucket with ionised liquid.
\item 
Put \textbf{7 topics} into the freezer for a while.
\item 
Let the cauldron cool down.
\item 
Dip \textbf{7 cooled topics} into the bucket with ionised liquid.
\item 
Use the saw to slice \textbf{7 cooled and wet topics} into bits.
\item 
Fold the \textbf{1 subject}, \textbf{3.02 spoonful of slogan}, \textbf{11.14 ounces of wet plot} and \textbf{7 cooled, wet and sliced topics} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{theme}.
\end{enumerate}
\newpage
\section{A thermometer}How to make a \textbf{thermometer} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.67 ounces of fever
\item 
7 celsiuses
\item 
2.26 spoonful of temperature
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Cauldron
\item 
Familiar chinchilla
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Heat the cauldron.
\item 
Feed \textbf{2.26 spoonful of temperature} to your familiar chinchilla.
\item 
Let the cauldron cool down.
\item 
Heat the cauldron.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{1.67 ounces of fever} into the bonfire.
\item 
Retrieve the \textbf{1.54 spoonful of ashes of "fever"} from the bonfire.
\item 
Wait until your familiar chinchilla poops. Receive \textbf{3.15 ounces of a very dirty pile of "temperature"}.
\item 
Fold the \textbf{7 celsiuses}, \textbf{1.54 spoonful of ashes of "fever"} and \textbf{3.15 ounces of a very dirty pile of "temperature"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{thermometer}.
\end{enumerate}
\newpage
\section{A thesaurus}How to make a \textbf{thesaurus} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1 encyclopedia
\item 
3.99 ounces of dictionary
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{1 encyclopedia} briefly into the bonfire to burn it a bit.
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{3.99 ounces of dictionary} into the bonfire.
\item 
Retrieve the \textbf{20.78 ounces of ashes of "dictionary"} from the bonfire.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a line into the circle and place \textbf{1 slightly burned encyclopedia} and \textbf{20.78 ounces of ashes of "dictionary"} on each end.
\item 
Whisper the following spell: "Pophesia compernego incohaero!"
\item 
Reluctantly, a \textbf{thesaurus} will appear inside the circle.
\end{enumerate}
\newpage
\section{A thick}How to make a \textbf{thick} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4 thinnesses
\item 
19.74 spoonful of layer
\item 
46.23 spoonful of fog
\item 
8.66 ounces of cream
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Mortar
\item 
Bonfire
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8.66 ounces of cream} into the bonfire.
\item 
Hold \textbf{46.23 spoonful of fog} briefly into the bonfire to burn them a bit.
\item 
Smash \textbf{19.74 spoonful of layer} with the mortar.
\item 
Put \textbf{19.74 spoonful of smashed layer} into the cauldron.
\item 
Stir the cauldron.
\item 
Wait.
\item 
Put \textbf{46.23 spoonful of slightly burned fog} into the bonfire.
\item 
Pour out the mixture from the cauldron to get the \textbf{5.2 spoonful of cauldron mixture "smashed layer"}.
\item 
Retrieve the \textbf{4.4 ounces of ashes of "cream and slightly burned fog"} from the bonfire.
\item 
Use screws to join the \textbf{4 thinnesses}, \textbf{5.2 spoonful of cauldron mixture "smashed layer"} and \textbf{4.4 ounces of ashes of "cream and slightly burned fog"} together into the form of a usable \textbf{thick}.
\end{enumerate}
\newpage
\section{A thimble}How to make a \textbf{thimble} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
25 vague notions of tumble
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Bucket with hot water
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Dip \textbf{25 vague notions of tumble} into the bucket with hot water.
\item 
Smash \textbf{25 wet vague notions of tumble} with the hammer.
\item 
Crack \textbf{25 wet and smashed vague notions of tumble} with the hammer.
\item 
Dip \textbf{25 wet, smashed and cracked vague notions of tumble} into the bucket with hot water.
\item 
Wait.
\item 
Crack \textbf{25 very wet, smashed and cracked vague notions of tumble} with the hammer.
\item 
Use glue to join the \textbf{25 very wet, smashed and crushed vague notions of tumble} together into the shape of a passable \textbf{thimble}.
\end{enumerate}
\newpage
\section{A thing}How to make a \textbf{thing} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
4.93 spoonful of element
\item 
2 vague notions of being specific
\item 
9.6 ounces of sureness
\item 
10 somes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bucket with water
\item 
Saw
\item 
Centrifuge
\item 
Container
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait for 3 hours.
\item 
Put \textbf{2 vague notions of being specific} into the rotating centrifuge.
\item 
Let the container cool down.
\item 
Stir the container.
\item 
Dip \textbf{4.93 spoonful of element} into the bucket with water.
\item 
Heat the container.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Use the saw to slice \textbf{4.93 spoonful of wet element} into bits.
\item 
Stop the centrifuge and retrieve the \textbf{7.41 ounces of centrifuged mixture "being specific"}.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a square into the circle and place \textbf{4.93 spoonful of wet and sliced element}, \textbf{9.6 ounces of sureness}, \textbf{10 somes} and \textbf{7.41 ounces of centrifuged mixture "being specific"} on each corner.
\item 
Intone the following spell: "Applectio! Vimentum arnea coxum corsitus bellicor, conporticia desco! Emius conculus! Chlossator disco aparius, patus inatum!"
\item 
Slowly, a \textbf{thing} will appear inside the circle.
\end{enumerate}
\newpage
\section{A tile}How to make a \textbf{tile} in 4 easy steps:

\subsection{Materials}\begin{itemize}
\item 
15.28 spoonful of carpet
\item 
18 porcelains
\item 
9.64 ounces of floor
\item 
28.57 ounces of shingle
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Cauldron
\item 
Fireplace
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Stir the cauldron.
\item 
Hold \textbf{9.64 ounces of floor} briefly into the fireplace to burn them a bit.
\item 
Hold \textbf{18 porcelains} briefly into the fireplace to burn them a bit.
\item 
Use glue to join the \textbf{15.28 spoonful of carpet}, \textbf{18 slightly burned porcelains}, \textbf{9.64 ounces of slightly burned floor} and \textbf{28.57 ounces of shingle} together into the form of a beautiful \textbf{tile}.
\end{enumerate}
\newpage
\section{A tomato}How to make a \textbf{tomato} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.67 ounces of garden
\item 
12.42 ounces of paste
\item 
34 lettuces
\item 
2 radishes
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Cauldron
\item 
Bonfire
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{2 radishes} briefly into the bonfire to burn them a bit.
\item 
Smash \textbf{8.67 ounces of garden} with the hammer.
\item 
Crack \textbf{12.42 ounces of paste} with the hammer.
\item 
Let the cauldron cool down.
\item 
Wait.
\item 
Fold the \textbf{8.67 ounces of smashed garden}, \textbf{12.42 ounces of cracked paste}, \textbf{34 lettuces} and \textbf{2 slightly burned radishes} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{tomato}.
\end{enumerate}
\newpage
\section{A touch}How to make a \textbf{touch} in 8 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16 clear concepts of hold
\item 
5 ideas of being tangent
\item 
4 ideas of handle
\item 
23.51 ounces of close
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{5 ideas of being tangent} with the hammer.
\item 
Crack \textbf{23.51 ounces of close} with the hammer.
\item 
Wait for an hour.
\item 
Put \textbf{4 ideas of handle} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{37.87 spoonful of centrifuged mixture "handle"}.
\item 
Dump the \textbf{16 clear concepts of hold}, \textbf{5 smashed ideas of being tangent}, \textbf{23.51 ounces of cracked close} and \textbf{37.87 spoonful of centrifuged mixture "handle"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{touch}.
\end{enumerate}
\newpage
\section{A trait}How to make a \textbf{trait} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.6 spoonful of custom
\item 
29 genes
\item 
10 uncommonnesses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Bonfire
\item 
Freezer
\item 
Bucket with water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Hold \textbf{8.6 spoonful of custom} briefly into the bonfire to burn them a bit.
\item 
Hold \textbf{29 genes} briefly into the bonfire to burn them a bit.
\item 
Use the saw to slice \textbf{8.6 spoonful of slightly burned custom} into bits.
\item 
Put \textbf{10 uncommonnesses} into the freezer for a while.
\item 
Fan the flames of the bonfire.
\item 
Wait for 10 minutes.
\item 
Dip \textbf{10 cooled uncommonnesses} into the bucket with water.
\item 
Fold the \textbf{8.6 spoonful of slightly burned and sliced custom}, \textbf{29 slightly burned genes} and \textbf{10 cooled and wet uncommonnesses} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{trait}.
\end{enumerate}
\newpage
\section{A trumpet}How to make a \textbf{trumpet} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
9.51 spoonful of flute
\item 
8.31 spoonful of clarinet
\item 
7.42 ounces of oboe
\item 
7.69 spoonful of instrument
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Freezer
\item 
Stone
\item 
Vessel
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{7.69 spoonful of instrument} into the vessel.
\item 
Smash \textbf{7.42 ounces of oboe} with the stone.
\item 
Put \textbf{7.42 ounces of smashed oboe} into the freezer for a while.
\item 
Let the vessel cool down.
\item 
Pour out the mixture from the vessel to get the \textbf{6.52 spoonful of vessel mixture "instrument"}.
\item 
Fold the \textbf{9.51 spoonful of flute}, \textbf{8.31 spoonful of clarinet}, \textbf{7.42 ounces of smashed and cooled oboe} and \textbf{6.52 spoonful of vessel mixture "instrument"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{trumpet}.
\end{enumerate}
\newpage
\section{A twin}How to make a \textbf{twin} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
8.93 spoonful of identicalness
\item 
6.44 ounces of alikeness
\item 
6 ideas of being duplicate
\item 
6 vague notions of being double
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Purifier
\item 
Glue
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Purify \textbf{6 ideas of being duplicate} with the purifier.
\item 
Put \textbf{6.44 ounces of alikeness} into the container.
\item 
Let the container cool down.
\item 
Pour out the mixture from the container to get the \textbf{2.32 spoonful of container mixture "alikeness"}.
\item 
Use glue to join the \textbf{8.93 spoonful of identicalness}, \textbf{6 purified ideas of being duplicate}, \textbf{6 vague notions of being double} and \textbf{2.32 spoonful of container mixture "alikeness"} together into the shape of a usable \textbf{twin}.
\end{enumerate}
\newpage
\section{A twist}How to make a \textbf{twist} in 10 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 clear concepts of turn
\item 
1 knot
\item 
10 ankles
\item 
25 ideas of spin
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Centrifuge
\item 
Container
\item 
Hammer
\item 
Freezer
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{1 knot} into the rotating centrifuge.
\item 
Put \textbf{2 clear concepts of turn} into the freezer for a while.
\item 
Crack \textbf{25 ideas of spin} with the hammer.
\item 
Let the container cool down.
\item 
Fan the flames of the bonfire.
\item 
Stir the container.
\item 
Heat the container.
\item 
Put \textbf{10 ankles} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{7.49 ounces of centrifuged mixture "knot and ankle"}.
\item 
Use tape to join the \textbf{2 cooled clear concepts of turn}, \textbf{25 cracked ideas of spin} and \textbf{7.49 ounces of centrifuged mixture "knot and ankle"} together into the form of a perfectly functional \textbf{twist}.
\end{enumerate}
\newpage
\section{An underground}How to make an \textbf{underground} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6.6 spoonful of subway
\item 
2.72 ounces of cave
\item 
7.7 spoonful of mole
\item 
2.53 spoonful of tunnel
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Saw
\item 
Stone
\item 
Tape
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Crack \textbf{2.72 ounces of cave} with the stone.
\item 
Use the saw to slice \textbf{2.53 spoonful of tunnel} into bits.
\item 
Smash \textbf{7.7 spoonful of mole} with the stone.
\item 
Purify \textbf{2.53 spoonful of sliced tunnel} with the purifier.
\item 
Crack \textbf{7.7 spoonful of smashed mole} with the stone.
\item 
Use tape to join the \textbf{6.6 spoonful of subway}, \textbf{2.72 ounces of cracked cave}, \textbf{7.7 spoonful of smashed and cracked mole} and \textbf{2.53 spoonful of sliced and purified tunnel} together into the form of a beautiful \textbf{underground}.
\end{enumerate}
\newpage
\section{An upstream}How to make an \textbf{upstream} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16 salmon
\item 
2 downstreams
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{16 salmon} briefly into the fireplace to burn them a bit.
\item 
Wait.
\item 
Purify \textbf{16 slightly burned salmon} with the purifier.
\item 
Put \textbf{16 slightly burned and purified salmon} into the fireplace.
\item 
Fan the flames of the fireplace.
\item 
Purify \textbf{2 downstreams} with the purifier.
\item 
Hold \textbf{2 purified downstreams} briefly into the fireplace to burn them a bit.
\item 
Retrieve the \textbf{8.06 spoonful of ashes of "slightly burned and purified salmon"} from the fireplace.
\item 
Put \textbf{2 purified and slightly burned downstreams} into the fireplace.
\item 
Put \textbf{8.06 spoonful of ashes of "slightly burned and purified salmon"} into the fireplace.
\item 
Retrieve the \textbf{45.61 spoonful of ashes of "purified and slightly burned downstream and ashes of "slightly burned and purified salmon""} from the fireplace.
\item 
Fold the \textbf{45.61 spoonful of ashes of "purified and slightly burned downstream and ashes of "slightly burned and purified salmon""} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in an \textbf{upstream}.
\end{enumerate}
\newpage
\section{A vanilla}How to make a \textbf{vanilla} in 6 easy steps:

\subsection{Materials}\begin{itemize}
\item 
15.67 spoonful of chocolate
\item 
2.71 ounces of pudding
\item 
8 clear concepts of shake
\item 
3 vague notions of being plain
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Saw
\item 
Purifier
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{2.71 ounces of pudding} into bits.
\item 
Wait for a very long time.
\item 
Purify \textbf{2.71 ounces of sliced pudding} with the purifier.
\item 
Stir the vessel.
\item 
Use the saw to slice \textbf{3 vague notions of being plain} into bits.
\item 
Use nails to join the \textbf{15.67 spoonful of chocolate}, \textbf{2.71 ounces of sliced and purified pudding}, \textbf{8 clear concepts of shake} and \textbf{3 sliced vague notions of being plain} together into the form of a perfectly functional \textbf{vanilla}.
\end{enumerate}
\newpage
\section{A vaseline}How to make a \textbf{vaseline} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
31.64 ounces of lubrication
\item 
12.17 ounces of petroleum
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Bucket with hot water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{31.64 ounces of lubrication} briefly into the fireplace to burn them a bit.
\item 
Fan the flames of the fireplace.
\item 
Dip \textbf{31.64 ounces of slightly burned lubrication} into the bucket with hot water.
\item 
Put \textbf{31.64 ounces of slightly burned and wet lubrication} into the fireplace.
\item 
Wait.
\item 
Put \textbf{12.17 ounces of petroleum} into the fireplace.
\item 
Retrieve the \textbf{37.38 spoonful of ashes of "slightly burned and wet lubrication and petroleum"} from the fireplace.
\item 
Fold the \textbf{37.38 spoonful of ashes of "slightly burned and wet lubrication and petroleum"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{vaseline}.
\end{enumerate}
\newpage
\section{A vice}How to make a \textbf{vice} in 5 easy steps:

\subsection{Materials}\begin{itemize}
\item 
14.25 spoonful of virtue
\item 
6 grips
\item 
4.2 ounces of clamp
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Bucket with clean water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Use the saw to slice \textbf{6 grips} into bits.
\item 
Dip \textbf{14.25 spoonful of virtue} into the bucket with clean water.
\item 
Wait.
\item 
Fold the \textbf{14.25 spoonful of wet virtue}, \textbf{6 sliced grips} and \textbf{4.2 ounces of clamp} together using advanced origami techniques.
\item 
If you've done it correctly, it should result in a \textbf{vice}.
\end{enumerate}
\newpage
\section{A victim}How to make a \textbf{victim} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
7.46 ounces of guiltlessness
\item 
2.36 spoonful of accident
\item 
6.71 ounces of accuser
\item 
10 clear concepts of suspect
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{2.36 spoonful of accident} into the rotating centrifuge.
\item 
Speed up the centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{8.25 ounces of centrifuged mixture "accident"}.
\item 
Put \textbf{8.25 ounces of centrifuged mixture "accident"} into the rotating centrifuge.
\item 
Put \textbf{7.46 ounces of guiltlessness} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{13.99 spoonful of centrifuged mixture "centrifuged mixture "accident" and guiltlessness"}.
\item 
Put \textbf{6.71 ounces of accuser} into the rotating centrifuge.
\item 
Fold the \textbf{10 clear concepts of suspect} and \textbf{13.99 spoonful of centrifuged mixture "centrifuged mixture "accident" and guiltlessness"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{victim}.
\end{enumerate}
\newpage
\section{A volt}How to make a \textbf{volt} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
95 shocks
\item 
1.41 ounces of electricity
\item 
73.26 ounces of watt
\item 
2 amps
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Fireplace
\item 
Centrifuge
\item 
Stone
\item 
Nails
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{2 amps} briefly into the fireplace to burn them a bit.
\item 
Put \textbf{1.41 ounces of electricity} into the rotating centrifuge.
\item 
Put \textbf{2 slightly burned amps} into the rotating centrifuge.
\item 
Crack \textbf{73.26 ounces of watt} with the stone.
\item 
Hold \textbf{95 shocks} briefly into the fireplace to burn them a bit.
\item 
Stop the centrifuge and retrieve the \textbf{4.69 spoonful of centrifuged mixture "electricity and slightly burned amp"}.
\item 
Use nails to join the \textbf{95 slightly burned shocks}, \textbf{73.26 ounces of cracked watt} and \textbf{4.69 spoonful of centrifuged mixture "electricity and slightly burned amp"} together into the form of a beautiful \textbf{volt}.
\end{enumerate}
\newpage
\section{A waffles}How to make a \textbf{waffles} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3.85 ounces of pancakes
\item 
23.02 spoonful of syrup
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Purifier
\item 
Bonfire
\item 
Mortar
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Purify \textbf{23.02 spoonful of syrup} with the purifier.
\item 
Crack \textbf{23.02 spoonful of purified syrup} with the mortar.
\item 
Heat the container.
\item 
Wait for a rather short time.
\item 
Fan the flames of the bonfire.
\item 
Heat the container.
\item 
Dump the \textbf{3.85 ounces of pancakes} and \textbf{23.02 spoonful of purified and cracked syrup} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{waffles}.
\end{enumerate}
\newpage
\section{A warrior}How to make a \textbf{warrior} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
2 fighters
\item 
7 weekends
\item 
5 vikings
\item 
1 clear concept of being brave
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Hammer
\item 
Vessel
\item 
Purifier
\item 
Screws
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Purify \textbf{2 fighters} with the purifier.
\item 
Crack \textbf{5 vikings} with the hammer.
\item 
Let the vessel cool down.
\item 
Put \textbf{2 purified fighters} into the vessel.
\item 
Crack \textbf{7 weekends} with the hammer.
\item 
Pour out the mixture from the vessel to get the \textbf{1.26 spoonful of vessel mixture "purified fighter"}.
\item 
Use screws to join the \textbf{7 cracked weekends}, \textbf{5 cracked vikings}, \textbf{1 clear concept of being brave} and \textbf{1.26 spoonful of vessel mixture "purified fighter"} together into the shape of a passable \textbf{warrior}.
\end{enumerate}
\newpage
\section{A weapon}How to make a \textbf{weapon} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
1.2 spoonful of pistol
\item 
7.86 ounces of gun
\item 
12 swords
\item 
3 daggers
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Hammer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Hold \textbf{1.2 spoonful of pistol} briefly into the bonfire to burn them a bit.
\item 
Wait for an hour.
\item 
Fan the flames of the bonfire.
\item 
Smash \textbf{3 daggers} with the hammer.
\item 
Wait for 3 days.
\item 
Dump the \textbf{1.2 spoonful of slightly burned pistol}, \textbf{7.86 ounces of gun}, \textbf{12 swords} and \textbf{3 smashed daggers} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{weapon}.
\end{enumerate}
\newpage
\section{A wife}How to make a \textbf{wife} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
29 clear concepts of marry
\item 
9.37 spoonful of daughter
\item 
16.11 spoonful of spouse
\item 
28 bosses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Pet cat
\item 
Bonfire
\item 
Container
\item 
Freezer
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Let the container cool down.
\item 
Pet your pet cat.
\item 
Put \textbf{9.37 spoonful of daughter} into the container.
\item 
Put \textbf{28 bosses} into the freezer for a while.
\item 
Put \textbf{28 cooled bosses} into the bonfire.
\item 
Put \textbf{29 clear concepts of marry} into the container.
\item 
Use the saw to slice \textbf{16.11 spoonful of spouse} into bits.
\item 
Retrieve the \textbf{6.93 spoonful of ashes of "cooled boss"} from the bonfire.
\item 
Pour out the mixture from the container to get the \textbf{9.71 ounces of container mixture "daughter and marry"}.
\item 
Fold the \textbf{16.11 spoonful of sliced spouse}, \textbf{6.93 spoonful of ashes of "cooled boss"} and \textbf{9.71 ounces of container mixture "daughter and marry"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{wife}.
\end{enumerate}
\newpage
\section{A wire}How to make a \textbf{wire} in 11 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.1 spoonful of hanger
\item 
6.95 ounces of cable
\item 
6.27 ounces of fence
\item 
8.86 spoonful of conductor
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Saw
\item 
Fireplace
\item 
Stone
\item 
Charcoal pencil
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{8.86 spoonful of conductor} into the fireplace.
\item 
Use the saw to slice \textbf{6.95 ounces of cable} into bits.
\item 
Hold \textbf{6.27 ounces of fence} briefly into the fireplace to burn them a bit.
\item 
Crack \textbf{6.27 ounces of slightly burned fence} with the stone.
\item 
Retrieve the \textbf{4.21 ounces of ashes of "conductor"} from the fireplace.
\item 
Wait for a long time.
\item 
Crack \textbf{6.27 ounces of slightly burned and cracked fence} with the stone.
\item 
Draw a magic circle on the floor using the charcoal pencil.
\item 
Draw a cross into the circle and place \textbf{5.1 spoonful of hanger}, \textbf{6.95 ounces of sliced cable}, \textbf{6.27 ounces of slightly burned and crushed fence} and \textbf{4.21 ounces of ashes of "conductor"} on each corner.
\item 
Chant the following spell: "Synedilanum!"
\item 
Suddendly, a \textbf{wire} will appear inside the circle.
\end{enumerate}
\newpage
\section{A wolf}How to make a \textbf{wolf} in 14 easy steps:

\subsection{Materials}\begin{itemize}
\item 
3 creatures
\item 
8 fang
\item 
6.87 spoonful of fox
\item 
180 wildnesses
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Fireplace
\item 
Stone
\item 
Container
\item 
Bucket with ionised water
\item 
Freezer
\item 
Electric paint
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Smash \textbf{3 creatures} with the stone.
\item 
Fan the flames of the fireplace.
\item 
Purify \textbf{3 smashed creatures} with the purifier.
\item 
Put \textbf{8 fang} into the fireplace.
\item 
Put \textbf{180 wildnesses} into the freezer for a while.
\item 
Dip \textbf{3 smashed and purified creatures} into the bucket with ionised water.
\item 
Stir the container.
\item 
Hold \textbf{180 cooled wildnesses} briefly into the fireplace to burn them a bit.
\item 
Smash \textbf{180 cooled and slightly burned wildnesses} with the stone.
\item 
Retrieve the \textbf{16.35 spoonful of ashes of "fangs"} from the fireplace.
\item 
Draw a magic circle on the floor using the electric paint.
\item 
Draw a cross into the circle and place \textbf{3 smashed, purified and wet creatures}, \textbf{6.87 spoonful of fox}, \textbf{180 cooled, slightly burned and smashed wildnesses} and \textbf{16.35 spoonful of ashes of "fangs"} on each corner.
\item 
Whisper the following spell: "Furo dis experaphita!"
\item 
Reluctantly, a \textbf{wolf} will appear inside the circle.
\end{enumerate}
\newpage
\section{A wreck}How to make a \textbf{wreck} in 13 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.03 spoonful of havoc
\item 
43 crashes
\item 
4.9 spoonful of accident
\item 
9.52 ounces of drive
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Bonfire
\item 
Cauldron
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Wait.
\item 
Stir the cauldron.
\item 
Put \textbf{4.9 spoonful of accident} into the bonfire.
\item 
Let the cauldron cool down.
\item 
Wait.
\item 
Heat the cauldron.
\item 
Put \textbf{43 crashes} into the bonfire.
\item 
Put \textbf{5.03 spoonful of havoc} into the cauldron.
\item 
Fan the flames of the bonfire.
\item 
Pour out the mixture from the cauldron to get the \textbf{2.31 spoonful of cauldron mixture "havoc"}.
\item 
Retrieve the \textbf{21.18 ounces of ashes of "accident and crash"} from the bonfire.
\item 
Fold the \textbf{9.52 ounces of drive}, \textbf{2.31 spoonful of cauldron mixture "havoc"} and \textbf{21.18 ounces of ashes of "accident and crash"} together using advanced origami techniques.
\item 
If you've done it correctly, it might result in a \textbf{wreck}.
\end{enumerate}
\newpage
\section{A yacht}How to make a \textbf{yacht} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
35 boats
\item 
1 idea of sailing
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Container
\item 
Centrifuge
\item 
Bonfire
\item 
Familiar cat
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Fan the flames of the bonfire.
\item 
Put \textbf{35 boats} into the rotating centrifuge.
\item 
Let the container cool down.
\item 
Heat the container.
\item 
Put \textbf{1 idea of sailing} into the container.
\item 
Pet your familiar cat.
\item 
Stir the container.
\item 
Let the container cool down.
\item 
Pour out the mixture from the container to get the \textbf{79.76 spoonful of container mixture "sailing"}.
\item 
Stop the centrifuge and retrieve the \textbf{1.6 ounces of centrifuged mixture "boat"}.
\item 
Dump the \textbf{79.76 spoonful of container mixture "sailing"} and \textbf{1.6 ounces of centrifuged mixture "boat"} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{yacht}.
\end{enumerate}
\newpage
\section{A yearly}How to make a \textbf{yearly} in 12 easy steps:

\subsection{Materials}\begin{itemize}
\item 
5.4 ounces of tradition
\item 
4 ideas of being annual
\item 
6 ideas of being monthly
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Centrifuge
\item 
Purifier
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{4 ideas of being annual} into the rotating centrifuge.
\item 
Put \textbf{6 ideas of being monthly} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{9.2 ounces of centrifuged mixture "being annual and being monthly"}.
\item 
Put \textbf{9.2 ounces of centrifuged mixture "being annual and being monthly"} into the rotating centrifuge.
\item 
Put \textbf{5.4 ounces of tradition} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{41.95 spoonful of centrifuged mixture "centrifuged mixture "being annual and being monthly" and tradition"}.
\item 
Wait.
\item 
Purify \textbf{41.95 spoonful of centrifuged mixture "centrifuged mixture "being annual and being monthly" and tradition"} with the purifier.
\item 
Put \textbf{41.95 spoonful of purified centrifuged mixture "centrifuged mixture "being annual and being monthly" and tradition"} into the rotating centrifuge.
\item 
Stop the centrifuge and retrieve the \textbf{5.23 spoonful of centrifuged mixture "purified centrifuged mixture "centrifuged mixture "being annual and being monthly" and tradition""}.
\item 
Dump the \textbf{5.23 spoonful of centrifuged mixture "purified centrifuged mixture "centrifuged mixture "being annual and being monthly" and tradition""} into a pile on the floor.
\item 
Wait until they magically transform into a \textbf{yearly}.
\end{enumerate}
\newpage
\section{A yellow}How to make a \textbf{yellow} in 7 easy steps:

\subsection{Materials}\begin{itemize}
\item 
6 squashes
\item 
9 mellowings
\item 
6 clear concepts of being pale
\item 
3.62 ounces of tarnish
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Vessel
\item 
Hammer
\item 
Bucket with clean water
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Dip \textbf{9 mellowings} into the bucket with clean water.
\item 
Wait.
\item 
Smash \textbf{6 clear concepts of being pale} with the hammer.
\item 
Put \textbf{6 squashes} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{6.4 ounces of vessel mixture "squash"}.
\item 
Fold the \textbf{9 wet mellowings}, \textbf{6 smashed clear concepts of being pale}, \textbf{3.62 ounces of tarnish} and \textbf{6.4 ounces of vessel mixture "squash"} together using advanced origami techniques.
\item 
If you've done it correctly, it could result in a \textbf{yellow}.
\end{enumerate}
\newpage
\section{A you}How to make a \textbf{you} in 9 easy steps:

\subsection{Materials}\begin{itemize}
\item 
16.38 ounces of without
\item 
12.91 spoonful of for
\item 
9 ideas of being damn
\item 
1.91 ounces of screw
\end{itemize}
\subsection{Tools}\begin{itemize}
\item 
Purifier
\item 
Vessel
\item 
Ballpoint pen
\end{itemize}
\subsection{Instructions}\begin{enumerate}
\item 
Put \textbf{12.91 spoonful of for} into the vessel.
\item 
Pour out the mixture from the vessel to get the \textbf{3.63 ounces of vessel mixture "for"}.
\item 
Purify \textbf{1.91 ounces of screw} with the purifier.
\item 
Heat the vessel.
\item 
Let the vessel cool down.
\item 
Draw a magic circle on the floor using the ballpoint pen.
\item 
Draw a square into the circle and place \textbf{16.38 ounces of without}, \textbf{9 ideas of being damn}, \textbf{1.91 ounces of purified screw} and \textbf{3.63 ounces of vessel mixture "for"} on each corner.
\item 
Chant the following spell: "Fundeflo! Adfeclinasco incubi decemptachia puticius immundata, simpleborius rebia!"
\item 
Reluctantly, a \textbf{you} will appear inside the circle.
\end{enumerate}
\newpage
\end{document}
